\documentclass{article}
\usepackage{amsmath,amssymb,mathtools}
\begin{document}

\section*{Higham Chapter 4 Kahan returned-sum bottleneck}

I am formalizing the source-strength theorem for Kahan compensated summation
from Higham, \emph{Accuracy and Stability of Numerical Algorithms}, 2nd ed.,
Chapter 4, equation (4.8).  Please answer as a mathematician: give a rigorous
proof route, identify hidden assumptions, or state a corrected theorem if the
claimed route is false under the assumptions below.  I do not need Lean code.

\subsection*{Target}

For Algorithm 4.2, the ordinary returned stored sum $\widehat{s}_n$ should have
a source-shaped backward-error representation
\[
  \widehat{s}_n=\sum_{i=1}^n x_i(1+\mu_i),
  \qquad |\mu_i|\le 2u+O(nu^2).
\]
I need an explicit coefficient proof with first-order term $2u$, allowing loose
second-order constants.  Bounds like $O(nu)$, $14u+O(nu^2)$, or conditional
theorems that assume the final representation are not useful.

\subsection*{Algorithm and model}

The Kahan step is the usual one:
\[
  y=\operatorname{fl}(x-e),\qquad
  t=\operatorname{fl}(s+y),\qquad
  e'=\operatorname{fl}(\operatorname{fl}(t-s)-y),\qquad
  s'=t.
\]
The initial state is $s=e=0$ and the returned value is the stored $s$, not
$s+e$.  A standard local model is used for each rounded operation:
\[
  \operatorname{fl}(a\circ b)=(a\circ b)(1+\delta),\qquad |\delta|\le u,
\]
when that operation is in range.  In the concrete finite-format wrapper, finite
round-to-even and usual exactness/coherence lemmas are available, but arbitrary
input order is not assumed to satisfy FastTwoSum order conditions.

\subsection*{What is already proved locally}

\begin{itemize}
\item The compensated total $s_n+e_n$ does have source coefficients
  $1+\theta_i$ with $|\theta_i|\le 2u+O(nu^2)$.
\item The ordinary returned $s_n$ is proved to have the desired
  $2u+O(nu^2)$ coefficient bound if every correction subtraction
  $(t-s)-y$ is exact, or under sufficient FastTwoSum/Sterbenz/Ferguson-style
  finite-format hypotheses.
\item The bare relative-error model is too weak: it does not force the first
  step from $(0,0)$ to return $(x,0)$, and there are small-$u$ counterexamples
  to a bare-model $2u+C u^2$ returned-sum cap.
\item Finite coordinates alone do not imply exact correction subtraction.
  Tail FastTwoSum order, tail Sterbenz, tail Ferguson, and direct tail finite
  subtraction are all false for arbitrary input order.
\item A triangle bound from the compensated total $s+e$ to returned $s$ is too
  weak because the retained correction coefficient is first order.
\item An affine residual bridge would close the theorem if the final retained
  correction residual were bounded by $Cnu^2\sum_i |x_i|$, but the current
  input-only residual majorant is false: with one exact input it is first order.
\end{itemize}

\subsection*{Useful cancellation identities already available}

At a single Kahan coefficient step, local algebra shows the correction residual
is not independently first order:
\[
  r_e+\delta_{\mathrm{sub}}=O(u^2),
\]
where $\delta_{\mathrm{sub}}$ is the rounding error in $(t-s)-y$.  A companion
identity gives
\[
  r_{\mathrm{total}}-r_e-\delta_y=O(u^2),
\]
where $\delta_y$ is the rounding error in $x-e$.  These are available both
locally and in prefix-indexed coefficient wrappers.  The missing proof is how
to propagate this cancellation through the returned stored coordinate $s$ so
that the final source coefficient has only $2u+O(nu^2)$ loss without assuming
$\delta_{\mathrm{sub}}=0$.

\subsection*{Questions}

\begin{enumerate}
\item Is Higham's equation (4.8) for the ordinary returned $s_n$ true under only
  the standard local relative-error model plus finite-format coherence, for
  arbitrary input order?  Or does the published proof implicitly assume exact
  correction subtraction, FastTwoSum order, a guard digit, no underflow, or a
  different returned quantity such as $s_n+e_n$?
\item If it is true for ordinary returned $s_n$, give a detailed coefficient
  recurrence that uses the cancellation identities above and yields
  $|\mu_i|\le 2u+Cnu^2$.  Please spell out the induction invariants and where
  first-order $\delta_{\mathrm{sub}}$ terms cancel.
\item If it is not true as stated, give the sharp corrected theorem and the
  weakest mathematically natural hypotheses that make it true.
\item Please separate source-faithful proof facts from speculation.  I need
  small lemmas suitable for a proof assistant, not a broad explanation.
\end{enumerate}

\end{document}
