\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Higham Chapter 4 Kahan Eq. (4.8): hidden coherence follow-up}

We are formalizing Higham, \emph{Accuracy and Stability of Numerical
Algorithms}, 2nd ed., Chapter 4, equation (4.8), for Kahan summation.
The target is the ordinary returned stored sum
\[
  \widehat{s}_n = \sum_i x_i (1+\mu_i),
  \qquad |\mu_i| \le 2u + O(nu^2),
\]
with explicit constants suitable for Lean.

We already have a Lean proof for the paired compensated total \(s+e\), and
we have a conditional theorem for the ordinary returned sum if every correction
subtraction is exact.  We also have local non-exact-subtraction cancellation
facts.  For one abstract step, using real coefficients, define:
\[
\begin{aligned}
t_s &= A+C,\\
t_x &= B+D,\\
r &= t_x - t_s,\\
c &= D-C.
\end{aligned}
\]
The available local facts, in Lean as
\texttt{highamCh4KahanSuffixCounterexampleLocalFacts}, are
\[
\begin{aligned}
|t_s-1|&\le 3u^2,\\
|t_x-1|&\le 2u+9u^2,\\
|C|&\le u(1+u)^2,\\
|c|&\le u(1+u)^2(3+u),\\
|c+\delta_{\rm sub}|&\le 7u^2,\\
|r-c-\delta_y|&\le u^2,\\
|r+\delta_{\rm sub}-\delta_y|&\le 8u^2,\\
|\delta_{\rm sub}|&\le u,\qquad |\delta_y|\le u.
\end{aligned}
\]
The returned coordinate after propagating a paired state \((T,E)\) through one
homogeneous step is
\[
  \operatorname{returned}(T,E) = (A+C)T + (B+D)E - (CT+DE).
\]

GPT-5.5 Pro previously suggested, and Lean now proves, that these local facts
alone are insufficient.  The two symbolic steps
\[
\begin{array}{c|ccccc|cc}
 & A&B&C&D&x&\delta_{\rm sub}&\delta_y\\
\hline
1&1&1+u&0&u+u^2&0&-u&u\\
2&1+u&1+u&-u&-u&0&0&0
\end{array}
\]
satisfy all the local facts for \(0\le u\le1\).  Injecting a unit source at
step 1 and propagating through step 2 gives returned coefficient
\[
  (1+u)^3,\qquad |(1+u)^3-1|=3u+3u^2+u^3.
\]
Thus for every fixed \(K\ge0\) and sufficiently small \(u>0\), the local facts
coexist with failure of the cap \(2u+Ku^2\).

\section*{Question}

Give a mathematically rigorous, Lean-friendly next route.  I need one of:

\begin{enumerate}
\item A precise extra ``coherence'' invariant, stated only in terms of the
step coefficients/source-suffix recurrence and actual Kahan rounding deltas,
that rules out the two-step symbolic counterexample and is strong enough to
prove the original leading \(2u\) source-coefficient theorem with explicit
\(O(nu^2)\) constants.

\item A corrected theorem surface if the original leading \(2u\) returned
coefficient theorem is too strong without additional assumptions.  State the
correct leading constant, explicit second-order constants, and the recurrence
proof skeleton.

\item A proof that the two-step symbolic counterexample cannot arise from an
actual finite round-to-even Kahan trace, with the exact finite-format or
operation-order hypotheses needed.
\end{enumerate}

Please be concrete.  Define any new quantities, state every hypothesis, and
give a recurrence proof that can be translated into Lean inequalities.  Avoid
``big-O'' unless you also provide explicit constants.  If a hidden hypothesis
is necessary, say exactly where it enters and why the symbolic counterexample
violates it.

\end{document}
