\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Higham Chapter 6, Problem 6.10: Lean-oriented proof route}

I am formalizing a numerical linear algebra chapter in Lean.  Please give a
rigorous, Lean-friendly proof plan for the following theorem, broken into small
lemmas with exact algebraic identities and all side conditions.

Let \(F\in\mathbb C^{n\times n}\), let
\[
  B=\begin{bmatrix} I & F\\ 0 & I\end{bmatrix},
\]
and let \(t=\|F\|_2\), the spectral/operator 2-norm.  Higham Problem 6.10 asks
for the formula
\[
  \|B\|_2
  =
  \sqrt{\frac{2+t^2+t\sqrt{4+t^2}}{2}}.
\]
It also notes that when \(t=1\), this value is the golden ratio.

\section*{Existing Lean-side objects}

The local repository already has:

\begin{itemize}
\item complex matrices as finite matrices over \(\mathbb C\);
\item a concrete complex operator norm \(\operatorname{op2}(A)=\|A\|_2\);
\item a checked rectangular SVD package:
  \(F=U\Sigma V^*\), with unitary coordinate changes and diagonal-or-zero
  singular-value matrix;
\item \(\operatorname{op2}(F)\) equals the largest singular value;
\item unitary changes preserve the Euclidean/operator norm, or can be proved
  from their vector-norm preservation;
\item standard finite-dimensional Euclidean vector norm facts.
\end{itemize}

\section*{Requested output}

Please do not give a high-level sketch only.  I need a proof route suitable for
formalization.  In particular:

\begin{enumerate}
\item Show how to reduce \(B\) by unitary block diagonal factors to the case
  \[
    \begin{bmatrix} I & \Sigma\\ 0 & I\end{bmatrix}
  \]
  without changing the operator norm.
\item For diagonal \(\Sigma=\operatorname{diag}(\sigma_i)\), show how the
  squared norm reduces to the maximum over independent \(2\times2\) blocks
  \[
    D_\sigma=\begin{bmatrix}1&\sigma\\0&1\end{bmatrix}.
  \]
\item Compute the largest singular value of \(D_\sigma\).  Please give the
  exact eigenvalues of \(D_\sigma^*D_\sigma\), prove which one is the largest
  for \(\sigma\ge0\), and simplify it to
  \[
    \lambda_{\max}(\sigma)
      =\frac{2+\sigma^2+\sigma\sqrt{4+\sigma^2}}{2}.
  \]
\item Prove monotonicity of
  \[
    g(\sigma)=\sqrt{\frac{2+\sigma^2+\sigma\sqrt{4+\sigma^2}}{2}}
  \]
  on \([0,\infty)\), preferably by an algebraic argument avoiding calculus if
  possible.  This should justify replacing \(\max_i g(\sigma_i)\) by
  \(g(\sigma_{\max})=g(\|F\|_2)\).
\item Give a compact proof that \(g(1)=(1+\sqrt5)/2\).
\end{enumerate}

If there is a shorter route avoiding a full block-diagonal direct-sum theorem,
please include it too, but make clear which lemmas would be easiest to prove in
Lean.

\end{document}
