\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{GPT-5.5 Pro retry: answer now, not a plan}

Please solve the mathematical question below.  Do not respond with ``I will''
or a plan.  Start with one of:

\[
\text{Conclusion: leading }2u\text{ can be restored, by invariant ...}
\]
or
\[
\text{Conclusion: leading }2u\text{ cannot be restored from these hypotheses; corrected leading constant is ...}
\]

Then provide explicit inequalities and proof steps.

\subsection*{Kahan coefficient recurrence}

For one coefficient step, stored coordinates propagate by
\[
  s' = A s + B e,\qquad e' = C s + D e.
\]
Paired coordinates are
\[
  z=s+e,\qquad q=e,
\]
with
\[
  z'=Tz+Rq,\qquad q'=Cz+Hq,
\]
where
\[
  T=A+C,\qquad B_T=B+D,\qquad R=B_T-T,\qquad H=D-C.
\]
The ordinary returned coefficient is \(r=z-q=s\), so
\[
  r'=z'-q'=A z+(B-A)q=A r+Bq.
\]
For a source coefficient injected at step \(i\),
\[
  z_0=B_i+D_i,\qquad q_0=D_i,\qquad r_0=B_i.
\]

\subsection*{Local facts already proved}

For every actual Kahan coefficient step, with \(0\le u\le 1/64\), there exist
\(\delta_{\rm sub},\delta_y\) satisfying
\[
  |\delta_{\rm sub}|\le u,\qquad |\delta_y|\le u,
\]
and
\[
\begin{aligned}
  |T-1| &\le 3u^2,\\
  |B_T-1| &\le 2u+9u^2,\\
  |C| &\le u(1+u)^2,\\
  |H| &\le u(1+u)^2(3+u),\\
  |H+\delta_{\rm sub}| &\le 7u^2,\\
  |R-H-\delta_y| &\le u^2,\\
  |R+\delta_{\rm sub}-\delta_y| &\le 8u^2.
\end{aligned}
\]
From these facts one can prove the paired/source-total bound
\[
  |z_m-1|\le 2u+(9+13m)u^2,\qquad |q_m|\le 3u
\]
for any actual suffix of length \(m\) with \(mu^2\le 1/16\).

However, local facts alone do not imply
\[
  |r_m-1|\le 2u+K u^2
\]
with fixed \(K\): a symbolic two-step example satisfying these facts gives
\[
  r_m=(1+u)^3=1+3u+3u^2+u^3.
\]
Thus a leading-\(2u\) proof must use an extra actual-trace coherence property,
not just the displayed local inequalities.

\subsection*{Task}

Answer rigorously:

\begin{enumerate}
\item Is there an actual Kahan-trace invariant relating \(q_j\), \(r_j\), and
      the subsequent \(\delta_{\rm sub},\delta_y\) that restores
      \(|r_m-1|\le 2u+O(mu^2)\)?
\item If yes, state it as a local/suffix-friendly invariant and prove the
      recurrence with explicit constants.
\item If no, prove why a corrected theorem must have leading constant bigger
      than \(2\), and say whether the best source-honest ordinary returned
      bound from the known facts is leading \(3u\), \(5u\), or another value.
\end{enumerate}

Do not assume exact correction subtraction unless the theorem is explicitly
conditional.  That exact-subtraction route is already handled separately.

\end{document}
