\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Question: Higham Problem 6.1, equality in the $S/2$ matrix norm bound}

This is a math-only proof-route request for formalization.  Please do not rely
on repository files.  I need a rigorous theorem statement and proof plan,
including caveats, for the equality case in the entrywise-sum/spectral-norm
bound from Higham, Chapter 6, Problem 6.1.

Definitions:
\[
  \|A\|_S=\sum_{i,j}|a_{ij}|,\qquad
  \|A\|_2=\sigma_{\max}(A),\qquad r=\operatorname{rank}(A).
\]
The table bound I have formalized is
\[
  \|A\|_S \le \sqrt{mn\,r}\,\|A\|_2
\]
for an \(m\times n\) complex matrix \(A\).  It follows from
\[
  \|A\|_S \le \sqrt{mn}\,\|A\|_F,\qquad
  \|A\|_F \le \sqrt{r}\,\|A\|_2.
\]

Higham Problem 6.1 then says, in the extracted text:
\[
\text{``Show that equality in } \|A\|_S \le \alpha_{S,2}\|A\|_2
\text{ is attained for square real matrices \(A\) iff \(A\) is a scalar
multiple of a Hadamard matrix, and for square complex matrices if }
a_{rs}=\exp(2\pi i(r-1)(s-1)/n).''}
\]

Potential issue: with the rank-sensitive bound above, the all-ones matrix
\(J=e e^T\) has rank \(1\) and seems to satisfy equality:
\[
  \|J\|_S=n^2,\quad r=1,\quad \|J\|_2=n,\quad
  \sqrt{n^2\cdot 1}\,\|J\|_2=n^2,
\]
but \(J\) is not a Hadamard matrix for \(n>1\).  This suggests the source's
``iff Hadamard'' may refer to the full-rank square case, or to a non-rank-
sensitive constant, or it may need a caveat.

Please answer:

1. What is the mathematically correct equality characterization for
   \[
     \|A\|_S = \sqrt{mn\,\operatorname{rank}(A)}\,\|A\|_2
   \]
   over real or complex matrices?

2. In the square real full-rank case, prove carefully that equality is
   equivalent to \(A=cH\), where \(H\) is a real Hadamard matrix
   (\(|H_{ij}|=1\) and \(H^T H=nI\)), allowing for the zero matrix caveat if
   needed.

3. Explain exactly where the equality conditions enter:
   equality in Cauchy--Schwarz for \(\|A\|_S\le\sqrt{mn}\|A\|_F\), and equality
   in \(\|A\|_F\le\sqrt{r}\|A\|_2\).

4. Give a Lean-friendly proof route using only finite sums, singular values or
   Gram matrix/operator-norm facts, and elementary equality cases.  I need
   detailed rigorous steps, not code.

5. State which source-facing theorem(s) should be formalized to avoid proving a
   false claim: a general equality characterization, a nonzero full-rank square
   real iff theorem, or a weaker forward/backward pair.

\end{document}
