\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Question for GPT-5.5 Pro: Kahan summation Eq. (4.8) returned coefficient}

I am formalizing Higham, \emph{Accuracy and Stability of Numerical Algorithms},
2nd ed., Chapter 4, Eq. (4.8), for Kahan summation.  Please give a rigorous
mathematical proof route, not Lean code.  I need to know whether a hidden
coherence invariant can recover the ordinary returned-sum source coefficient
bound with leading constant \(2u\), or whether the honest theorem surface must
weaken the leading constant.

\subsection*{Current coefficient model}

For one Kahan coefficient step let
\[
  A,B,C,D\in\mathbb R.
\]
In stored-sum/correction coordinates the homogeneous source-coefficient
propagation is
\[
  s' = A s + B e,\qquad e' = C s + D e.
\]
In paired coordinates
\[
  z=s+e,\qquad q=e,
\]
the same step is
\[
  z' = Tz + Rq,\qquad q' = Cz + Hq,
\]
where
\[
  T=A+C,\qquad B_T=B+D,\qquad R=B_T-T,\qquad H=D-C.
\]
The ordinary returned coefficient is
\[
  r = z-q=s.
\]
Therefore
\[
  r'=z'-q'=(T-C)z+(R-H)q=A z+(B-A)q.
\]
Equivalently, since \(z=r+q\),
\[
  r' = A r + B q.
\]

For a source coefficient injected at step \(i\), the initial paired state is
\[
  z_0=B_i+D_i,\qquad q_0=D_i,\qquad r_0=B_i.
\]
The later suffix steps use the recurrence above.

\subsection*{Facts already proved locally}

For every actual Kahan coefficient step, with unit roundoff \(u\le 1/64\), Lean
already proves the following local facts.  There exist roundoff deltas
\(\delta_{\rm sub},\delta_y\), with
\[
  |\delta_{\rm sub}|\le u,\qquad |\delta_y|\le u,
\]
such that
\[
\begin{aligned}
  |T-1| &\le 3u^2,\\
  |B_T-1| &\le 2u+9u^2,\\
  |C| &\le u(1+u)^2,\\
  |H| &\le u(1+u)^2(3+u),\\
  |H+\delta_{\rm sub}| &\le 7u^2,\\
  |R-H-\delta_y| &\le u^2,\\
  |R+\delta_{\rm sub}-\delta_y| &\le 8u^2.
\end{aligned}
\]
From these facts I proved a corrected paired-coordinate suffix theorem:
if initially
\[
  |z_0-1|\le 2u+9u^2,\qquad |q_0|\le 3u,
\]
then after any suffix of length \(m\) satisfying \(m u^2\le 1/16\),
\[
  |z_m-1|\le 2u+(9+13m)u^2,\qquad |q_m|\le 3u.
\]
I also proved that the actual Kahan source-total coefficients satisfy this
theorem.

\subsection*{Known obstruction}

The local facts above alone cannot imply an ordinary returned coefficient cap
\[
  |r_m-1|\le 2u+K u^2
\]
with fixed \(K\).  A two-step symbolic example satisfying all local facts gives
\[
  r_m=(1+u)^3,
\]
so
\[
  |r_m-1|=3u+3u^2+u^3.
\]
Thus any proof of Higham's printed leading-\(2u\) statement must use some extra
coherence property of actual Kahan traces/coefficient steps, not only the local
facts listed above.

\subsection*{What I need}

Please answer these questions rigorously:

1. Is there a plausible hidden invariant specific to actual Kahan coefficient
   steps that restores
   \[
     |r_m-1|\le 2u+O(m u^2)
   \]
   for every source coefficient?
2. If yes, state the invariant in mathematical form and give detailed proof
   steps showing how it combines with the recurrence \(r'=A r+Bq\) or
   \(r'=z'-q'\).  Please make the invariant local/suffix-friendly enough to
   become Lean lemmas.
3. If no, explain why the leading-\(2u\) returned-coordinate theorem is not
   derivable under the standard local relative-error Kahan model, and propose
   the sharpest source-honest corrected theorem surface.  Is the corrected
   ordinary returned coefficient leading \(3u\), \(5u\), or something else?
4. Avoid vague big-O only.  Give explicit inequalities with constants that can
   be formalized.

Important: do not assume exact correction subtraction unless you explicitly
mark the theorem as conditional; that route is already formalized separately.

\end{document}
