\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{url}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Exp}{\mathbb{E}}
\newcommand{\Frob}[1]{\left\lVert #1\right\rVert_F}
\newcommand{\Norm}[1]{\left\lVert #1\right\rVert_2}
\newcommand{\NormOne}[1]{\left\lVert #1\right\rVert_1}
\newcommand{\EntryOne}[1]{\left\lVert #1\right\rVert_{1,1}}
\newcommand{\fl}{\operatorname{fl}}
\newcommand{\I}{I}
\newcommand{\eps}{\varepsilon}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\tr}{\operatorname{tr}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem*{baseline}{Exact baseline}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\title{Algorithm 3: Floating-Point Theorem Surfaces for SRHT and CountSketch Preconditioning}
\author{}
\date{}

\begin{document}
\sloppy

\maketitle

\section*{Scope}

Algorithm 3 in the RandNLA survey applies random projection or
preconditioning matrices to an input matrix \(A\):
\[
  \Pi_L A,\qquad A\Pi_R,\qquad \Pi_L A\Pi_R .
\]
The survey states this step for several random projection families
\cite{DrineasMahoney2016RandNLA}.  This note records the final theorem
surfaces for the closed signed-Hadamard/SRHT branch, the collision-free
CountSketch actual-input branch, and the current implementation-facing
CountSketch product-grid sparse-Gram branch.  The SRHT part includes
deterministic orthogonal-preconditioning identities, exact SRHT row-norm
uniformization, uniform row sampling after preconditioning, and the
floating-point transfer terms.  The CountSketch part covers concrete
collision-free and finite-cover Markov/Frobenius routes with sparse-apply and
sparse-Gram floating-point arithmetic.  These CountSketch routes are not the
optimal input-sparsity subspace embedding theorem of Clarkson--Woodruff
\cite{ClarksonWoodruff2013}.
Gaussian and FJLT transforms are not included here.

\section*{Notation}

Let \(m,n,s\) be positive integers, and let \(U\in\R^{m\times n}\) have
orthonormal columns:
\[
  U^T U=\I_n .
\]
For a matrix \(V\in\R^{m\times n}\), write \(V_{i*}\) for row \(i\).  If
\(V^TV=\I_n\), define its leverage probability
\[
  \ell_i(V)=\frac{\Norm{V_{i*}}^2}{n}.
\]

Let \(H\in\R^{m\times m}\) be an exact orthogonal matrix whose entries are
flat:
\[
  H^T H=\I_m,\qquad H_{ik}^2=\frac1m\quad\text{for all }i,k.
\]
Let \(\omega=(\omega_1,\ldots,\omega_m)\) be an exact Rademacher sign vector,
meaning that the \(2^m\) sign vectors in \(\{\pm1\}^m\) are equally likely.
Set
\[
  D_\omega=\diag(\omega_1,\ldots,\omega_m),\qquad
  V_\omega=H D_\omega U .
\]
The random signs are the only randomness in \(V_\omega\).

After preconditioning, draw exact iid uniform row indices
\[
  J_1,\ldots,J_s\in\{1,\ldots,m\},
  \qquad
  \Prob[J_t=i]=\frac1m .
\]
The exact uniform-row sketch of \(V_\omega\) is
\[
  \widetilde V_{\omega,J,tj}
  =
  \frac{(V_\omega)_{J_tj}}{\sqrt{s/m}} ,
\]
and its exact sampled Gram matrix is
\[
  G_s(V_\omega)
  =
  \widetilde V_{\omega,J}^{\,T}\widetilde V_{\omega,J}
  =
  \frac1s\sum_{t=1}^s m\,
  (V_\omega)_{J_t*}^{\,T}(V_\omega)_{J_t*}.
\]
The probability symbol \(\Prob[\cdot]\) is always taken with respect to the
exact product law of \(\omega\) and \(J=(J_1,\ldots,J_s)\), unless a theorem
explicitly restricts it to the sign law or the row-sampling law.

For symmetric matrices \(X,Y\in\R^{n\times n}\), write \(X\preceq Y\) when
\[
  x^T X x\le x^T Y x
  \qquad\text{for every }x\in\R^n .
\]

Let \(u\ge0\) be the floating-point unit roundoff.  When a length-\(r\)
floating-point dot product or matrix product is charged, \(\gamma_r\) denotes
the valid accumulated roundoff factor for that length, in the usual Higham
model \cite{Higham2002}.  For a deterministic row-norm cap \(R\ge0\), define
the uniform-row floating-point budgets
\[
  \tau_{\rm scale}(R)
  =
  n(2u+u^2)mR,
\]
\[
  \tau_{\rm dot}(R;s)
  =
  n\,\gamma_s(1+u)^2mR,
\]
and
\[
  \tau_{\rm unif}(R;s)
  =
  \tau_{\rm scale}(R)+\tau_{\rm dot}(R;s).
\]
Here \(\tau_{\rm scale}\) charges rounded uniform row scaling and
\(\tau_{\rm dot}\) charges the final rounded Gram dot products.

For \(\theta>0\), \(L>0\), and \(\eps>0\), define
\[
  \beta_+(\theta,L)
  =
  \frac{\exp(\theta L)-\theta L-1}{L^2},
  \qquad
  \beta_-(\theta)
  =
  \exp(\theta)-\theta-1,
\]
and the exact uniform-row tail budget
\[
\begin{aligned}
  \Phi(\theta,L,\eps,s,n)
  &:=
  e^{-\theta s\eps}\,n\,
    e^{s\beta_+(\theta,L)(L^2+1)}
  \\
  &\quad+
  e^{-\theta s\eps}\,n\,
    e^{s\beta_-(\theta)(L^2+1)} .
\end{aligned}
\]
The parameter \(\eps\) is the exact user-chosen subspace-embedding distortion
tolerance.  It is not computed by Algorithm 3 and therefore carries no
floating-point error term.  Once \(\eps\) is chosen, the sample size \(s\) and
Chernoff parameter \(\theta\) must make the exact sampling budget
\(\Phi(\theta,L,\eps,s,n)\) small enough.  A standard constant-distortion
instantiation is \(\eps=1/2\); keeping \(\eps\) symbolic gives the usual
accuracy-versus-sample-size tradeoff.
For a dimension parameter \(q\), row-bound parameter \(L\), distortion
tolerance \(\eps\), and sampling failure budget \(\delta\), define the exact
sample-count rule
\[
  s_{\min}(L,\eps,\delta;q)
  =
  \min\left\{
    k\in\mathbb N_{>0}:
    \exists\,\theta>0\text{ such that }
    \Phi(\theta,L,\eps,k,q)\le\delta
  \right\}.
\]
Thus \(s\) is an exact integer design parameter: the algorithm draws exactly
\(s\) iid uniform row indices after this value has been chosen.  The choice of
\(s\) is not a floating-point computation in the theorem.  The usual
matrix-Chernoff scaling \cite{Tropp2012} gives the sufficient order
\[
  s_{\min}(L,\eps,\delta;q)
  =
  O\!\left(\frac{L}{\eps^2}\log\frac{q}{\delta}\right),
\]
with absolute constants in the standard \(0<\eps<1\) regime.
For the source-sharp SRHT row-norm radius, define
\[
  S(t)=\sqrt{\frac nm}+t,\qquad
  R(t)=S(t)^2,\qquad
  L(t)=mR(t),\qquad
  \tau_{\rm SRHT}(t)=\tau_{\rm unif}(R(t);s).
\]

\section*{What Is Exact and What Is Computed}

\begin{itemize}
  \item Exact arithmetic objects: the input matrix \(A\) as handed to
  Algorithm 3, any analysis-only orthonormal basis \(U\) for a column space,
  \(H\), \(D_\omega\), \(V_\omega\), the Rademacher sign law, the uniform row
  law, the exact sketch \(\widetilde V_{\omega,J}\), and exact Gram matrices
  such as \(G_s(V_\omega)\).  These are the mathematical reference objects in
  the probability bounds.
  \item Exact integer and Boolean objects: a Sylvester/Walsh sign pattern
  generated from bit parities is an exact deterministic sign table.  Its
  entries are \(\pm1\) exactly.  The scale factor \(\sqrt{1/m}\), if computed
  in floating point, is not part of that exact integer/Boolean generation.
  The sample count \(s\) is an exact positive integer chosen from the
  sampling-budget rule \(s_{\min}\); the theorem does not model floating-point
  error in choosing this integer.
  \item Floating-point objects after an exact \(V_\omega\) is supplied:
  the uniform denominator \(\sqrt{s/m}\) may be replaced by a computed
  \(\widehat d\), the sampled rows may be scaled by rounded division, and the
  final Gram entries may be computed by rounded dot products.  These operations
  are charged by denominator and \(\tau_{\rm unif}\) budgets.
  \item Floating-point objects used to form \(V_\omega\): an implementation may
  store or generate \(\widehat H\), store realized signs
  \(\widehat\omega\), form \(\widehat P_\omega\approx HD_\omega\), use a
  computed input basis \(\widehat U\), and form
  \(\widehat V_\omega=\fl(\widehat P_\omega\widehat U)\).  These quantities
  are computable in floating point only after explicit entrywise or normwise
  certificates are supplied.
  \item Floating-point objects used on the actual input matrix \(A\): the
  materialized SRHT preconditioner \(\widehat P_\omega\), the product
  \(\widehat Y_\omega=\fl(\widehat P_\omega A)\), rounded uniform-row scaling,
  and the rounded sampled Gram matrix are computed.  The exact comparison
  objects are \(Y_\omega=P_\omega A\), the exact scaled sample from
  \(Y_\omega\), and \(A^TA\).
  \item A QR, SVD, singular-vector, or basis routine that produces
  \(\widehat U\) is not part of the SRHT probability theorem.  Its error enters
  through a separate matrix certificate for \(\widehat U-U\).  Without that
  certificate, the theorem remains an exact-\(U\) statement.
\end{itemize}

\section*{Deterministic Orthogonal Preconditioning}

\begin{theorem}[Exact Frobenius stability]
Let \(A\in\R^{m\times n}\).  If
\(\Pi_L\in\R^{m\times m}\) and \(\Pi_R\in\R^{n\times n}\) are exact
orthogonal matrices, then
\[
  \Frob{\Pi_LA}=\Frob{A},\qquad
  \Frob{A\Pi_R}=\Frob{A},\qquad
  \Frob{\Pi_LA\Pi_R}=\Frob{A}.
\]
\end{theorem}

\begin{theorem}[Exact orthonormal-column and leverage-denominator invariance]
Let \(U\in\R^{m\times n}\) satisfy \(U^TU=\I_n\).  If
\(\Pi_L\in\R^{m\times m}\) and \(\Pi_R\in\R^{n\times n}\) are exact
orthogonal matrices, then
\[
  (\Pi_LU)^T(\Pi_LU)=\I_n,\qquad
  (U\Pi_R)^T(U\Pi_R)=\I_n,\qquad
  (\Pi_LU\Pi_R)^T(\Pi_LU\Pi_R)=\I_n .
\]
Consequently the leverage denominator remains exactly \(n\):
\[
  \sum_{i=1}^m \Norm{(\Pi_LU)_{i*}}^2
  =
  \sum_{i=1}^m \Norm{(U\Pi_R)_{i*}}^2
  =
  \sum_{i=1}^m \Norm{(\Pi_LU\Pi_R)_{i*}}^2
  =
  n .
\]
\end{theorem}

\begin{theorem}[Exact signed-Hadamard orthogonal preprocessing]
Let \(H\in\R^{m\times m}\) be exact orthogonal, and let
\(\omega\in\{\pm1\}^m\).  Then \(D_\omega\) and \(HD_\omega\) are orthogonal.
For every \(U\in\R^{m\times n}\) with \(U^TU=\I_n\),
\[
  (HD_\omega U)^T(HD_\omega U)=\I_n,
  \qquad
  \sum_{i=1}^m \Norm{(HD_\omega U)_{i*}}^2=n .
\]
Under the exact Rademacher law, this event has probability one.
\end{theorem}

\section*{Uniform Row Denominator}

\begin{theorem}[Computed uniform-row denominator certificate]
Let
\[
  d=\sqrt{s/m},\qquad \widehat d\ne0,\qquad d\ne0,
  \qquad |\widehat d-d|\le \eta_d .
\]
For an exact row value \(V_{ij}\), define the exact scaled value
\[
  B_{ij}=V_{ij}/d
\]
and the floating-point scaled value
\[
  \widehat B_{ij}^{\,\widehat d}=\fl(V_{ij}/\widehat d).
\]
Then
\[
  \left|\widehat B_{ij}^{\,\widehat d}-B_{ij}\right|
  \le
  \left|V_{ij}/\widehat d\right|u
  +
  \frac{|V_{ij}|\,\eta_d}{|\widehat d|\,|d|}.
\]
The row index is still drawn from the exact uniform law \(1/m\).  Only the
non-probability scalar \(\widehat d\) and the final rounded division are
charged.
\end{theorem}

\begin{theorem}[Closed denominator routines]
Assume \(0<u<1\), \(m>0\), \(s>0\), and \(d=\sqrt{s/m}\).  The preceding
certificate applies with the following choices of \(\eta_d\):
\[
\begin{array}{@{}ll@{}}
\text{exact denominator} &
  \eta_d=0,\\[2mm]
\widehat d=\fl(\sqrt{s/m})\text{ with exact input }s/m &
  \eta_d=d\,u,\\[2mm]
\widehat x=\fl(s/m),\ \widehat d=\fl(\sqrt{\widehat x}) &
  \eta_d=d\bigl(\sqrt{1+u}\,u+u\bigr),\\[2mm]
\widehat r=\fl(1/m),\ \widehat x=\fl(s\widehat r),\
  \widehat d=\fl(\sqrt{\widehat x}) &
  \eta_d=d\left(\sqrt{(1+u)(1+u)}\,u+2u+u^2\right),\\[2mm]
\widehat s_0=\fl(\sqrt{s}),\ \widehat m_0=\fl(\sqrt{m}),\
  \widehat d=\fl(\widehat s_0/\widehat m_0) &
  \eta_d=d\,\dfrac{3u+u^2}{1-u},\\[4mm]
\widehat s_0=\fl(\sqrt{s}),\ \widehat m_0=\fl(\sqrt{m}),\
  \widehat r_m=\fl(1/\widehat m_0),\
  \widehat d=\fl(\widehat s_0\widehat r_m) &
  \eta_d=d\,\dfrac{4u+3u^2+u^3}{1-u}.
\end{array}
\]
Each line charges a different floating-point way to compute the same exact
denominator \(d=\sqrt{s/m}\).  None of these routines changes the uniform row
law.
The final SRHT implementation-facing theorems below use the last routine,
\[
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt m))
  \right),
  \qquad
  |\widehat d_\star-d|
  \le
  d\,\frac{4u+3u^2+u^3}{1-u}.
\]
The stored-sign CountSketch endpoint at the end of this note is also
instantiated with the four rounded alternatives above: exact-input square
root, divide-then-square-root, reciprocal-multiply-then-square-root, and
square-root-divide-square-root.  The exact-denominator line remains an
analysis/infrastructure specialization rather than a floating-point
denominator computation.
\end{theorem}

\section*{Exact SRHT Uniformization}

\begin{baseline}[Source-sharp signed-Hadamard row norms]
Assume \(m>0\), \(U^TU=\I_n\), and \(H_{ik}^2=1/m\) for every \(i,k\).
For every \(t>0\),
\[
  \Prob_\omega\!\left[
    \forall i,\quad
    \Norm{(HD_\omega U)_{i*}}\le
    \sqrt{\frac nm}+t
  \right]
  \ge
  1-m\exp\!\left(-\frac{mt^2}{8}\right).
\]
Equivalently,
\[
  \Prob_\omega\!\left[
    \forall i,\quad
    \ell_i(HD_\omega U)\le
    \frac{(\sqrt{n/m}+t)^2}{n}
  \right]
  \ge
  1-m\exp\!\left(-\frac{mt^2}{8}\right).
\]
This is the signed-Hadamard/SRHT row-norm bound corresponding to Tropp's SRHT
analysis \cite{Tropp2011SRHT}; the CACM Algorithm 3 discussion uses this kind
of random preprocessing to make subsequent uniform row sampling effective
\cite{DrineasMahoney2016RandNLA}.
\end{baseline}

\begin{theorem}[Logarithmic SRHT preprocessing radius]
Let \(0<\delta_{\rm pre}<m\), and set
\[
  t_\delta=\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}} .
\]
Then
\[
  \Prob_\omega\!\left[
    \forall i,\quad
    \Norm{(HD_\omega U)_{i*}}^2
    \le
    \left(\sqrt{\frac nm}+t_\delta\right)^2
  \right]
  \ge
  1-\delta_{\rm pre}.
\]
\end{theorem}

\begin{baseline}[Coordinate-Hoeffding fallback]
Let \(B\ge0\), \(\lambda>0\), and define
\[
  \eta_{\rm coord}(B,\lambda,m)
  =
  2\exp(-\lambda B)\exp\!\left(\frac{\lambda^2}{2m}\right).
\]
If
\[
  \sum_{i=1}^m\sum_{j=1}^n
    \eta_{\rm coord}(B,\lambda,m)
  \le
  \delta_{\rm pre},
\]
then
\[
  \Prob_\omega\!\left[
    \forall i,\quad
    \Norm{(HD_\omega U)_{i*}}^2\le nB^2
  \right]
  \ge
  1-\delta_{\rm pre}.
\]
When \(H\) is orthogonal and \(n>0\), the same event implies
\[
  \ell_i(HD_\omega U)\le B^2
  \qquad\text{for every }i.
\]
This fallback is weaker than the source-sharp SRHT radius, but it has the same
exact/computed separation: the signs are random exact objects, while all later
floating-point arithmetic is charged separately.
\end{baseline}

\section*{Exact Uniform Row Sampling After Preconditioning}

\begin{theorem}[Uniform one-step Loewner bound]
Let \(V\in\R^{m\times n}\) have orthonormal columns, and define
\[
  X_i(V)=m\,V_{i*}^{\,T}V_{i*}\in\R^{n\times n}.
\]
Then \(X_i(V)\succeq0\) and
\[
  \frac1m\sum_{i=1}^m X_i(V)=\I_n .
\]
If \(\Norm{V_{i*}}^2\le R\), then
\[
  X_i(V)\preceq mR\,\I_n .
\]
\end{theorem}

\begin{baseline}[Uniform row sample-average concentration]
Let \(V\in\R^{m\times n}\) have orthonormal columns.  Suppose that for every
row \(i\),
\[
  X_i(V)\preceq L\I_n,\qquad m\Norm{V_{i*}}^2\le L .
\]
If
\[
  \Phi(\theta,L,\eps,s,n)\le\delta_{\rm sample},
\]
then
\[
  \Prob_J\!\left[
    G_s(V)-\I_n\preceq\eps\I_n
    \ \text{and}\
    -(G_s(V)-\I_n)\preceq\eps\I_n
  \right]
  \ge
  1-\delta_{\rm sample}.
\]
This is the matrix trace-MGF row-sampling bound used in the SRHT composition;
the matrix concentration lineage is represented by Tropp's matrix tail bounds
\cite{Tropp2012}.
\end{baseline}

\begin{theorem}[Exact source-sharp SRHT plus uniform row sampling]
Let \(t>0\).  Assume
\[
  m\exp\!\left(-\frac{mt^2}{8}\right)
  \le
  \delta_{\rm pre}
\]
and
\[
  \Phi(\theta,L(t),\eps,s,n)\le\delta_{\rm sample}.
\]
Then, under the exact product law of Rademacher preprocessing and iid uniform
row sampling,
\[
  \Prob\!\left[
    G_s(V_\omega)-\I_n\preceq\eps\I_n
    \ \text{and}\
    -(G_s(V_\omega)-\I_n)\preceq\eps\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
\end{theorem}

\begin{theorem}[Exact logarithmic SRHT plus uniform row sampling]
Let \(0<\delta_{\rm pre}<m\), and set
\[
  t_\delta=\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}} .
\]
If
\[
  \Phi(\theta,L(t_\delta),\eps,s,n)\le\delta_{\rm sample},
\]
then
\[
  \Prob\!\left[
    G_s(V_\omega)-\I_n\preceq\eps\I_n
    \ \text{and}\
    -(G_s(V_\omega)-\I_n)\preceq\eps\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
\end{theorem}

\section*{Floating-Point Uniform Row Sampling}

In this section \(V_\omega=HD_\omega U\) is still the exact mathematical
preconditioned basis.  Let
\[
  \widehat G_{\omega,J}^{\rm exactV}
\]
denote the Gram matrix whose sampled rows are taken from this exact
\(V_\omega\), whose row scaling is carried out by floating-point division, and
whose entries are computed by floating-point dot products.

\begin{theorem}[Fixed row-norm floating-point radius]
Assume \(\gamma_s\) is valid.  If every sampled exact row satisfies
\[
  \Norm{(V_\omega)_{J_t*}}^2\le R
  \qquad(t=1,\ldots,s),
\]
then
\[
  \Frob{
    \widehat G_{\omega,J}^{\rm exactV}-G_s(V_\omega)
  }
  \le
  \tau_{\rm unif}(R;s).
\]
Consequently, any exact two-sided Loewner event with radius \(\eps\) transfers
to the computed Gram matrix with radius
\(\eps+\tau_{\rm unif}(R;s)\).
\end{theorem}

\begin{theorem}[Source-sharp SRHT floating-point uniform row sampling]
Let \(t>0\).  Assume
\[
  m\exp\!\left(-\frac{mt^2}{8}\right)
  \le
  \delta_{\rm pre},
  \qquad
  \Phi(\theta,L(t),\eps,s,n)\le\delta_{\rm sample},
\]
and assume \(\gamma_s\) is valid.  Then
\[
  \Prob\!\left[
    -(\eps+\tau_{\rm SRHT}(t))\I_n
    \preceq
    \widehat G_{\omega,J}^{\rm exactV}-\I_n
    \preceq
    (\eps+\tau_{\rm SRHT}(t))\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
The logarithmic version substitutes
\[
  t=\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
\]
whenever \(0<\delta_{\rm pre}<m\).
\end{theorem}

\begin{remark}
The probability lower bound is unchanged from the exact SRHT theorem.  The only
change is the deterministic additive radius
\[
  \tau_{\rm SRHT}(t)
  =
  n(2u+u^2)mR(t)
  +
  n\gamma_s(1+u)^2mR(t).
\]
The first term is row-scaling error and the second term is dot-product error.
\end{remark}

\section*{Fully Computed Modeled SRHT Bounds}

This section fixes a concrete computed path and gives actual error bounds for
that path.  The path is a materialized scaled-pattern SRHT preconditioner:
the sign pattern is generated exactly by integer/Boolean arithmetic, the
normalization scale is rounded, the realized Rademacher signs are stored by a
rounded copy routine, the preconditioner matrix is formed by rounded products,
and the preconditioned matrix or sampled Gram matrix is computed in floating
point.  The probability laws are still exact mathematical laws.

The closed fully computed path below does not claim to cover an arbitrary
computed QR/SVD basis routine, an arbitrary FHT memory layout, or an arbitrary
vectorized overwrite schedule.  Those paths are not part of the final theorem
unless their concrete roundoff recurrences are reduced to the same displayed
computed quantities.

For any transform dimension \(N\), define
\[
  \widehat p_N
  =
  \frac{(1+\gamma_N)(1+u)^2}{\sqrt N},
\]
\[
  \alpha_N
  =
  \frac{\gamma_N(1+u)^2+u(1+u)+u}{\sqrt N},
\]
and
\[
  \kappa_N=\gamma_N\widehat p_N+\alpha_N .
\]
Here \(\widehat p_N\) bounds the magnitude of every computed materialized SRHT
entry, \(\alpha_N\) bounds the absolute error of every computed materialized
SRHT entry, and \(\kappa_N\) is the coefficient that appears when multiplying
one such computed preconditioner by a matrix.  These quantities are small when
the usual accumulated factors \(\gamma_N\) and the unit roundoff \(u\) are
small; the \(1/\sqrt N\) scaling is the Hadamard normalization.

\begin{theorem}[Computed materialized scaled-pattern SRHT preconditioner]
Let \(N>0\), and let \(S\in\R^{N\times N}\) be an exact sign-pattern table:
\[
  S_{ij}^2=1 .
\]
For the Sylvester/Walsh SRHT, \(S\) is the exact bit-parity sign table and is
therefore generated with exact integer/Boolean arithmetic.  Define the exact
and computed scales
\[
  c_N=\sqrt{1/N},\qquad \widehat c_N=\fl(\sqrt{1/N}),
\]
the exact and computed scaled tables
\[
  H_{ij}=c_NS_{ij},\qquad \widehat H_{ij}=\widehat c_NS_{ij},
\]
and the scale-table error radius
\[
  E^H_{ij}=c_Nu|S_{ij}|.
\]
Then
\[
  |\widehat H_{ij}-H_{ij}|\le E^H_{ij},
  \qquad H_{ij}^2=\frac1N .
\]

Let \(\sigma\in\{\pm1\}^N\) be the exact realized Rademacher sign vector.  The
implementation stores it by one of the rounded copy routines
\[
  \widehat\sigma_i=\fl(\sigma_i\cdot1),\qquad
  \widehat\sigma_i^+=\fl(\sigma_i+0),\qquad
  \widehat\sigma_i^-=\fl(\sigma_i-0).
\]
For any one of these three stored sign vectors, write the stored vector as
\(\widehat\sigma^{\rho}\).  Since \(|\sigma_i|=1\), its sign-storage error is
\[
  |\widehat\sigma^{\rho}_i-\sigma_i|\le E^{\sigma,\rho}_i,
  \qquad E^{\sigma,\rho}_i=u .
\]
Set
\[
  D=\diag(\sigma),\qquad
  \widehat D^\rho=\diag(\widehat\sigma^\rho),\qquad
  P=HD,\qquad
  \widehat P^\rho=\fl(\widehat H\widehat D^\rho).
\]
Under the floating-point model with valid \(\gamma_N\), the computed
materialized preconditioner satisfies
\[
  |\widehat P^\rho_{ij}|\le \widehat p_N,
  \qquad
  |\widehat P^\rho_{ij}-P_{ij}|\le \alpha_N .
\]
Thus the bound charges the rounded scale, rounded sign storage, and rounded
formation of the materialized \(HD\) preconditioner, but it exposes the result
through the two interpretable scalars \(\widehat p_N\) and \(\alpha_N\).
\end{theorem}

\begin{theorem}[Computed Algorithm 3 preconditioned matrices]
Let \(A\in\R^{m\times n}\) be the exact input matrix for Algorithm 3.  Let
\(S^L\in\R^{m\times m}\) and \(S^R\in\R^{n\times n}\) be exact sign-pattern
tables:
\[
  (S^L_{ik})^2=1,\qquad (S^R_{kj})^2=1 .
\]
Let \(\sigma^L\in\{\pm1\}^m\) and \(\sigma^R\in\{\pm1\}^n\) be the exact
realized Rademacher sign vectors.  Store each sign by one of the rounded copy
routines \(\fl(\sigma_i\cdot1)\), \(\fl(\sigma_i+0)\), or
\(\fl(\sigma_i-0)\), and call the stored signs
\(\widehat\sigma^L\) and \(\widehat\sigma^R\).  Then
\[
  |\widehat\sigma^L_i-\sigma^L_i|\le u,\qquad
  |\widehat\sigma^R_j-\sigma^R_j|\le u .
\]
Define the exact and computed left scale tables
\[
  c_m=\sqrt{1/m},\qquad \widehat c_m=\fl(\sqrt{1/m}),
\]
\[
  H^L_{ik}=c_mS^L_{ik},\qquad
  \widehat H^L_{ik}=\widehat c_mS^L_{ik},
  \qquad
  E^{H,L}_{ik}=c_mu|S^L_{ik}|.
\]
Define the exact and computed right scale tables
\[
  c_n=\sqrt{1/n},\qquad \widehat c_n=\fl(\sqrt{1/n}),
\]
\[
  H^R_{kj}=c_nS^R_{kj},\qquad
  \widehat H^R_{kj}=\widehat c_nS^R_{kj},
  \qquad
  E^{H,R}_{kj}=c_nu|S^R_{kj}|.
\]
Set
\[
  P_L=H^L\diag(\sigma^L),\qquad
  \widehat P_L=\fl(\widehat H^L\diag(\widehat\sigma^L)),
\]
\[
  P_R=H^R\diag(\sigma^R),\qquad
  \widehat P_R=\fl(\widehat H^R\diag(\widehat\sigma^R)).
\]
The entrywise preconditioner radii are
\[
  |\widehat P_{L,ik}-P_{L,ik}|\le \alpha_m,
  \qquad
  |\widehat P_{R,kj}-P_{R,kj}|\le \alpha_n,
\]
and the computed preconditioner entries satisfy
\[
  |\widehat P_{L,ik}|\le\widehat p_m,
  \qquad
  |\widehat P_{R,kj}|\le\widehat p_n .
\]

For left preconditioning, define
\[
  B_L=P_LA,\qquad \widehat B_L=\fl(\widehat P_LA),
\]
then
\[
  |(\widehat B_L)_{ij}-(B_L)_{ij}|
  \le
  \kappa_m\,\NormOne{A_{*j}}
  \le
  \kappa_m\sqrt m\,\Norm{A_{*j}} .
\]

For right preconditioning, define
\[
  B_R=AP_R,\qquad \widehat B_R=\fl(A\widehat P_R),
\]
then
\[
  |(\widehat B_R)_{ij}-(B_R)_{ij}|
  \le
  \kappa_n\,\NormOne{A_{i*}}
  \le
  \kappa_n\sqrt n\,\Norm{A_{i*}} .
\]

For two-sided preconditioning, first compute \(\widehat W=\widehat B_L\) and
let \(W=P_LA\).  Then compute
\[
  B_{LR}=P_LAP_R,\qquad
  \widehat B_{LR}=\fl(\widehat W\,\widehat P_R).
\]
Let
\[
  \EntryOne{A}=\sum_{p=1}^m\sum_{q=1}^n |A_{pq}|.
\]
Then the row-sensitive bound is
\[
  |(\widehat B_{LR})_{ij}-(B_{LR})_{ij}|
  \le
  (\gamma_n\widehat p_n+\alpha_n)\NormOne{W_{i*}}
  +
  (1+\gamma_n)\widehat p_n\kappa_m\EntryOne{A}.
\]
Consequently,
\[
\begin{aligned}
  |(\widehat B_{LR})_{ij}-(B_{LR})_{ij}|
  &\le
  (\gamma_n\widehat p_n+\alpha_n)\sqrt n\,\Frob{A}
  \\
  &\quad+
  (1+\gamma_n)\widehat p_n\kappa_m\EntryOne{A}.
\end{aligned}
\]
These three displayed bounds are the Algorithm 3 floating-point changes for
the computed matrices \(\Pi_LA\), \(A\Pi_R\), and \(\Pi_LA\Pi_R\) on the
materialized scaled-pattern SRHT path.
\end{theorem}

\begin{theorem}[Computed materialized SRHT basis and uniform-row Gram]
Let \(U\in\R^{m\times n}\) be the exact orthonormal-column analysis basis used
in the SRHT subspace-embedding theorem.  Let \(S\in\R^{m\times m}\) be an exact
sign-pattern table with \(S_{ia}^2=1\), and let
\(\omega\in\{\pm1\}^m\) be the exact realized Rademacher sign vector.  Store
the signs by one of the rounded copy routines
\(\fl(\omega_a\cdot1)\), \(\fl(\omega_a+0)\), or \(\fl(\omega_a-0)\), and
write the stored signs as \(\widehat\omega^\rho\).  Then
\[
  |\widehat\omega^\rho_a-\omega_a|\le u .
\]
Define
\[
  c_m=\sqrt{1/m},\qquad \widehat c_m=\fl(\sqrt{1/m}),
\]
\[
  H_{ia}=c_mS_{ia},\qquad
  \widehat H_{ia}=\widehat c_mS_{ia},
  \qquad
  E^H_{ia}=c_mu|S_{ia}|.
\]
Set
\[
  D_\omega=\diag(\omega),\qquad
  \widehat D_\omega^\rho=\diag(\widehat\omega^\rho),
\]
\[
  P_\omega=HD_\omega,\qquad
  \widehat P_\omega^\rho=\fl(\widehat H\widehat D_\omega^\rho).
\]
Define
\[
  V_\omega=P_\omega U,\qquad
  \widehat V_\omega^\rho=\fl(\widehat P_\omega^\rho U).
\]
Define the computed-basis entry radius
\[
  \Delta_V
  =
  \kappa_m\sqrt m
  =
  \gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u .
\]
Then
\[
  |\widehat V^\rho_{\omega,ij}-(V_\omega)_{ij}|
  \le
  \Delta_V .
\]
The scalar \(\Delta_V\) uses only the universal column bound
\(\NormOne{U_{*j}}\le\sqrt m\), which follows from \(U^TU=\I_n\).  Thus no
column-by-column property of \(U\) is needed in the final displayed radius.

Let \(J=(J_1,\ldots,J_s)\) be the exact uniform row sample.  The final concrete
SRHT endpoint uses the computed denominator
\[
  d=\sqrt{s/m},
  \qquad
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt m))
  \right),
\]
and the locally proved denominator certificate gives
\[
  \widehat d_\star\ne0,
  \qquad
  |\widehat d_\star-d|
  \le
  d\,\frac{4u+3u^2+u^3}{1-u}.
\]
Define the concrete relative denominator error
\[
  \delta_d=\frac{4u+3u^2+u^3}{1-u},
  \qquad 0\le\delta_d<1,
\]
and the relative scaled-row entry error
\[
  \zeta(t)
  =
  \frac{S(t)(u+\delta_d)+(1+u)\Delta_V}
       {(1-\delta_d)S(t)}.
\]
On the exact SRHT row-norm event, every exact scaled sketch entry has absolute
value at most \(\sqrt{m/s}\,S(t)\), and every computed scaled sketch entry
differs from it by at most \(\sqrt{m/s}\,S(t)\zeta(t)\).

Let the computed sampled matrix be
\[
  \widehat B^\rho_{tj}
  =
  \fl\!\left(\widehat V^\rho_{\omega,J_tj}/\widehat d_\star\right),
  \qquad
  \widehat G_{\omega,J}^\rho
  =
  \fl\!\left((\widehat B^\rho)^T\widehat B^\rho\right).
\]
Define the final readable floating-point radius
\[
  T_{\rm SRHT}^{\rm fp}(t)
  =
  nm\,S(t)^2
  \left(
    2\zeta(t)+\zeta(t)^2
    +
    \gamma_s\bigl(1+\zeta(t)\bigr)^2
  \right).
\]
Equivalently, substituting \(\zeta(t)\), \(S(t)\), \(\delta_d\), and
\(\Delta_V\), the same exact radius is
\begingroup
\small
\[
\begin{aligned}
  T_{\rm SRHT}^{\rm fp}(t)
  &=
  nm\left(\sqrt{\frac nm}+t\right)^2
  \Bigg[
    2
    \frac{
      \left(\sqrt{\frac nm}+t\right)
      \left(u+\frac{4u+3u^2+u^3}{1-u}\right)
      +(1+u)
      \left(\gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u\right)
    }{
      \left(1-\frac{4u+3u^2+u^3}{1-u}\right)
      \left(\sqrt{\frac nm}+t\right)
    }
  \\
  &\quad+
    \left(
    \frac{
      \left(\sqrt{\frac nm}+t\right)
      \left(u+\frac{4u+3u^2+u^3}{1-u}\right)
      +(1+u)
      \left(\gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u\right)
    }{
      \left(1-\frac{4u+3u^2+u^3}{1-u}\right)
      \left(\sqrt{\frac nm}+t\right)
    }
    \right)^2
  \\
  &\quad+
    \gamma_s
    \left(
      1+
      \frac{
        \left(\sqrt{\frac nm}+t\right)
        \left(u+\frac{4u+3u^2+u^3}{1-u}\right)
        +(1+u)
        \left(\gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u\right)
      }{
        \left(1-\frac{4u+3u^2+u^3}{1-u}\right)
        \left(\sqrt{\frac nm}+t\right)
      }
    \right)^2
  \Bigg].
\end{aligned}
\]
\endgroup
In the small-roundoff regime
\[
  0\le u,\gamma_m,\gamma_s,\frac{4u+3u^2+u^3}{1-u}\le c<1,
  \qquad \sqrt{\frac nm}+t>0,
\]
the component terms have the orders
\[
  \Delta_V=\Theta(\gamma_m+u),
  \qquad
  \zeta(t)
  =
  \Theta\!\left(
    u+\frac{4u+3u^2+u^3}{1-u}
    +\frac{\gamma_m+u}{\sqrt{n/m}+t}
  \right),
\]
with constants depending only on the fixed bound \(c\).  Since all terms are
nonnegative and
\[
  2\zeta+\zeta^2+\gamma_s(1+\zeta)^2
  =
  \Theta(\zeta+\gamma_s)
  \qquad(0\le \zeta,\gamma_s\le c),
\]
the final radius has the asymptotic order
\[
  T_{\rm SRHT}^{\rm fp}(t)
  =
  \Theta\!\left(
    nm\left(\sqrt{\frac nm}+t\right)^2
    \left[
      \gamma_s+u+\frac{4u+3u^2+u^3}{1-u}
      +\frac{\gamma_m+u}{\sqrt{n/m}+t}
    \right]
  \right).
\]
Equivalently,
\[
  T_{\rm SRHT}^{\rm fp}(t)
  =
  \Theta\!\left(
    nm\left(\sqrt{\frac nm}+t\right)^2
      \left(\gamma_s+u+\frac{4u+3u^2+u^3}{1-u}\right)
    +
    nm\left(\sqrt{\frac nm}+t\right)(\gamma_m+u)
  \right).
\]
In the same irreducible variables,
\[
\begin{aligned}
  T_{\rm SRHT}^{\rm fp}(t)
  &=
  \Theta\!\left(
    nm\left(\sqrt{\frac nm}+t\right)^2
    \left(\gamma_s+u+\frac{4u+3u^2+u^3}{1-u}\right)
  \right.
  \\
  &\qquad\left.
    +
    nm\left(\sqrt{\frac nm}+t\right)(\gamma_m+u)
  \right).
\end{aligned}
\]

Assume the exact SRHT preprocessing and uniform-row sample budgets
\[
  m\exp\!\left(-\frac{mt^2}{8}\right)\le\delta_{\rm pre},
  \qquad
  \Phi(\theta,L(t),\eps,s,n)\le\delta_{\rm sample}.
\]
Then the fully computed materialized SRHT Gram satisfies
\[
  \Prob\!\left[
    -(\eps+T_{\rm SRHT}^{\rm fp}(t))\I_n
    \preceq
    \widehat G_{\omega,J}^\rho-\I_n
    \preceq
    (\eps+T_{\rm SRHT}^{\rm fp}(t))\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
No additional perturbation event is used.  The radius depends only on \(u\),
\(\gamma_m\), \(\gamma_s\), \(m,n,s\), the SRHT parameter \(t\), and the
concrete relative denominator error
\(\delta_d=(4u+3u^2+u^3)/(1-u)\).  For fixed \(m,n,s,t\),
\[
  T_{\rm SRHT}^{\rm fp}(t)\longrightarrow 0
  \qquad
  \text{as}\qquad
  u,\gamma_m,\gamma_s,\frac{4u+3u^2+u^3}{1-u}\longrightarrow 0,
\]
so the bound is non-vacuous in the small-roundoff regime.  In the
exact-denominator infrastructure specialization, \(\delta_d=0\); that is not
the selected final concrete denominator routine in this note.
\end{theorem}

\begin{remark}
The previous theorem is an analysis-basis theorem.  It is the right statement
when the exact SRHT subspace-embedding analysis is written for an
orthonormal-column matrix \(U\), but it is not by itself the Algorithm 3
input-matrix theorem.  Algorithm 3 receives \(A\), and the computed product is
\(\fl(\widehat P_\omega A)\), not \(\fl(\widehat P_\omega U)\).
\end{remark}

\begin{theorem}[Fully computed SRHT theorem on the Algorithm 3 input matrix]
Let \(A\in\R^{m\times n}\) be the exact input matrix handed to Algorithm 3.
Assume \(A\ne0\), let \(r=\operatorname{rank}(A)\), and choose exact
analysis-only factors
\[
  U_A\in\R^{m\times r},
  \qquad
  C_A\in\R^{r\times n},
  \qquad
  U_A^TU_A=\I_r,
  \qquad
  A=U_AC_A .
\]
The matrices \(U_A\) and \(C_A\) are exact arithmetic objects used only in the
analysis.  They are not computed by Algorithm 3.  The implemented algorithm
computes with the input matrix \(A\).

Let \(0<\delta_{\rm pre}<m\), \(0\le\delta_{\rm sample}\), and
\(0<\eps<1\).  Set
\[
  t_{\rm pre}=\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}},
  \qquad
  S_A=\sqrt{\frac rm}+t_{\rm pre},
  \qquad
  L_A=mS_A^2 .
\]
Choose the exact sample count \(s\) and an exact Chernoff parameter
\(\theta_A>0\) so that
\[
  \Phi(\theta_A,L_A,\eps,s,r)\le\delta_{\rm sample}.
\]
The choice of \(s\), \(\theta_A\), and the probability laws below is exact
arithmetic; no sampling probability table is computed.

Let \(\mathcal S\in\R^{m\times m}\) be an exact sign-pattern table such that
\[
  H_{ia}=\sqrt{1/m}\,\mathcal S_{ia}
\]
is orthogonal and flat.  Let \(\omega\in\{\pm1\}^m\) be the exact Rademacher
sign vector, and let \(J=(J_1,\ldots,J_s)\) be the exact uniform row-sample
trace.  The concrete computed SRHT path in this theorem is
\[
  \widehat H_{ia}=\fl(\sqrt{1/m})\,\mathcal S_{ia},
  \qquad
  \widehat\omega_a=\fl(\omega_a\cdot1),
  \qquad
  \widehat D_\omega=\diag(\widehat\omega),
\]
\[
  P_\omega=H\diag(\omega),
  \qquad
  \widehat P_\omega=\fl(\widehat H\widehat D_\omega),
  \qquad
  Y_\omega=P_\omega A,
  \qquad
  \widehat Y_\omega=\fl(\widehat P_\omega A).
\]
Here \(P_\omega,Y_\omega\) are exact references, while
\(\widehat P_\omega,\widehat Y_\omega\) are computed floating-point objects.
The stored-sign path displayed here uses \(\fl(\omega_a\cdot1)\); the
formalization also has the analogous add-zero and subtract-zero stored-sign
certificates.

Let the final concrete uniform row-scale denominator be
\[
  d=\sqrt{s/m},
  \qquad
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt m))
  \right).
\]
The value \(\widehat d_\star\) is a computed non-probability quantity, and the
formalized certificate proves
\[
  \widehat d_\star\ne0,
  \qquad
  |\widehat d_\star-d|
  \le
  d\,\frac{4u+3u^2+u^3}{1-u}.
\]
Define
\[
  B_{\omega,J,tj}=\frac{(Y_\omega)_{J_tj}}{d},
  \qquad
  \widetilde B_{\omega,J,tj}=
    \frac{(\widehat Y_\omega)_{J_tj}}{d},
  \qquad
  \widehat B_{\omega,J,tj}=
    \fl\!\left(\frac{(\widehat Y_\omega)_{J_tj}}{\widehat d_\star}\right),
\]
and
\[
  \widehat G_A(\omega,J)
  =
  \fl\!\left(\widehat B_{\omega,J}^{\,T}\widehat B_{\omega,J}\right).
\]

The fully computed perturbation radius is
\[
  \tau_A^{\rm cd}(\omega,J)
  =
  \tau_{\rm den}(\omega,J)
  +
  \tau_{\rm dot}(\omega,J)
  +
  \tau_{\rm prod}(\omega,J).
\]
First define the row-scaling entry budget
\[
  E^{\rm den}_{tj}
  =
  |\widehat B_{\omega,J,tj}|\,u
  +
  \frac{|(\widehat Y_\omega)_{J_tj}|\,d\,
        \frac{4u+3u^2+u^3}{1-u}}
       {|\widehat d_\star|\,d}.
\]
Then
\[
  \tau_{\rm den}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      E^{\rm den}_{tj}|\widehat B_{\omega,J,tk}|
      +
      |\widetilde B_{\omega,J,tj}|E^{\rm den}_{tk}
    \right)_{j,k=1}^n
  \right\|_F
\]
and
\[
  \tau_{\rm dot}(\omega,J)
  =
  \left\|
    \left(
      \gamma_s
      \sum_{t=1}^s
      |\widehat B_{\omega,J,tj}|\,|\widehat B_{\omega,J,tk}|
    \right)_{j,k=1}^n
  \right\|_F .
\]
For the product term, let
\[
  e^H_{ia}=\sqrt{1/m}\,u\,|\mathcal S_{ia}|,
  \qquad
  e^\omega_a=u,
\]
and define the preconditioner-entry budget
\[
\begin{aligned}
  E^P_{\omega,ia}
  &=
  \gamma_m
  \sum_{b=1}^m |\widehat H_{ib}|\,
    |\widehat D_{\omega,ba}|
  +
  \sum_{b=1}^m e^H_{ib}\,|\widehat D_{\omega,ba}|
  +
  \sum_{b=1}^m |H_{ib}|\,e^\omega_b\,{\bf 1}_{b=a}.
\end{aligned}
\]
The entrywise budget for the computed product
\(\widehat Y_\omega=\fl(\widehat P_\omega A)\) is
\[
  E^Y_{\omega,ij}
  =
  \gamma_m\sum_{a=1}^m
    |(\widehat P_\omega)_{ia}|\,|A_{aj}|
  +
  \sum_{a=1}^m E^P_{\omega,ia}|A_{aj}|,
\]
and
\[
  \tau_{\rm prod}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{E^Y_{\omega,J_tj}}{d}
        |\widetilde B_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{E^Y_{\omega,J_tk}}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
Then the fully computed Algorithm 3 sampled input Gram satisfies
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_A^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_A^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
There is no extra perturbation event, no extra existence hypothesis, and no
\(\delta_{\rm comp}\) in this final statement.  All probabilities are exact
Rademacher and exact uniform-row probabilities.  All non-probability computed
objects on this SRHT path are charged in \(\tau_A^{\rm cd}\).
\end{theorem}

\begin{theorem}[Concrete Sylvester/Walsh FHT specialization]
Fix \(p\in\mathbb N\) and set \(m=2^p\).  Define the exact
Sylvester/Walsh sign table
\[
  S_p(i,a)=
  \begin{cases}
    -1, & \text{if the bit parity of }i\wedge a\text{ is odd},\\
     1, & \text{otherwise,}
  \end{cases}
\]
and define the normalized exact table
\[
  H_p(i,a)=\sqrt{1/m}\,S_p(i,a).
\]
The formalized result proves from this definition that \(H_p^TH_p=I_m\) and
\((H_p)_{ia}^2=1/m\).  Thus these are exact arithmetic facts about the
generated bit table, not hypotheses supplied to the final theorem.

Let the exact Algorithm 3 input have the analysis factorization
\[
  A=U_AC_A,\qquad U_A^TU_A=I_r .
\]
The matrices \(U_A\) and \(C_A\) are exact analysis-only witnesses.  The
implemented computation uses \(A\) directly.  For an exact Rademacher sign
vector \(\omega\), the concrete computed preconditioner is obtained by storing
the realized signs with the rounded multiply-one copy path, applying the
generated Sylvester/Walsh FHT butterfly schedule, and rounding the
normalization by \(\fl(\sqrt{1/m})\).  It then computes
\[
  \widehat Y_\omega=\fl(\widehat P_\omega A).
\]
For the downstream uniform row sketch, the concrete computed denominator is
\[
  d=\sqrt{s/m},\qquad
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt m))
  \right),
\]
with the same certified radius
\[
  |\widehat d_\star-d|
  \le
  d\,\frac{4u+3u^2+u^3}{1-u}.
\]
Let \(\tau_{A,{\rm syl}}^{\rm cd}(\omega,J)\) be the fully expanded radius
\(\tau_A^{\rm cd}(\omega,J)\) from the preceding theorem after substituting
\(\mathcal S=S_p\), \(H=H_p\), \(m=2^p\), and the generated-FHT stored-sign
preconditioner just described.

With
\[
  t_{\rm pre}=\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}},
  \qquad
  S_A=\sqrt{\frac rm}+t_{\rm pre},
  \qquad
  L_A=mS_A^2,
\]
and with the same exact sample-budget condition
\[
  \Phi(\theta_A,L_A,\eps,s,r)\le\delta_{\rm sample},
\]
the computed sampled input Gram satisfies
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_{A,{\rm syl}}^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_{A,{\rm syl}}^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
The exact objects are \(A\), \(U_A\), \(C_A\), \(S_p\), \(H_p\), and the
Rademacher and uniform-row laws.  The computed objects are the stored sign
vector, generated FHT butterflies, rounded normalization, \(\widehat P_\omega\),
\(\widehat Y_\omega\), \(\widehat d_\star\), sampled row divisions, and Gram
dot products.  No external orthogonality witness, flatness witness,
perturbation event, or extra existence hypothesis appears.
\end{theorem}

\begin{corollary}[Stored-input generated-FHT endpoints]
Keep the hypotheses and source sample-budget condition of the preceding
Sylvester/Walsh specialization.  Let
\[
  P_\omega=H_p\diag(\omega),
  \qquad
  Y_\omega=P_\omega A,
  \qquad
  d=\sqrt{s/m}.
\]
These are exact analysis references.  The exact matrices \(U_A\), \(C_A\),
\(A=U_AC_A\), \(H_p\), and \(P_\omega\) are not computed in this corollary,
and the Rademacher and uniform-row laws are exact mathematical laws.

Choose one concrete input-storage mode
\[
  \rho\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}.
\]
The implemented input-storage step is
\[
  \widehat A^{\rm in}_{aj}=
  \begin{cases}
    \fl_{\rm mul}(A_{aj},1),&\rho=\mathrm{mul1},\\
    \fl_{\rm add}(A_{aj},0),&\rho=\mathrm{add0},\\
    \fl_{\rm sub}(A_{aj},0),&\rho=\mathrm{sub0},
  \end{cases}
  \qquad
  E^A_{aj}=u|A_{aj}|,
\]
so
\[
  |\widehat A^{\rm in}_{aj}-A_{aj}|\le E^A_{aj}.
\]
This is the only new computed object relative to the preceding
generated-FHT endpoint.  The stored-sign generated-FHT preconditioner
\(\widehat P_\omega\), its exact reference \(P_\omega\), and its entrywise
budget \(E^P_{\omega,ia}\) are the same objects used above:
\[
  |(\widehat P_\omega)_{ia}-(P_\omega)_{ia}|
  \le E^P_{\omega,ia}.
\]
The implementation then forms the computed preconditioned input
\[
  \widehat Y^{\rm in}_{\omega}
  =
  \fl(\widehat P_\omega \widehat A^{\rm in}).
\]
The fully expanded entrywise product budget is
\[
  E^{Y,{\rm in}}_{\omega,ij}
  =
  \gamma_m\sum_{a=1}^m
    |(\widehat P_\omega)_{ia}|\,|\widehat A^{\rm in}_{aj}|
  +
  \sum_{a=1}^m E^P_{\omega,ia}|\widehat A^{\rm in}_{aj}|
  +
  \sum_{a=1}^m |(P_\omega)_{ia}|\,u|A_{aj}|.
\]
The last summand is the exact input-storage contribution; it is not a
probability term and not a hidden certificate.

Use the same computed denominator
\[
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt m))
  \right),
  \qquad
  |\widehat d_\star-d|
  \le
  d\,\delta_d,
  \qquad
  \delta_d=\frac{4u+3u^2+u^3}{1-u}.
\]
For sampled rows \(J_1,\ldots,J_s\), define
\[
  B_{\omega,J,tj}=\frac{(Y_\omega)_{J_tj}}{d},
  \qquad
  \widetilde B^{{\rm in}}_{\omega,J,tj}
  =
  \frac{(\widehat Y^{\rm in}_\omega)_{J_tj}}{d},
  \qquad
  \widehat B^{{\rm in}}_{\omega,J,tj}
  =
  \fl\!\left(
    \frac{(\widehat Y^{\rm in}_\omega)_{J_tj}}{\widehat d_\star}
  \right).
\]
The computed sampled Gram is
\[
  \widehat G_A^{\rm in}(\omega,J)
  =
  \fl\!\left(
    (\widehat B^{{\rm in}}_{\omega,J})^T
    \widehat B^{{\rm in}}_{\omega,J}
  \right).
\]
The row-scaling budget is
\[
  E^{{\rm den},{\rm in}}_{tj}
  =
  |\widehat B^{{\rm in}}_{\omega,J,tj}|\,u
  +
  \frac{|(\widehat Y^{\rm in}_\omega)_{J_tj}|\,d\,\delta_d}
       {|\widehat d_\star|\,d}.
\]
Define
\[
  \tau_{{\rm den},{\rm in}}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      E^{{\rm den},{\rm in}}_{tj}
      |\widehat B^{{\rm in}}_{\omega,J,tk}|
      +
      |\widetilde B^{{\rm in}}_{\omega,J,tj}|
      E^{{\rm den},{\rm in}}_{tk}
    \right)_{j,k=1}^n
  \right\|_F,
\]
\[
  \tau_{{\rm dot},{\rm in}}(\omega,J)
  =
  \left\|
    \left(
      \gamma_s
      \sum_{t=1}^s
      |\widehat B^{{\rm in}}_{\omega,J,tj}|\,
      |\widehat B^{{\rm in}}_{\omega,J,tk}|
    \right)_{j,k=1}^n
  \right\|_F,
\]
and
\[
  \tau_{{\rm prod},{\rm in}}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{E^{Y,{\rm in}}_{\omega,J_tj}}{d}
        |\widetilde B^{{\rm in}}_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{E^{Y,{\rm in}}_{\omega,J_tk}}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
The final stored-input radius is
\[
  \tau_{A,{\rm in}}^{\rm cd}(\omega,J)
  =
  \tau_{{\rm den},{\rm in}}(\omega,J)
  +
  \tau_{{\rm dot},{\rm in}}(\omega,J)
  +
  \tau_{{\rm prod},{\rm in}}(\omega,J).
\]
Then
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_{A,{\rm in}}^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A^{\rm in}(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_{A,{\rm in}}^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]

The input-storage part of the product radius is exactly
\[
  \Delta_{\rm in}(\omega,J)
  =
  u
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{\sum_{a=1}^m |(P_\omega)_{J_ta}|\,|A_{aj}|}{d}
        |\widetilde B^{{\rm in}}_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{\sum_{a=1}^m |(P_\omega)_{J_ta}|\,|A_{ak}|}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
Thus, for fixed \(m,n,s,p,A,\omega,J\), fixed \(d>0\), and nonzero displayed
coefficient,
\[
  \Delta_{\rm in}(\omega,J)
  =
  \Theta\!\left(
    u
    \left\|
      \left(
        \sum_{t=1}^s
        \frac{\sum_{a=1}^m |(P_\omega)_{J_ta}|\,|A_{aj}|}{d}
          |\widetilde B^{{\rm in}}_{\omega,J,tk}|
        +
        |B_{\omega,J,tj}|
        \frac{\sum_{a=1}^m |(P_\omega)_{J_ta}|\,|A_{ak}|}{d}
      \right)_{j,k=1}^n
    \right\|_F
  \right).
\]
The whole radius has the same non-vacuity property as the preceding
generated-FHT endpoint: for fixed dimensions, fixed exact references, and
sample realizations with \(\widehat d_\star\) bounded away from zero,
\[
  \tau_{A,{\rm in}}^{\rm cd}(\omega,J)\to0
  \quad\text{as}\quad
  u,\gamma_m,\gamma_s,E^P\to0.
\]
\end{corollary}

\begin{corollary}[All-coordinate add-zero FHT writeback specialization]
Keep the notation and hypotheses of the preceding Sylvester/Walsh
specialization.  Define the exact signed-Hadamard preconditioner
\[
  P_\omega=H_p\diag(\omega).
\]
Let \(\mathcal P_p=((q_\ell,r_\ell))_{\ell=1}^{L_p}\) be the deterministic
ordered pair schedule used by the generated Sylvester/Walsh FHT.  Here
\(q_\ell,r_\ell\in\{1,\ldots,m\}\), and \(L_p\) is the number of butterfly
pairs in the schedule.  For the standard radix-two Sylvester schedule,
\(L_p=p2^{p-1}\) when \(p>0\), and \(L_p=0\) when \(p=0\).

For each column \(a\) of the diagonal sign matrix, initialize the exact FHT
input, computed stored input, and entrywise input-error budget by
\[
  x_i^{(0,a)}=\omega_a{\bf 1}_{i=a},\qquad
  \widehat x_i^{(0,a)}
  =
  \begin{cases}
    \fl(\omega_a\cdot 1),& i=a,\\
    0,& i\ne a,
  \end{cases}
  \qquad
  E_i^{(0,a)}=u{\bf 1}_{i=a}.
\]
For \(\ell=1,\ldots,L_p\), write \(q=q_\ell\) and \(r=r_\ell\).  The exact
reference vector \(x^{(\ell,a)}\) is obtained from \(x^{(\ell-1,a)}\) by the
exact butterfly \(x_q+x_r\), \(x_q-x_r\), leaving all other coordinates
unchanged.  The computed pre-writeback vector \(y^{(\ell,a)}\) is
\[
  y_q^{(\ell,a)}
    =\fl(\widehat x_q^{(\ell-1,a)}+\widehat x_r^{(\ell-1,a)}),
  \qquad
  y_r^{(\ell,a)}
    =\fl(\widehat x_q^{(\ell-1,a)}-\widehat x_r^{(\ell-1,a)}),
\]
and \(y_i^{(\ell,a)}=\widehat x_i^{(\ell-1,a)}\) for \(i\notin\{q,r\}\).
Before the explicit copy/writeback, define
\[
  F_i^{(\ell,a)}
  =
  \begin{cases}
    u|\widehat x_q^{(\ell-1,a)}+\widehat x_r^{(\ell-1,a)}|
      +E_q^{(\ell-1,a)}+E_r^{(\ell-1,a)},& i=q,\\
    u|\widehat x_q^{(\ell-1,a)}-\widehat x_r^{(\ell-1,a)}|
      +E_q^{(\ell-1,a)}+E_r^{(\ell-1,a)},& i=r,\\
    E_i^{(\ell-1,a)},& i\notin\{q,r\}.
  \end{cases}
\]
The all-coordinate add-zero implementation stores every post-butterfly
coordinate, including untouched coordinates, by
\[
  \widehat x_i^{(\ell,a)}=\fl(y_i^{(\ell,a)}+0),
  \qquad
  E_i^{(\ell,a)}
    =
    F_i^{(\ell,a)}+u|y_i^{(\ell,a)}|.
\]
The final term \(u|y_i^{(\ell,a)}|\) is precisely the additional
floating-point writeback/copy charge.  It is a computed non-probability
operation; it does not alter the Rademacher or row-sampling law.

Set
\[
  c_p=\sqrt{1/m},\qquad
  \widehat c_p=\fl(\sqrt{1/m}),\qquad
  \eta_p=c_pu .
\]
The computed add-zero FHT preconditioner and its entrywise error budget are
\[
  \widehat P^+_{\omega,ia}
  =
  \fl\!\left(\widehat c_p\,\widehat x_i^{(L_p,a)}\right),
\]
and
\[
  E^{P,+}_{\omega,ia}
  =
  u|\widehat c_p\,\widehat x_i^{(L_p,a)}|
  +
  |\widehat c_p|E_i^{(L_p,a)}
  +
  \eta_p\bigl(|\widehat x_i^{(L_p,a)}|+E_i^{(L_p,a)}\bigr).
\]
Thus
\[
  |\widehat P^+_{\omega,ia}-(P_\omega)_{ia}|
  \le E^{P,+}_{\omega,ia}.
\]

Define the computed left-preconditioned matrix
\[
  \widehat Y^+_{\omega}=\fl(\widehat P^+_{\omega}A)
\]
and the corresponding product budget
\[
  E^{Y,+}_{\omega,ij}
  =
  \gamma_m\sum_{a=1}^m
    |\widehat P^+_{\omega,ia}|\,|A_{aj}|
  +
  \sum_{a=1}^m E^{P,+}_{\omega,ia}|A_{aj}|.
\]
With the same exact \(d=\sqrt{s/m}\) and the same computed
\(\widehat d_\star\), set
\[
  B_{\omega,J,tj}=\frac{(Y_\omega)_{J_tj}}{d},
  \qquad
  \widetilde B^+_{\omega,J,tj}
    =
    \frac{(\widehat Y^+_\omega)_{J_tj}}{d},
  \qquad
  \widehat B^+_{\omega,J,tj}
    =
    \fl\!\left(\frac{(\widehat Y^+_\omega)_{J_tj}}{\widehat d_\star}\right),
\]
and
\[
  \widehat G_A^+(\omega,J)
  =
  \fl\!\left((\widehat B^+_{\omega,J})^T\widehat B^+_{\omega,J}\right).
\]
Let
\[
  \delta_d=\frac{4u+3u^2+u^3}{1-u}.
\]
The row-scaling budget is
\[
  E^{{\rm den},+}_{tj}
  =
  |\widehat B^+_{\omega,J,tj}|\,u
  +
  \frac{|(\widehat Y^+_\omega)_{J_tj}|\,d\,\delta_d}
       {|\widehat d_\star|\,d}.
\]
Define
\[
  \tau_{{\rm den},+}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      E^{{\rm den},+}_{tj}|\widehat B^+_{\omega,J,tk}|
      +
      |\widetilde B^+_{\omega,J,tj}|E^{{\rm den},+}_{tk}
    \right)_{j,k=1}^n
  \right\|_F,
\]
\[
  \tau_{{\rm dot},+}(\omega,J)
  =
  \left\|
    \left(
      \gamma_s
      \sum_{t=1}^s
      |\widehat B^+_{\omega,J,tj}|\,|\widehat B^+_{\omega,J,tk}|
    \right)_{j,k=1}^n
  \right\|_F,
\]
and
\[
  \tau_{{\rm prod},+}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{E^{Y,+}_{\omega,J_tj}}{d}
        |\widetilde B^+_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{E^{Y,+}_{\omega,J_tk}}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
Finally set
\[
  \tau_{A,{\rm syl},+}^{\rm cd}(\omega,J)
  =
  \tau_{{\rm den},+}(\omega,J)
  +
  \tau_{{\rm dot},+}(\omega,J)
  +
  \tau_{{\rm prod},+}(\omega,J).
\]

Under the same exact preprocessing and sample-budget condition as in the
preceding theorem,
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_{A,{\rm syl},+}^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A^+(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_{A,{\rm syl},+}^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
For fixed \(p,m,n,s,A,\omega,J\), the additional writeback terms are finite
sums of factors proportional to \(u\).  In the small-roundoff regime
\(\gamma_m=\Theta(mu)\), \(\gamma_s=\Theta(su)\), and
\(\delta_d=\Theta(u)\), the displayed deterministic radius satisfies
\begin{align*}
  \tau_{A,{\rm syl},+}^{\rm cd}(\omega,J)
  &=
  O\!\Biggl(
    (u+\gamma_m+\gamma_s+\delta_d)
    \Biggl[
      \sum_{i,a}|\widehat x_i^{(L_p,a)}|\|A_{a,*}\|_1 \\
  &\hspace{2.8cm}
      +
      \sum_{\ell=1}^{L_p}\sum_{i,a}
        |y_i^{(\ell,a)}|\|A_{a,*}\|_1
      +
      \sum_{t,j,k}
        |\widehat B^+_{\omega,J,tj}|
        |\widehat B^+_{\omega,J,tk}|
    \Biggr]
  \Biggr),
\end{align*}
with \(\Theta\) of the same expanded expression whenever the bracketed
realized magnitude is bounded above and below by positive constants independent
of \(u\).  In particular,
\(\tau_{A,{\rm syl},+}^{\rm cd}(\omega,J)\to0\) as the roundoff quantities
tend to zero with the dimensions, exact input, and realized randomness fixed.
\end{corollary}

\begin{corollary}[Modified-coordinate add-zero FHT writeback specialization]
Keep the notation and hypotheses of Corollary 17.  The modified-coordinate
writeback implementation uses the same exact \(P_\omega\), the same pair
schedule \(\mathcal P_p=((q_\ell,r_\ell))_{\ell=1}^{L_p}\), and the same
computed pre-writeback vector \(y^{(\ell,a)}\) and pre-writeback budget
\(F^{(\ell,a)}\).  It differs only in the storage step after each butterfly:
for \(q=q_\ell\) and \(r=r_\ell\),
\[
  \widehat x_i^{(\ell,a),\mathrm{mc}}
  =
  \begin{cases}
    \fl(y_i^{(\ell,a),\mathrm{mc}}+0),& i\in\{q,r\},\\
    y_i^{(\ell,a),\mathrm{mc}},& i\notin\{q,r\},
  \end{cases}
\]
and
\[
  E_i^{(\ell,a),\mathrm{mc}}
  =
  \begin{cases}
    F_i^{(\ell,a),\mathrm{mc}}+u|y_i^{(\ell,a),\mathrm{mc}}|,
      & i\in\{q,r\},\\
    F_i^{(\ell,a),\mathrm{mc}},& i\notin\{q,r\}.
  \end{cases}
\]
The superscript \({\rm mc}\) denotes the modified-coordinate recurrence.  Thus
only the two coordinates whose FHT values are changed by the butterfly receive
the extra add-zero copy charge.

With the same
\[
  c_p=\sqrt{1/m},\qquad
  \widehat c_p=\fl(\sqrt{1/m}),\qquad
  \eta_p=c_pu,
\]
define
\[
  \widehat P^{\rm mc}_{\omega,ia}
  =
  \fl\!\left(\widehat c_p\,\widehat x_i^{(L_p,a),\mathrm{mc}}\right)
\]
and
\[
  E^{P,{\rm mc}}_{\omega,ia}
  =
  u|\widehat c_p\,\widehat x_i^{(L_p,a),\mathrm{mc}}|
  +
  |\widehat c_p|E_i^{(L_p,a),\mathrm{mc}}
  +
  \eta_p\bigl(
    |\widehat x_i^{(L_p,a),\mathrm{mc}}|
    +E_i^{(L_p,a),\mathrm{mc}}
  \bigr).
\]
Then
\[
  |\widehat P^{\rm mc}_{\omega,ia}-(P_\omega)_{ia}|
  \le E^{P,{\rm mc}}_{\omega,ia}.
\]
Define
\[
  \widehat Y^{\rm mc}_\omega=\fl(\widehat P^{\rm mc}_\omega A),
\]
\[
  E^{Y,{\rm mc}}_{\omega,ij}
  =
  \gamma_m\sum_{a=1}^m
    |\widehat P^{\rm mc}_{\omega,ia}|\,|A_{aj}|
  +
  \sum_{a=1}^m E^{P,{\rm mc}}_{\omega,ia}|A_{aj}|.
\]
Using the same concrete denominator \(\widehat d_\star\), define
\[
  \widetilde B^{\rm mc}_{\omega,J,tj}
    =
    \frac{(\widehat Y^{\rm mc}_\omega)_{J_tj}}{d},
  \qquad
  \widehat B^{\rm mc}_{\omega,J,tj}
    =
    \fl\!\left(
      \frac{(\widehat Y^{\rm mc}_\omega)_{J_tj}}{\widehat d_\star}
    \right),
\]
and
\[
  \widehat G_A^{\rm mc}(\omega,J)
  =
  \fl\!\left(
    (\widehat B^{\rm mc}_{\omega,J})^T
    \widehat B^{\rm mc}_{\omega,J}
  \right).
\]
Define
\[
  E^{{\rm den},{\rm mc}}_{tj}
  =
  |\widehat B^{\rm mc}_{\omega,J,tj}|\,u
  +
  \frac{|(\widehat Y^{\rm mc}_\omega)_{J_tj}|\,d\,\delta_d}
       {|\widehat d_\star|\,d}.
\]
Then
\[
  \tau_{{\rm den},{\rm mc}}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      E^{{\rm den},{\rm mc}}_{tj}
        |\widehat B^{\rm mc}_{\omega,J,tk}|
      +
      |\widetilde B^{\rm mc}_{\omega,J,tj}|
        E^{{\rm den},{\rm mc}}_{tk}
    \right)_{j,k=1}^n
  \right\|_F,
\]
\[
  \tau_{{\rm dot},{\rm mc}}(\omega,J)
  =
  \left\|
    \left(
      \gamma_s
      \sum_{t=1}^s
      |\widehat B^{\rm mc}_{\omega,J,tj}|\,
      |\widehat B^{\rm mc}_{\omega,J,tk}|
    \right)_{j,k=1}^n
  \right\|_F,
\]
and
\[
  \tau_{{\rm prod},{\rm mc}}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{E^{Y,{\rm mc}}_{\omega,J_tj}}{d}
        |\widetilde B^{\rm mc}_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{E^{Y,{\rm mc}}_{\omega,J_tk}}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
The full modified-coordinate radius is
\[
  \tau_{A,{\rm syl},{\rm mc}}^{\rm cd}(\omega,J)
  =
  \tau_{{\rm den},{\rm mc}}(\omega,J)
  +
  \tau_{{\rm dot},{\rm mc}}(\omega,J)
  +
  \tau_{{\rm prod},{\rm mc}}(\omega,J).
\]

Under the same exact preprocessing and sample-budget condition,
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_{A,{\rm syl},{\rm mc}}^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A^{\rm mc}(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_{A,{\rm syl},{\rm mc}}^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
For fixed \(p,m,n,s,A,\omega,J\), the extra modified-coordinate copy terms are
finite sums of factors \(u|y_i^{(\ell,a),\mathrm{mc}}|\) only over
\(i\in\{q_\ell,r_\ell\}\).  In the same small-roundoff regime,
\[
  \tau_{A,{\rm syl},{\rm mc}}^{\rm cd}(\omega,J)
  =
  O\!\left(
    \tau_{A,{\rm syl},+}^{\rm cd}(\omega,J)
  \right),
\]
and its irreducible copy contribution replaces
\[
  \sum_{\ell=1}^{L_p}\sum_{i,a}
    |y_i^{(\ell,a)}|\|A_{a,*}\|_1
\]
by the smaller realized sum
\[
  \sum_{\ell=1}^{L_p}\sum_{a}
    \left(
      |y_{q_\ell}^{(\ell,a),\mathrm{mc}}|
      +
      |y_{r_\ell}^{(\ell,a),\mathrm{mc}}|
    \right)\|A_{a,*}\|_1 .
\]
Consequently the modified-coordinate radius is non-vacuous and tends to zero
as the roundoff quantities tend to zero with all dimensions, exact inputs, and
realized randomness fixed.
\end{corollary}

\begin{corollary}[All-coordinate multiply-one and subtract-zero FHT writeback specializations]
Keep the notation and hypotheses of the all-coordinate add-zero FHT
specialization.  Let
\[
  \rho\in\{{\rm mul1},{\rm sub0}\}
\]
be a label for the two additional all-coordinate storage routines, and define
the rounded storage map
\[
  c_{\rm mul1}(z)=\fl(z\cdot1),
  \qquad
  c_{\rm sub0}(z)=\fl(z-0).
\]
Both routines use the same exact signed-Hadamard preconditioner
\[
  P_\omega=H_p\diag(\omega),
\]
the same exact Sylvester/Walsh pair schedule
\(\mathcal P_p=((q_\ell,r_\ell))_{\ell=1}^{L_p}\), and the same exact
Rademacher and exact uniform-row probability laws as before.  Their computed
initial diagonal sign columns are still stored by the rounded multiply-one
sign copy:
\[
  x_i^{(0,a),\rho}=\omega_a{\bf 1}_{i=a},\qquad
  \widehat x_i^{(0,a),\rho}
  =
  \begin{cases}
    \fl(\omega_a\cdot1),& i=a,\\
    0,& i\ne a,
  \end{cases}
  \qquad
  E_i^{(0,a),\rho}=u{\bf 1}_{i=a}.
\]

For \(\ell=1,\ldots,L_p\), write \(q=q_\ell\) and \(r=r_\ell\).  The exact
reference vector \(x^{(\ell,a),\rho}\) is obtained by the exact FHT butterfly.
The computed pre-writeback vector is
\[
  y_q^{(\ell,a),\rho}
    =\fl(\widehat x_q^{(\ell-1,a),\rho}
          +\widehat x_r^{(\ell-1,a),\rho}),
  \qquad
  y_r^{(\ell,a),\rho}
    =\fl(\widehat x_q^{(\ell-1,a),\rho}
          -\widehat x_r^{(\ell-1,a),\rho}),
\]
and \(y_i^{(\ell,a),\rho}=\widehat x_i^{(\ell-1,a),\rho}\) for
\(i\notin\{q,r\}\).  Before the explicit copy/writeback, define
\[
  F_i^{(\ell,a),\rho}
  =
  \begin{cases}
    u|\widehat x_q^{(\ell-1,a),\rho}
      +\widehat x_r^{(\ell-1,a),\rho}|
      +E_q^{(\ell-1,a),\rho}+E_r^{(\ell-1,a),\rho},& i=q,\\
    u|\widehat x_q^{(\ell-1,a),\rho}
      -\widehat x_r^{(\ell-1,a),\rho}|
      +E_q^{(\ell-1,a),\rho}+E_r^{(\ell-1,a),\rho},& i=r,\\
    E_i^{(\ell-1,a),\rho},& i\notin\{q,r\}.
  \end{cases}
\]
The all-coordinate \(\rho\)-writeback step stores every coordinate by
\[
  \widehat x_i^{(\ell,a),\rho}=c_\rho(y_i^{(\ell,a),\rho}),
  \qquad
  E_i^{(\ell,a),\rho}
    =
    F_i^{(\ell,a),\rho}+u|y_i^{(\ell,a),\rho}|.
\]
Thus both \(z\mapsto\fl(z\cdot1)\) and \(z\mapsto\fl(z-0)\) are charged as
computed non-probability writebacks, while the random signs and sampled rows
remain exact.

With
\[
  c_p=\sqrt{1/m},\qquad
  \widehat c_p=\fl(\sqrt{1/m}),\qquad
  \eta_p=c_pu,
\]
define
\[
  \widehat P^\rho_{\omega,ia}
  =
  \fl\!\left(\widehat c_p\,\widehat x_i^{(L_p,a),\rho}\right),
\]
\[
  E^{P,\rho}_{\omega,ia}
  =
  u|\widehat c_p\,\widehat x_i^{(L_p,a),\rho}|
  +
  |\widehat c_p|E_i^{(L_p,a),\rho}
  +
  \eta_p\bigl(|\widehat x_i^{(L_p,a),\rho}|
      +E_i^{(L_p,a),\rho}\bigr).
\]
Then
\[
  |\widehat P^\rho_{\omega,ia}-(P_\omega)_{ia}|
  \le E^{P,\rho}_{\omega,ia}.
\]
Define
\[
  \widehat Y^\rho_\omega=\fl(\widehat P^\rho_\omega A),
  \qquad
  E^{Y,\rho}_{\omega,ij}
  =
  \gamma_m\sum_{a=1}^m
    |\widehat P^\rho_{\omega,ia}|\,|A_{aj}|
  +
  \sum_{a=1}^m E^{P,\rho}_{\omega,ia}|A_{aj}|.
\]
Using the same exact denominator \(d=\sqrt{s/m}\), the same computed
\(\widehat d_\star\), and the same
\[
  \delta_d=\frac{4u+3u^2+u^3}{1-u},
\]
define
\[
  \widetilde B^\rho_{\omega,J,tj}
    =
    \frac{(\widehat Y^\rho_\omega)_{J_tj}}{d},
  \qquad
  \widehat B^\rho_{\omega,J,tj}
    =
    \fl\!\left(
      \frac{(\widehat Y^\rho_\omega)_{J_tj}}{\widehat d_\star}
    \right),
\]
\[
  \widehat G_A^\rho(\omega,J)
  =
  \fl\!\left((\widehat B^\rho_{\omega,J})^T
             \widehat B^\rho_{\omega,J}\right),
\]
and
\[
  E^{{\rm den},\rho}_{tj}
  =
  |\widehat B^\rho_{\omega,J,tj}|\,u
  +
  \frac{|(\widehat Y^\rho_\omega)_{J_tj}|\,d\,\delta_d}
       {|\widehat d_\star|\,d}.
\]
The denominator, dot-product, and preconditioned-product contributions are
\[
  \tau_{{\rm den},\rho}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      E^{{\rm den},\rho}_{tj}
        |\widehat B^\rho_{\omega,J,tk}|
      +
      |\widetilde B^\rho_{\omega,J,tj}|
        E^{{\rm den},\rho}_{tk}
    \right)_{j,k=1}^n
  \right\|_F,
\]
\[
  \tau_{{\rm dot},\rho}(\omega,J)
  =
  \left\|
    \left(
      \gamma_s\sum_{t=1}^s
      |\widehat B^\rho_{\omega,J,tj}|\,
      |\widehat B^\rho_{\omega,J,tk}|
    \right)_{j,k=1}^n
  \right\|_F,
\]
and
\[
  \tau_{{\rm prod},\rho}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{E^{Y,\rho}_{\omega,J_tj}}{d}
        |\widetilde B^\rho_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{E^{Y,\rho}_{\omega,J_tk}}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
Set
\[
  \tau_{A,{\rm syl},\rho}^{\rm cd}(\omega,J)
  =
  \tau_{{\rm den},\rho}(\omega,J)
  +
  \tau_{{\rm dot},\rho}(\omega,J)
  +
  \tau_{{\rm prod},\rho}(\omega,J).
\]
Under the same exact preprocessing and sample-budget condition,
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_{A,{\rm syl},\rho}^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A^\rho(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_{A,{\rm syl},\rho}^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]

For fixed \(p,m,n,s,A,\omega,J\), the irreducible all-coordinate copy
contribution is
\[
  \sum_{\ell=1}^{L_p}\sum_{i,a}
    |y_i^{(\ell,a),\rho}|\|A_{a,*}\|_1 .
\]
In the small-roundoff regime
\(\gamma_m=\Theta(mu)\), \(\gamma_s=\Theta(su)\), and
\(\delta_d=\Theta(u)\),
\begin{align*}
  \tau_{A,{\rm syl},\rho}^{\rm cd}(\omega,J)
  &=
  O\!\Biggl(
    (u+\gamma_m+\gamma_s+\delta_d)
    \Biggl[
      \sum_{i,a}|\widehat x_i^{(L_p,a),\rho}|\|A_{a,*}\|_1\\
  &\hspace{2.8cm}
      +
      \sum_{\ell=1}^{L_p}\sum_{i,a}
        |y_i^{(\ell,a),\rho}|\|A_{a,*}\|_1
      +
      \sum_{t,j,k}
        |\widehat B^\rho_{\omega,J,tj}|
        |\widehat B^\rho_{\omega,J,tk}|
    \Biggr]
  \Biggr).
\end{align*}
The same expression is a \(\Theta\)-order description whenever the bracketed
realized magnitude is bounded above and below by positive constants
independent of \(u\).  Consequently both \({\rm mul1}\) and \({\rm sub0}\)
radii are non-vacuous and tend to zero as the roundoff quantities tend to zero
with all dimensions, exact inputs, and realized randomness fixed.
\end{corollary}

\begin{corollary}[Modified-coordinate multiply-one and subtract-zero FHT writeback specializations]
Keep the notation and hypotheses of the modified-coordinate add-zero
specialization and the all-coordinate \({\rm mul1}/{\rm sub0}\)
specialization.  Let
\[
  \rho\in\{{\rm mul1},{\rm sub0}\},
  \qquad
  c_{\rm mul1}(z)=\fl(z\cdot1),
  \qquad
  c_{\rm sub0}(z)=\fl(z-0).
\]
The exact signed-Hadamard preconditioner is still
\[
  P_\omega=H_p\diag(\omega),
\]
and the pair schedule is still
\[
  \mathcal P_p=((q_\ell,r_\ell))_{\ell=1}^{L_p}.
\]
For each column \(a\), initialize
\[
  x_i^{(0,a),{\rm mc},\rho}=\omega_a{\bf 1}_{i=a},\qquad
  \widehat x_i^{(0,a),{\rm mc},\rho}
  =
  \begin{cases}
    \fl(\omega_a\cdot1),& i=a,\\
    0,& i\ne a,
  \end{cases}
  \qquad
  E_i^{(0,a),{\rm mc},\rho}=u{\bf 1}_{i=a}.
\]
For the \(\ell\)-th pair, write \(q=q_\ell\) and \(r=r_\ell\).  The exact
reference vector \(x^{(\ell,a),{\rm mc},\rho}\) is obtained by the exact FHT
butterfly.  The computed pre-writeback vector is
\[
  y_q^{(\ell,a),{\rm mc},\rho}
    =
    \fl(\widehat x_q^{(\ell-1,a),{\rm mc},\rho}
        +\widehat x_r^{(\ell-1,a),{\rm mc},\rho}),
\]
\[
  y_r^{(\ell,a),{\rm mc},\rho}
    =
    \fl(\widehat x_q^{(\ell-1,a),{\rm mc},\rho}
        -\widehat x_r^{(\ell-1,a),{\rm mc},\rho}),
\]
and \(y_i^{(\ell,a),{\rm mc},\rho}
=\widehat x_i^{(\ell-1,a),{\rm mc},\rho}\) for \(i\notin\{q,r\}\).
Before the explicit modified-coordinate writeback, define
\[
  F_i^{(\ell,a),{\rm mc},\rho}
  =
  \begin{cases}
    u|\widehat x_q^{(\ell-1,a),{\rm mc},\rho}
      +\widehat x_r^{(\ell-1,a),{\rm mc},\rho}|
      +E_q^{(\ell-1,a),{\rm mc},\rho}
      +E_r^{(\ell-1,a),{\rm mc},\rho},& i=q,\\
    u|\widehat x_q^{(\ell-1,a),{\rm mc},\rho}
      -\widehat x_r^{(\ell-1,a),{\rm mc},\rho}|
      +E_q^{(\ell-1,a),{\rm mc},\rho}
      +E_r^{(\ell-1,a),{\rm mc},\rho},& i=r,\\
    E_i^{(\ell-1,a),{\rm mc},\rho},& i\notin\{q,r\}.
  \end{cases}
\]
The modified-coordinate \(\rho\)-writeback stores only the two butterfly
outputs:
\[
  \widehat x_i^{(\ell,a),{\rm mc},\rho}
  =
  \begin{cases}
    c_\rho(y_i^{(\ell,a),{\rm mc},\rho}),& i\in\{q,r\},\\
    y_i^{(\ell,a),{\rm mc},\rho},& i\notin\{q,r\},
  \end{cases}
\]
\[
  E_i^{(\ell,a),{\rm mc},\rho}
  =
  \begin{cases}
    F_i^{(\ell,a),{\rm mc},\rho}
      +u|y_i^{(\ell,a),{\rm mc},\rho}|,& i\in\{q,r\},\\
    F_i^{(\ell,a),{\rm mc},\rho},& i\notin\{q,r\}.
  \end{cases}
\]
Thus \(z\mapsto\fl(z\cdot1)\) and \(z\mapsto\fl(z-0)\) are charged only on
modified coordinates; untouched coordinates carry their prior propagated
error without a writeback term.

With
\[
  c_p=\sqrt{1/m},\qquad
  \widehat c_p=\fl(\sqrt{1/m}),\qquad
  \eta_p=c_pu,
\]
define
\[
  \widehat P^{{\rm mc},\rho}_{\omega,ia}
  =
  \fl\!\left(
    \widehat c_p\,\widehat x_i^{(L_p,a),{\rm mc},\rho}
  \right),
\]
\[
  E^{P,{\rm mc},\rho}_{\omega,ia}
  =
  u|\widehat c_p\,\widehat x_i^{(L_p,a),{\rm mc},\rho}|
  +
  |\widehat c_p|E_i^{(L_p,a),{\rm mc},\rho}
  +
  \eta_p\bigl(
    |\widehat x_i^{(L_p,a),{\rm mc},\rho}|
    +E_i^{(L_p,a),{\rm mc},\rho}
  \bigr).
\]
Then
\[
  |\widehat P^{{\rm mc},\rho}_{\omega,ia}-(P_\omega)_{ia}|
  \le E^{P,{\rm mc},\rho}_{\omega,ia}.
\]
Set
\[
  \widehat Y^{{\rm mc},\rho}_\omega
  =
  \fl(\widehat P^{{\rm mc},\rho}_\omega A),
\]
\[
  E^{Y,{\rm mc},\rho}_{\omega,ij}
  =
  \gamma_m\sum_{a=1}^m
    |\widehat P^{{\rm mc},\rho}_{\omega,ia}|\,|A_{aj}|
  +
  \sum_{a=1}^m E^{P,{\rm mc},\rho}_{\omega,ia}|A_{aj}|.
\]
Using the same \(d=\sqrt{s/m}\), \(\widehat d_\star\), and
\(\delta_d=(4u+3u^2+u^3)/(1-u)\), define
\[
  \widetilde B^{{\rm mc},\rho}_{\omega,J,tj}
    =
    \frac{(\widehat Y^{{\rm mc},\rho}_\omega)_{J_tj}}{d},
  \qquad
  \widehat B^{{\rm mc},\rho}_{\omega,J,tj}
    =
    \fl\!\left(
      \frac{(\widehat Y^{{\rm mc},\rho}_\omega)_{J_tj}}
           {\widehat d_\star}
    \right),
\]
\[
  \widehat G_A^{{\rm mc},\rho}(\omega,J)
  =
  \fl\!\left(
    (\widehat B^{{\rm mc},\rho}_{\omega,J})^T
    \widehat B^{{\rm mc},\rho}_{\omega,J}
  \right).
\]
Let
\[
  E^{{\rm den},{\rm mc},\rho}_{tj}
  =
  |\widehat B^{{\rm mc},\rho}_{\omega,J,tj}|\,u
  +
  \frac{|(\widehat Y^{{\rm mc},\rho}_\omega)_{J_tj}|\,d\,\delta_d}
       {|\widehat d_\star|\,d}.
\]
Define
\[
  \tau_{{\rm den},{\rm mc},\rho}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      E^{{\rm den},{\rm mc},\rho}_{tj}
        |\widehat B^{{\rm mc},\rho}_{\omega,J,tk}|
      +
      |\widetilde B^{{\rm mc},\rho}_{\omega,J,tj}|
        E^{{\rm den},{\rm mc},\rho}_{tk}
    \right)_{j,k=1}^n
  \right\|_F,
\]
\[
  \tau_{{\rm dot},{\rm mc},\rho}(\omega,J)
  =
  \left\|
    \left(
      \gamma_s\sum_{t=1}^s
      |\widehat B^{{\rm mc},\rho}_{\omega,J,tj}|\,
      |\widehat B^{{\rm mc},\rho}_{\omega,J,tk}|
    \right)_{j,k=1}^n
  \right\|_F,
\]
and
\[
  \tau_{{\rm prod},{\rm mc},\rho}(\omega,J)
  =
  \left\|
    \left(
      \sum_{t=1}^s
      \frac{E^{Y,{\rm mc},\rho}_{\omega,J_tj}}{d}
        |\widetilde B^{{\rm mc},\rho}_{\omega,J,tk}|
      +
      |B_{\omega,J,tj}|
      \frac{E^{Y,{\rm mc},\rho}_{\omega,J_tk}}{d}
    \right)_{j,k=1}^n
  \right\|_F .
\]
The full modified-coordinate \(\rho\)-radius is
\[
  \tau_{A,{\rm syl},{\rm mc},\rho}^{\rm cd}(\omega,J)
  =
  \tau_{{\rm den},{\rm mc},\rho}(\omega,J)
  +
  \tau_{{\rm dot},{\rm mc},\rho}(\omega,J)
  +
  \tau_{{\rm prod},{\rm mc},\rho}(\omega,J).
\]
Under the same exact preprocessing and sample-budget condition,
\[
  \Prob\!\left[
    (1-\eps)A^TA-\tau_{A,{\rm syl},{\rm mc},\rho}^{\rm cd}(\omega,J)\I_n
    \preceq
    \widehat G_A^{{\rm mc},\rho}(\omega,J)
    \preceq
    (1+\eps)A^TA+\tau_{A,{\rm syl},{\rm mc},\rho}^{\rm cd}(\omega,J)\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]

For fixed \(p,m,n,s,A,\omega,J\), the modified-coordinate copy contribution is
\[
  \sum_{\ell=1}^{L_p}\sum_a
  \left(
    |y_{q_\ell}^{(\ell,a),{\rm mc},\rho}|
    +
    |y_{r_\ell}^{(\ell,a),{\rm mc},\rho}|
  \right)\|A_{a,*}\|_1 .
\]
In the small-roundoff regime
\(\gamma_m=\Theta(mu)\), \(\gamma_s=\Theta(su)\), and
\(\delta_d=\Theta(u)\),
\begin{align*}
  \tau_{A,{\rm syl},{\rm mc},\rho}^{\rm cd}(\omega,J)
  &=
  O\!\Biggl(
    (u+\gamma_m+\gamma_s+\delta_d)
    \Biggl[
      \sum_{i,a}
        |\widehat x_i^{(L_p,a),{\rm mc},\rho}|\|A_{a,*}\|_1\\
  &\hspace{2.7cm}
      +
      \sum_{\ell=1}^{L_p}\sum_a
        \left(
          |y_{q_\ell}^{(\ell,a),{\rm mc},\rho}|
          +
          |y_{r_\ell}^{(\ell,a),{\rm mc},\rho}|
        \right)\|A_{a,*}\|_1\\
  &\hspace{2.7cm}
      +
      \sum_{t,j,k}
        |\widehat B^{{\rm mc},\rho}_{\omega,J,tj}|
        |\widehat B^{{\rm mc},\rho}_{\omega,J,tk}|
    \Biggr]
  \Biggr).
\end{align*}
The same expression is a \(\Theta\)-order description whenever the bracketed
realized magnitude is bounded above and below by positive constants
independent of \(u\).  Consequently both modified-coordinate \({\rm mul1}\)
and modified-coordinate \({\rm sub0}\) radii are non-vacuous and tend to zero
as the roundoff quantities tend to zero with all dimensions, exact inputs, and
realized randomness fixed.

For the modeled functional FHT schedules, the formalized same-stage
no-alias/order facts show that distinct generated butterfly pairs commute for
the rounded base update and for all three modified-coordinate writeback
routines.  These facts justify reordering distinct pairs inside one
generated stage for this model; they do not assert arbitrary in-place,
vectorized, or overwrite-array semantics.  The same certificates are also
specialized to the concrete Sylvester/Walsh stage list
\(\operatorname{Pairs}_{\rm syl}(p,r)\), so the \(2^p\)-dimensional generated
stage interface can be used directly without unfolding to a generic stride
schedule.
The matching no-touch facts for the rounded base schedule and the three
modified-coordinate writeback schedules say that any coordinate outside every
scheduled pair is returned unchanged.  This is why the
modified-coordinate copy contribution appears only on pair outputs; the
statement is not claimed for all-coordinate writeback routines, which rewrite
every coordinate by design.
The corresponding propagated-budget certificates are also proved: on those
same untouched coordinates, the base rounded budget and the three
modified-coordinate budgets remain exactly equal to the incoming radius \(E_i\).
The same value and propagated-budget certificates are specialized to the
concrete Sylvester/Walsh generated interfaces: the full generated schedule
\(\operatorname{Pairs}_{\rm syl}(p)\) and a single generated stage
\(\operatorname{Pairs}_{\rm syl}(p,r)\).  Thus, whenever a coordinate is outside
every pair in the relevant generated list, the full or one-stage rounded base
schedule and the three modified-coordinate schedules return the incoming value,
and their propagated budgets return exactly the incoming radius.  This adds no
probability-law term and no additional roundoff radius; it is a concrete
interface wrapper for the already charged functional schedules.
\end{corollary}

\begin{corollary}[Readable deterministic cap for computed SRHT on the Algorithm 3 input]
Let \(A\in\R^{m\times n}\) be the exact input matrix handed to Algorithm 3.
Let \(0<\delta_{\rm pre}<m\) be the target SRHT preprocessing failure budget.
Let \(0<\delta_{\rm sample}<1\) be the target uniform-row sampling failure
budget.  Fix an exact distortion tolerance \(0<\eps<1\), and set
\[
  t_{\rm pre}
  =
  \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}} .
\]
This is the standard logarithmic choice from Tropp's SRHT row-norm analysis
\cite{Tropp2011SRHT}.  It makes
\[
  m\exp\!\left(-\frac{m t_{\rm pre}^2}{8}\right)
  =
  \delta_{\rm pre}.
\]
Assume first that \(A\ne0\).  Let
\[
  r=\operatorname{rank}(A)
\]
and choose exact analysis-only matrices \(U_A\in\R^{m\times r}\) and
\(C_A\in\R^{r\times n}\) such that
\[
  U_A^TU_A=\I_r,
  \qquad
  A=U_AC_A .
\]
The matrix \(U_A\) is not computed by the algorithm in this theorem.  It is
only the exact column-space basis used to state the SRHT probability event.
This corollary is the fixed-radius readable cap obtained by bounding the
sample-dependent radius \(\tau_A^{\rm cd}(\omega,J)\) from the preceding theorem
on the same exact SRHT row-norm event.

Let \(\mathcal S\in\R^{m\times m}\) be an exact sign-pattern table with
\(\mathcal S_{ia}^2=1\), and let
\(\omega\in\{\pm1\}^m\) be the exact realized Rademacher sign vector.  Store
the signs by one of the rounded copy routines
\(\fl(\omega_a\cdot1)\), \(\fl(\omega_a+0)\), or \(\fl(\omega_a-0)\), and
write the stored signs as \(\widehat\omega^\rho\), so that
\[
  |\widehat\omega^\rho_a-\omega_a|\le u .
\]
Define
\[
  c_m=\sqrt{1/m},\qquad \widehat c_m=\fl(\sqrt{1/m}),
\]
\[
  H_{ia}=c_m\mathcal S_{ia},
  \qquad
  \widehat H_{ia}=\widehat c_m\mathcal S_{ia},
\]
\[
  D_\omega=\diag(\omega),\qquad
  \widehat D_\omega^\rho=\diag(\widehat\omega^\rho),
\]
and
\[
  P_\omega=HD_\omega,\qquad
  \widehat P_\omega^\rho=\fl(\widehat H\widehat D_\omega^\rho).
\]
Then \(P_\omega\) is exact arithmetic and orthogonal, while
\(\widehat P_\omega^\rho\) is the computed materialized preconditioner.  The
computed preconditioner is charged by the rounded-scale, stored-sign, and
rounded \(H\diag(\omega)\) product budgets displayed in the preceding theorem.

Define the exact and computed Algorithm 3 preconditioned matrices
\[
  Y_\omega=P_\omega A,
  \qquad
  \widehat Y_\omega^\rho=\fl(\widehat P_\omega^\rho A).
\]
For every row \(i\) and column \(j\),
\[
  |\widehat Y^\rho_{\omega,ij}-(Y_\omega)_{ij}|
  \le
  \kappa_m\NormOne{A_{*j}} .
\]
Thus the preconditioned matrix bound is for the actual input matrix \(A\), not
for an assumed orthonormal input.

Define the column-size parameters
\[
  a_1=\max_{1\le j\le n}\NormOne{A_{*j}},
  \qquad
  a_2=\max_{1\le j\le n}\Norm{A_{*j}},
  \qquad
  \mu_A=\frac{a_1}{\sqrt m\,a_2}.
\]
Since \(A\ne0\), \(a_2>0\); also \(0<\mu_A\le1\).  Define the
rank-sensitive logarithmic SRHT radius
\[
  S_{A,\log}(\delta_{\rm pre})
  =
  \sqrt{\frac rm}
  +
  \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}},
  \qquad
  L_{A,\log}(\delta_{\rm pre})
  =
  m\,S_{A,\log}(\delta_{\rm pre})^2,
\]
choose the exact row-sample count
\[
  s
  =
  s_{\min}\!\left(
    L_{A,\log}(\delta_{\rm pre}),
    \eps,
    \delta_{\rm sample};
    r
  \right),
\]
and choose any exact Chernoff parameter \(\theta_A>0\) witnessing this
definition, so that
\[
  \Phi(\theta_A,L_{A,\log}(\delta_{\rm pre}),\eps,s,r)
  \le\delta_{\rm sample}.
\]
For a standard constant-distortion specialization, take \(\eps=1/2\); then
\[
  s
  =
  s_{\min}\!\left(
    L_{A,\log}(\delta_{\rm pre}),
    1/2,
    \delta_{\rm sample};
    r
  \right),
\]
and the literature-order sufficient scaling is
\[
  s
  =
  O\!\left(
    \left(
      \sqrt r+\sqrt{8\log(m/\delta_{\rm pre})}
    \right)^2
    \log\frac{r}{\delta_{\rm sample}}
  \right).
\]
For symbolic \(0<\eps<1\), the same rule gives
\[
  s
  =
  O\!\left(
    \frac{
      \left(
        \sqrt r+\sqrt{8\log(m/\delta_{\rm pre})}
      \right)^2
    }{\eps^2}
    \log\frac{r}{\delta_{\rm sample}}
  \right).
\]
This is an exact parameter-selection step, not a floating-point computation.
Define the explicit preconditioner-product roundoff scalar
\[
  K_m
  =
  \gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u .
\]
Equivalently, \(\kappa_m=K_m/\sqrt m\).  Let
\[
  d=\sqrt{s/m},
  \qquad
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt m))
  \right),
\]
and
\[
  \delta_d=\frac{4u+3u^2+u^3}{1-u},
  \qquad 0\le\delta_d<1 .
\]
The denominator certificate proves
\(\widehat d_\star\ne0\) and
\(|\widehat d_\star-d|\le d\,\delta_d\).
On the exact SRHT row-norm event for \(U_A\), every exact scaled input-sketch
entry satisfies
\[
  \left|
    \frac{(Y_\omega)_{J_tj}}{d}
  \right|
  \le
  \sqrt{\frac ms}\,S_{A,\log}(\delta_{\rm pre})\,a_2 .
\]
Here the column norm of \(C_A\) equals the column norm of \(A\), because
\(U_A^TU_A=\I_r\) and \(A=U_AC_A\).
Every corresponding computed scaled entry differs from it by at most the same
quantity times
\[
  \zeta_{A,\log}(\delta_{\rm pre})
  =
  \frac{
    u+\delta_d+
    (1+u)\mu_AK_m/S_{A,\log}(\delta_{\rm pre})
  }{1-\delta_d}.
\]

Let
\[
  B_{\omega,J,tj}=\frac{(Y_\omega)_{J_tj}}{d},
  \qquad
  \widehat B^\rho_{\omega,J,tj}
  =
  \fl\!\left(\widehat Y^\rho_{\omega,J_tj}/\widehat d_\star\right).
\]
The exact sampled input Gram and computed sampled input Gram are
\[
  G_A(\omega,J)=B_{\omega,J}^{\,T}B_{\omega,J},
  \qquad
  \widehat G_A^\rho(\omega,J)
  =
  \fl\!\left((\widehat B^\rho_{\omega,J})^T
             \widehat B^\rho_{\omega,J}\right).
\]
Conditioned on \(\omega\), the exact row sample is unbiased:
\[
  \Exp_J[G_A(\omega,J)\mid\omega]
  =
  (P_\omega A)^T(P_\omega A)
  =
  A^TA .
\]
This identity is exact arithmetic; it is not computed by the algorithm.

Define the final floating-point radius by the fully expanded formula
\[
\begin{aligned}
  T_{A,\log}^{\rm fp}(\delta_{\rm pre})
  &=
  nm
  \left(
    \sqrt{\frac rm}
    +
    \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
  \right)^2
  \\
  &\quad\times
  \left(\max_{1\le j\le n}\Norm{A_{*j}}\right)^2
  \\
  &\quad\times
  \Bigg[
    2
    \frac{
      u+\frac{4u+3u^2+u^3}{1-u}
      +
      (1+u)
      \frac{\max_{1\le j\le n}\NormOne{A_{*j}}}
           {\sqrt m\,\max_{1\le j\le n}\Norm{A_{*j}}}
      \frac{\gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u}
           {
             \sqrt{r/m}
             +
             \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
           }
    }{
      1-\frac{4u+3u^2+u^3}{1-u}
    }
  \\
  &\quad+
    \left(
    \frac{
      u+\frac{4u+3u^2+u^3}{1-u}
      +
      (1+u)
      \frac{\max_{1\le j\le n}\NormOne{A_{*j}}}
           {\sqrt m\,\max_{1\le j\le n}\Norm{A_{*j}}}
      \frac{\gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u}
           {
             \sqrt{r/m}
             +
             \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
           }
    }{
      1-\frac{4u+3u^2+u^3}{1-u}
    }
    \right)^2
  \\
  &\quad+
    \gamma_s
    \left(
      1+
      \frac{
        u+\frac{4u+3u^2+u^3}{1-u}
        +
        (1+u)
        \frac{\max_{1\le j\le n}\NormOne{A_{*j}}}
             {\sqrt m\,\max_{1\le j\le n}\Norm{A_{*j}}}
        \frac{\gamma_m(2+\gamma_m)(1+u)^2+u(1+u)+u}
             {
               \sqrt{r/m}
               +
               \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
             }
      }{
        1-\frac{4u+3u^2+u^3}{1-u}
      }
    \right)^2
  \Bigg].
\end{aligned}
\]
This is exactly the compact expression
\[
  nm\,S_{A,\log}(\delta_{\rm pre})^2a_2^2
  \left(
    2\zeta_{A,\log}(\delta_{\rm pre})
    +\zeta_{A,\log}(\delta_{\rm pre})^2
    +
    \gamma_s(1+\zeta_{A,\log}(\delta_{\rm pre}))^2
  \right),
\]
but all locally introduced shorthand has been recursively replaced in the
displayed definition of \(T_{A,\log}^{\rm fp}(\delta_{\rm pre})\), including
the concrete denominator relative error
\((4u+3u^2+u^3)/(1-u)\).  The exact-denominator variant is available as
infrastructure by replacing this relative denominator term by \(0\); it is not
the selected final concrete endpoint in this corollary.
On the same exact SRHT row-norm event,
\[
  \Frob{\widehat G_A^\rho(\omega,J)-G_A(\omega,J)}
  \le
  T_{A,\log}^{\rm fp}(\delta_{\rm pre}).
\]

By construction of the exact sample count \(s\) and witness \(\theta_A\),
\[
  \Phi(\theta_A,L_{A,\log}(\delta_{\rm pre}),\eps,s,r)
  \le\delta_{\rm sample}.
\]
Then the fully computed Algorithm 3 sampled input Gram satisfies
\[
  \Prob\!\left[
    (1-\eps)A^TA-T_{A,\log}^{\rm fp}(\delta_{\rm pre})\I_n
    \preceq
    \widehat G_A^\rho(\omega,J)
    \preceq
    (1+\eps)A^TA+T_{A,\log}^{\rm fp}(\delta_{\rm pre})\I_n
  \right]
  \ge
  1-\delta_{\rm pre}-\delta_{\rm sample}.
\]
The probability uses only the exact Rademacher and exact uniform-row laws.  No
probability table is computed.  The non-probability computations charged in
\(T_{A,\log}^{\rm fp}(\delta_{\rm pre})\) are the rounded scale
\(\widehat c_m\), rounded sign storage, rounded formation of
\(\widehat P_\omega^\rho\), rounded formation of
\(\widehat Y_\omega^\rho=\fl(\widehat P_\omega^\rho A)\), rounded denominator
\(\widehat d_\star\), rounded row scaling, and rounded Gram dot products.

In the small-roundoff regime
\[
  0\le u,\gamma_m,\gamma_s,\frac{4u+3u^2+u^3}{1-u}\le c<1,
  \qquad
  \sqrt{\frac rm}+\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}>0,
  \qquad
  A\ne0,
\]
with \(m,n,r,s,\delta_{\rm pre}\) and the column norms of \(A\) fixed, the
expanded relative error fraction in
\(T_{A,\log}^{\rm fp}(\delta_{\rm pre})\) has order
\[
  \Theta\!\left(
    u+\frac{4u+3u^2+u^3}{1-u}
    +
    \frac{
      (\gamma_m+u)\max_{1\le j\le n}\NormOne{A_{*j}}
    }{
      \sqrt m
      \left(
        \sqrt{r/m}+\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
      \right)
      \max_{1\le j\le n}\Norm{A_{*j}}
    }
  \right),
\]
and
\begingroup
\small
\[
\begin{aligned}
  T_{A,\log}^{\rm fp}(\delta_{\rm pre})
  =
  \Theta\!\left(
    nm
    \left(
      \sqrt{\frac rm}
      +
      \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
    \right)^2
    \right.
  \\
  \left.
    \qquad\times
    \left(\max_{1\le j\le n}\Norm{A_{*j}}\right)^2
    \left[
      \gamma_s+u+\frac{4u+3u^2+u^3}{1-u}
      +
      \frac{
        (\gamma_m+u)\max_{1\le j\le n}\NormOne{A_{*j}}
      }{
        \sqrt m
        \left(
          \sqrt{r/m}+\sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
        \right)
        \max_{1\le j\le n}\Norm{A_{*j}}
      }
    \right]
  \right).
\end{aligned}
\]
\endgroup
Equivalently,
\begingroup
\small
\[
\begin{aligned}
  T_{A,\log}^{\rm fp}(\delta_{\rm pre})
  =
  \Theta\!\left(
    nm
    \left(
      \sqrt{\frac rm}
      +
      \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
    \right)^2
    \right.
  \\
  \left.
    \qquad\times
    \left(\max_{1\le j\le n}\Norm{A_{*j}}\right)^2
    \left(\gamma_s+u+\frac{4u+3u^2+u^3}{1-u}\right)
  \right.
  \\
  \left.
    +
    n\sqrt m
    \left(
      \sqrt{\frac rm}
      +
      \sqrt{\frac{8\log(m/\delta_{\rm pre})}{m}}
    \right)
    \left(\max_{1\le j\le n}\NormOne{A_{*j}}\right)
    \left(\max_{1\le j\le n}\Norm{A_{*j}}\right)
    (\gamma_m+u)
  \right).
\end{aligned}
\]
\endgroup
For fixed \(A,m,n,r,s,\delta_{\rm pre}\),
\[
  T_{A,\log}^{\rm fp}(\delta_{\rm pre})\longrightarrow0
  \qquad
  \text{as}\qquad
  u,\gamma_m,\gamma_s,\frac{4u+3u^2+u^3}{1-u}\longrightarrow0,
\]
so the result is non-vacuous.  If \(A=0\), then \(a_1=a_2=0\),
\(A^TA=0\), the exact and computed preconditioned products are zero in the
floating-point model, and the theorem holds with
\(T_{A,\log}^{\rm fp}(\delta_{\rm pre})=0\).
\end{corollary}

\section*{CountSketch Sparse-Gram Endpoints}

This section records the currently closed CountSketch branches for Algorithm
3.  The CountSketch transform is the usual sparse embedding pattern
\cite{CharikarChenFarachColton2002,ClarksonWoodruff2013}.  The first closed
route below is collision-free, with probability loss \(m^2/r\); it is
non-vacuous only when \(r\) is larger than \(m^2\).  The later product-grid
route is the local finite-cover Markov/Frobenius route.  Neither route should
be read as the optimal Clarkson--Woodruff subspace-embedding concentration
theorem.

Let \(r\) be the number of CountSketch buckets.  A hash
\[
  h:\{1,\ldots,m\}\to\{1,\ldots,r\}
\]
and a sign vector \(\omega\in\{\pm1\}^m\) are sampled from the exact
CountSketch product law.  Sampling probabilities are exact mathematical laws
in this note.  Define the exact sparse CountSketch matrix
\[
  S_{h,\omega}(i,k)=
  \begin{cases}
    \omega_k,& h(k)=i,\\
    0,& h(k)\ne i,
  \end{cases}
\]
and the exact sketched matrix
\[
  Y(h,\omega;A)=S_{h,\omega}A .
\]
The exact CountSketch Gram error is
\[
  \Delta_{\rm CS}(h,\omega;A)
  =
  Y(h,\omega;A)^TY(h,\omega;A)-A^TA .
\]

The computed sparse matrix \(\widehat Y\) is formed entrywise by multiplying
each selected input entry by its exact sign in floating point and then
accumulating each bucket in floating point.  Let
\[
  b_i(h)=\#\{k:h(k)=i\}
\]
be the exact bucket size.  The entrywise sparse-apply error radius is
\[
  E^{\rm CS}_{ij}(h,\omega;A)
  =
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{k:h(k)=i}|\omega_k|\,|A_{kj}|.
\]
This is computable from the exact realized hash/sign pattern and the exact
input magnitudes.  It charges the rounded signed products and the rounded
bucket accumulation.  Let \(|Y|\) denote entrywise absolute value.  The rounded
sparse-Gram matrix is
\[
  \widehat G(h,\omega;A)
  =
  \fl\!\left(\widehat Y^T\widehat Y\right),
\]
where each Gram entry is a rounded length-\(r\) dot product.  The fully
expanded sparse-Gram floating-point radius is
\[
\begin{aligned}
  T_{\rm CSGram}^{\rm fp}(h,\omega;A)
  &:=
  \Frob{
    \left(
      \gamma_r
      \sum_{i=1}^{r}
      \bigl(|Y_{ij}|+E^{\rm CS}_{ij}\bigr)
      \bigl(|Y_{ik}|+E^{\rm CS}_{ik}\bigr)
    \right)_{j,k=1}^{n}
  }
  \\
  &\quad+
  \Frob{
    \left(
      \sum_{i=1}^{r}
      \left[
        E^{\rm CS}_{ij}|Y_{ik}|
        +
        |Y_{ij}|E^{\rm CS}_{ik}
        +
        E^{\rm CS}_{ij}E^{\rm CS}_{ik}
      \right]
    \right)_{j,k=1}^{n}
  } .
\end{aligned}
\]
For fixed \(h,\omega,A\), valid \(\gamma_r\), and small bucket roundoff,
\[
  T_{\rm CSGram}^{\rm fp}
  =
  \Theta\!\left(
    \gamma_r\Frob{|Y|^T|Y|}
    +
    \Frob{(E^{\rm CS})^T|Y|+|Y|^TE^{\rm CS}}
  \right)
\]
when the displayed leading term is nonzero.  Since
\(E^{\rm CS}_{ij}=\Theta((u+\gamma_{b_i})\sum_{k:h(k)=i}|A_{kj}|)\), the
radius vanishes as \(u,\gamma_r,\gamma_{b_i}\to0\) for fixed realized
hash/sign data and fixed \(A\).

\subsection*{Collision-Free Actual-Input Route}

Let \(q\) be an exact analysis dimension.  Let
\[
  U\in\R^{m\times q},\qquad C\in\R^{q\times n},
  \qquad U^TU=\I_q,\qquad A=UC .
\]
The matrices \(U\) and \(C\) are exact analysis witnesses for the column space
of the input.  Algorithm 3 is not assumed to compute them in this theorem; the
implemented arithmetic below uses the actual input entries of \(A\).

The collision-free event is
\[
  h(a)\ne h(b)\qquad\text{for every }a\ne b.
\]
Under the exact CountSketch hash law,
\[
  \Prob_h[h\text{ is collision-free}]\ge 1-\frac{m^2}{r}.
\]
On this event, the exact sparse transform preserves all Gram matrices:
\[
  Y(h,\omega;A)^TY(h,\omega;A)=A^TA .
\]
The Rademacher signs remain exact mathematical signs; only their use in
floating-point multiplications is charged.

After the exact CountSketch draw, let
\[
  \sigma_1,\ldots,\sigma_s\in\{1,\ldots,r\}
\]
be exact iid uniform row samples.  Let \(\delta_{\rm samp}\ge0\) be such that
\[
  \Phi(\theta,r,\eps,s,q)\le\delta_{\rm samp},
  \qquad \theta>0.
\]
Here the uniform-row Loewner radius parameter is \(L=r\), because a
collision-free CountSketch applied to an orthonormal \(U\) has orthonormal
columns and every row has squared norm at most one.  Thus a uniform row sample
from the \(r\)-row preconditioned matrix has one-sample Loewner radius \(r\).

Set
\[
  d=\sqrt{s/r},\qquad
  \widehat d_\star=
  \fl\!\left(\fl(\sqrt{s})\,\fl(1/\fl(\sqrt r))\right),
\]
and
\[
  \Delta_\star=\frac{4u+3u^2+u^3}{1-u}.
\]
The concrete denominator routine proves
\[
  \widehat d_\star\ne0,\qquad
  |\widehat d_\star-d|\le d\,\Delta_\star .
\]
Define the exact and computed sampled rows
\[
  B_{tj}=\frac{Y_{\sigma_tj}}{d},\qquad
  \widehat B_{tj}=\fl\!\left(
    \frac{\widehat Y_{\sigma_tj}}{\widehat d_\star}\right),
  \qquad
  \widetilde B_{tj}=\frac{\widehat Y_{\sigma_tj}}{d}.
\]
The denominator-and-division entry radius is
\[
  E^{\rm den}_{tj}
  =
  u|\widehat B_{tj}|
  +
  \frac{|\widehat Y_{\sigma_tj}|}{|\widehat d_\star|}\,\Delta_\star .
\]
The sparse-apply entry radius propagated to the sampled rows is
\[
  F_{tj}
  =
  \frac{E^{\rm CS}_{\sigma_tj}(h,\omega;A)}{d}.
\]
The fully expanded downstream floating-point radius is
\[
  T_{\rm CF,row}^{\rm fp}
  =
  T_{\rm den}^{\rm fp}
  +
  T_{\rm dot}^{\rm fp}
  +
  T_{\rm basis}^{\rm fp},
\]
where
\[
  T_{\rm den}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{t=1}^{s}
      E^{\rm den}_{tj}|\widehat B_{tk}|
      +
      |\widetilde B_{tj}|E^{\rm den}_{tk}
    \right)_{j,k=1}^{n}},
\]
\[
  T_{\rm dot}^{\rm fp}
  =
  \Frob{
    \left(
      \gamma_s\sum_{t=1}^{s}
      |\widehat B_{tj}|\,|\widehat B_{tk}|
    \right)_{j,k=1}^{n}},
\]
and
\[
  T_{\rm basis}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{t=1}^{s}
      F_{tj}|\widetilde B_{tk}|+|B_{tj}|F_{tk}
    \right)_{j,k=1}^{n}} .
\]

\begin{corollary}[Collision-free CountSketch actual-input sampled Gram]
Assume \(r>0\), \(s>0\), \(U^TU=\I_q\), \(A=UC\), valid \(\gamma_m\) for the
sparse bucket accumulations, valid \(\gamma_s\) for the sampled-Gram dot
products, \(0<u<1\), \(\theta>0\), and
\[
  \Phi(\theta,r,\eps,s,q)\le\delta_{\rm samp},
  \qquad
  \frac{m^2}{r}+\delta_{\rm samp}\le\delta .
\]
Let
\[
  \widehat G_{\rm CF}^{\rm fp}
  =
  \fl\!\left(\widehat B^T\widehat B\right)
\]
be the matrix produced by the implemented path: rounded sparse CountSketch
apply to the actual input \(A\), the concrete denominator
\(\widehat d_\star\), rounded sampled-row divisions, and rounded length-\(s\)
Gram dot products.  Then
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\eps A^TA-T_{\rm CF,row}^{\rm fp}\I_n
    \preceq
    \widehat G_{\rm CF}^{\rm fp}-A^TA
    \preceq
    \eps A^TA+T_{\rm CF,row}^{\rm fp}\I_n
  \right]
  \ge 1-\delta .
\end{aligned}
\]
The exact objects are \(A\), the analysis witnesses \(U,C\), the hash/sign
law, the uniform row-sampling law, \(Y=S_{h,\omega}A\), and \(A^TA\).  The
computed non-probability objects are \(\widehat Y\), \(\widehat d_\star\),
\(\widehat B\), and \(\widehat G_{\rm CF}^{\rm fp}\).  There is no
perturbation-event hypothesis, extra existence hypothesis, generic
denominator parameter, or probability-computation error term.

For fixed realized \(h,\omega,\sigma,A\), fixed \(d>0\), and nonzero leading
deterministic coefficient,
\[
\begin{aligned}
  T_{\rm CF,row}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s\Frob{|\widehat B|^T|\widehat B|}
  +
  \Frob{(E^{\rm den})^T|\widehat B|
        +|\widetilde B|^TE^{\rm den}}
  \\
  &+
  \Frob{F^T|\widetilde B|+|B|^TF}
  \Big),
\end{aligned}
\]
with the irreducible substitutions
\[
  E^{\rm den}_{tj}
  =
  \Theta\!\left(
    u|\widehat B_{tj}|
    +
    \frac{|\widehat Y_{\sigma_tj}|}{|\widehat d_\star|}
    \frac{4u+3u^2+u^3}{1-u}
  \right)
\]
and
\[
  F_{tj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{b_{\sigma_t}(h)}}{\sqrt{s/r}}
    \sum_{k:h(k)=\sigma_t}|A_{kj}|
  \right).
\]
Consequently \(T_{\rm CF,row}^{\rm fp}\to0\) as
\[
  u,\gamma_s,\gamma_{b_i(h)},\frac{4u+3u^2+u^3}{1-u}\to0
\]
for fixed realized data.  The exact probability loss has order
\[
  \Theta\!\left(\frac{m^2}{r}+\Phi(\theta,r,\eps,s,q)\right),
\]
and is non-vacuous when \(m^2/r+\Phi(\theta,r,\eps,s,q)<1\).
\end{corollary}

\subsection*{Stored-Sign Collision-Free Actual-Input Route}

The preceding actual-input theorem uses exact Rademacher signs directly in the
modeled sparse apply.  If the implementation first stores the realized signs,
the probability law is unchanged, but the stored signs are computed
non-probability objects and their rounding must be charged.

Let the storage mode be
\[
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
where
\[
  \widehat\omega_k^{\rho_{\rm sig}}
  \in
  \{\fl(\omega_k\cdot1),\,\fl(\omega_k+0),\,\fl(\omega_k-0)\}.
\]
Since \(|\omega_k|=1\), each concrete mode satisfies
\[
  |\widehat\omega_k^{\rho_{\rm sig}}-\omega_k|\le u .
\]
The exact objects remain \(U,C,A=UC\), \(Y=S_{h,\omega}A\), the exact
hash/sign law, the exact uniform row-sampling law, and \(A^TA\).  The
computed non-probability objects are now the stored sign table
\(\widehat\omega^{\rho_{\rm sig}}\), the rounded sparse apply
\(\widehat Y^{\rho_{\rm sig}}\), the concrete denominator
\(\widehat d_\star\), rounded sampled-row divisions, and rounded
sampled-Gram dot products.

For each CountSketch bucket \(i\), define the stored-sign sparse-apply radius
\[
\begin{aligned}
  E^{{\rm CS},\rho_{\rm sig}}_{ij}(h,\omega;A)
  &:=
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{k:h(k)=i}
      |\widehat\omega_k^{\rho_{\rm sig}}|\,|A_{kj}|\\
  &\quad+
  \sum_{k:h(k)=i}
      |\widehat\omega_k^{\rho_{\rm sig}}-\omega_k|\,|A_{kj}| .
\end{aligned}
\]
After exact row samples \(\sigma_1,\ldots,\sigma_s\), set
\[
  B_{tj}=\frac{Y_{\sigma_tj}}{d},\qquad
  \widehat B^{\rho_{\rm sig}}_{tj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig}}_{\sigma_tj}}
         {\widehat d_\star}\right),
  \qquad
  \widetilde B^{\rho_{\rm sig}}_{tj}
  =
  \frac{\widehat Y^{\rho_{\rm sig}}_{\sigma_tj}}{d}.
\]
The denominator-and-division radius becomes
\[
  E^{{\rm den},\rho_{\rm sig}}_{tj}
  =
  u|\widehat B^{\rho_{\rm sig}}_{tj}|
  +
  \frac{|\widehat Y^{\rho_{\rm sig}}_{\sigma_tj}|}
       {|\widehat d_\star|}
  \frac{4u+3u^2+u^3}{1-u},
\]
and the sampled sparse-apply radius is
\[
  F^{\rho_{\rm sig}}_{tj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig}}_{\sigma_tj}(h,\omega;A)}{d}.
\]
Define the stored-sign collision-free downstream radius by the irreducible
sum
\[
  T_{{\rm CF,row},\rho_{\rm sig}}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig}}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig}}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig}}^{\rm fp},
\]
where
\[
  T_{{\rm den},\rho_{\rm sig}}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{t=1}^{s}
      E^{{\rm den},\rho_{\rm sig}}_{tj}
      |\widehat B^{\rho_{\rm sig}}_{tk}|
      +
      |\widetilde B^{\rho_{\rm sig}}_{tj}|
      E^{{\rm den},\rho_{\rm sig}}_{tk}
    \right)_{j,k=1}^{n}},
\]
\[
  T_{{\rm dot},\rho_{\rm sig}}^{\rm fp}
  =
  \Frob{
    \left(
      \gamma_s\sum_{t=1}^{s}
      |\widehat B^{\rho_{\rm sig}}_{tj}|\,
      |\widehat B^{\rho_{\rm sig}}_{tk}|
    \right)_{j,k=1}^{n}},
\]
and
\[
  T_{{\rm basis},\rho_{\rm sig}}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{t=1}^{s}
      F^{\rho_{\rm sig}}_{tj}
      |\widetilde B^{\rho_{\rm sig}}_{tk}|
      +
      |B_{tj}|F^{\rho_{\rm sig}}_{tk}
    \right)_{j,k=1}^{n}} .
\]

\begin{corollary}[Stored-sign collision-free CountSketch actual-input sampled Gram]
Assume the hypotheses of the preceding collision-free actual-input corollary,
and store every realized Rademacher sign by one of
\(\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\) before the sparse apply.  Let
\[
  \widehat G_{{\rm CF},\rho_{\rm sig}}^{\rm fp}
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig}})^T
    \widehat B^{\rho_{\rm sig}}\right)
\]
be the matrix produced by the implemented path: rounded sign storage, rounded
sparse CountSketch apply to the actual input \(A\), the concrete denominator
\(\widehat d_\star\), rounded sampled-row divisions, and rounded length-\(s\)
Gram dot products.  Then
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\eps A^TA-T_{{\rm CF,row},\rho_{\rm sig}}^{\rm fp}\I_n
    \preceq
    \widehat G_{{\rm CF},\rho_{\rm sig}}^{\rm fp}-A^TA
    \preceq
    \eps A^TA+T_{{\rm CF,row},\rho_{\rm sig}}^{\rm fp}\I_n
  \right]
  \ge 1-\delta .
\end{aligned}
\]
No extra probability loss is introduced by sign storage; the storage errors
enter only through the deterministic radius \(T_{{\rm CF,row},\rho_{\rm sig}}^{\rm fp}\).

For fixed realized \(h,\omega,\sigma,A\), fixed \(d>0\), and nonzero leading
deterministic coefficient,
\[
\begin{aligned}
  T_{{\rm CF,row},\rho_{\rm sig}}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s\Frob{
      |\widehat B^{\rho_{\rm sig}}|^T
      |\widehat B^{\rho_{\rm sig}}|}
  +
  \Frob{
      (E^{{\rm den},\rho_{\rm sig}})^T
      |\widehat B^{\rho_{\rm sig}}|
      +
      |\widetilde B^{\rho_{\rm sig}}|^T
      E^{{\rm den},\rho_{\rm sig}}}
  \\
  &+
  \Frob{
      (F^{\rho_{\rm sig}})^T|\widetilde B^{\rho_{\rm sig}}|
      +
      |B|^TF^{\rho_{\rm sig}}}
  \Big),
\end{aligned}
\]
with the irreducible substitutions
\[
  E^{{\rm den},\rho_{\rm sig}}_{tj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig}}_{tj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig}}_{\sigma_tj}|}
         {|\widehat d_\star|}
    \frac{4u+3u^2+u^3}{1-u}
  \right)
\]
and
\[
  F^{\rho_{\rm sig}}_{tj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{b_{\sigma_t}(h)}}{\sqrt{s/r}}
    \sum_{k:h(k)=\sigma_t}|A_{kj}|
  \right).
\]
Hence \(T_{{\rm CF,row},\rho_{\rm sig}}^{\rm fp}\to0\) as
\[
  u,\gamma_s,\gamma_{b_i(h)},\frac{4u+3u^2+u^3}{1-u}\to0
\]
for fixed realized data.  The probability loss is still
\[
  \Theta\!\left(\frac{m^2}{r}+\Phi(\theta,r,\eps,s,q)\right),
\]
so the result is non-vacuous under the same condition
\(m^2/r+\Phi(\theta,r,\eps,s,q)<1\).
\end{corollary}

\subsection*{Permuted-Bucket Stored-Sign Actual-Input Route}

Some sparse CountSketch implementations traverse the entries in each realized
bucket in a fixed order chosen by the implementation.  For a realized hash
\(h\), let
\[
  \pi_i(h):\{0,\ldots,b_i(h)-1\}\to\{0,\ldots,b_i(h)-1\}
\]
be the exact permutation used to traverse bucket \(i\), and let
\[
  k_{i,t}^{\pi}(h)
  :=
  \mathrm{bucketIndex}\bigl(h,i,\pi_i(h)(t)\bigr)
\]
be the original input-row index reached at traversal position \(t\).  The
permutations \(\pi_i(h)\) are exact discrete implementation choices.  They are
not random laws and are not floating-point real quantities, but the sparse
signed products and bucket accumulations executed in that order are computed
and must be charged.

With the same stored sign modes
\(\rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}\), define
the permuted sparse-apply entry radius
\[
\begin{aligned}
  E^{{\rm CS},\rho_{\rm sig},\pi}_{ij}(h,\omega;A)
  &:=
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{t=0}^{b_i(h)-1}
    |\widehat\omega_{k_{i,t}^{\pi}(h)}^{\rho_{\rm sig}}|\,
    |A_{k_{i,t}^{\pi}(h),j}|\\
  &\quad+
  \sum_{t=0}^{b_i(h)-1}
    |\widehat\omega_{k_{i,t}^{\pi}(h)}^{\rho_{\rm sig}}
      -\omega_{k_{i,t}^{\pi}(h)}|\,
    |A_{k_{i,t}^{\pi}(h),j}| .
\end{aligned}
\]
Let \(\widehat Y^{\rho_{\rm sig},\pi}\) be the rounded sparse CountSketch
apply to the actual input \(A\), using the stored signs and the traversal
orders \(\pi_i(h)\).  Define
\[
  \widehat B^{\rho_{\rm sig},\pi}_{tj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_tj}}
         {\widehat d_\star}\right),
  \qquad
  \widetilde B^{\rho_{\rm sig},\pi}_{tj}
  =
  \frac{\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_tj}}{d},
\]
\[
  E^{{\rm den},\rho_{\rm sig},\pi}_{tj}
  =
  u|\widehat B^{\rho_{\rm sig},\pi}_{tj}|
  +
  \frac{|\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_tj}|}
       {|\widehat d_\star|}
  \frac{4u+3u^2+u^3}{1-u},
\]
and
\[
  F^{\rho_{\rm sig},\pi}_{tj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig},\pi}_{\sigma_tj}
        (h,\omega;A)}{d}.
\]
The irreducible permuted-bucket stored-sign downstream radius is
\[
  T_{{\rm CF,row},\rho_{\rm sig},\pi}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig},\pi}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig},\pi}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig},\pi}^{\rm fp},
\]
where
\[
\begin{aligned}
  T_{{\rm den},\rho_{\rm sig},\pi}^{\rm fp}
  &:=
  \Frob{
    (E^{{\rm den},\rho_{\rm sig},\pi})^T
    |\widehat B^{\rho_{\rm sig},\pi}|
    +
    |\widetilde B^{\rho_{\rm sig},\pi}|^T
    E^{{\rm den},\rho_{\rm sig},\pi}},\\
  T_{{\rm dot},\rho_{\rm sig},\pi}^{\rm fp}
  &:=
  \gamma_s
  \Frob{
    |\widehat B^{\rho_{\rm sig},\pi}|^T
    |\widehat B^{\rho_{\rm sig},\pi}|},\\
  T_{{\rm basis},\rho_{\rm sig},\pi}^{\rm fp}
  &:=
  \Frob{
    (F^{\rho_{\rm sig},\pi})^T
    |\widetilde B^{\rho_{\rm sig},\pi}|
    +
    |B|^TF^{\rho_{\rm sig},\pi}} .
\end{aligned}
\]

\begin{corollary}[Permuted-bucket stored-sign collision-free actual-input sampled Gram]
Assume the hypotheses of the stored-sign collision-free actual-input
corollary, and fix the exact bucket traversal orders \(\pi_i(h)\).  Let
\[
  \widehat G_{{\rm CF},\rho_{\rm sig},\pi}^{\rm fp}
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig},\pi})^T
    \widehat B^{\rho_{\rm sig},\pi}\right)
\]
be the matrix produced by rounded sign storage, permuted-order rounded sparse
CountSketch apply to the actual input \(A\), the concrete denominator
\(\widehat d_\star\), rounded sampled-row divisions, and rounded length-\(s\)
Gram dot products.  Then
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\eps A^TA
    -T_{{\rm CF,row},\rho_{\rm sig},\pi}^{\rm fp}\I_n
    \preceq
    \widehat G_{{\rm CF},\rho_{\rm sig},\pi}^{\rm fp}-A^TA
    \preceq
    \eps A^TA
    +T_{{\rm CF,row},\rho_{\rm sig},\pi}^{\rm fp}\I_n
  \right]
  \ge 1-\delta .
\end{aligned}
\]
Exact objects are \(U,C,A=UC\), the hash/sign/row-sampling laws, the bucket
orders \(\pi_i(h)\), \(Y=S_{h,\omega}A\), and \(A^TA\).  Computed
non-probability objects are the stored signs, sparse signed products,
permuted-order bucket accumulations, \(\widehat d_\star\), row divisions, and
Gram dot products.  No extra probability loss is introduced by the traversal
order.

For fixed realized \(h,\omega,\sigma,A,\pi\), fixed \(d>0\), and nonzero
leading deterministic coefficient,
\[
\begin{aligned}
  T_{{\rm CF,row},\rho_{\rm sig},\pi}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s\Frob{
      |\widehat B^{\rho_{\rm sig},\pi}|^T
      |\widehat B^{\rho_{\rm sig},\pi}|}
  +
  \Frob{
      (E^{{\rm den},\rho_{\rm sig},\pi})^T
      |\widehat B^{\rho_{\rm sig},\pi}|
      +
      |\widetilde B^{\rho_{\rm sig},\pi}|^T
      E^{{\rm den},\rho_{\rm sig},\pi}}
  \\
  &+
  \Frob{
      (F^{\rho_{\rm sig},\pi})^T
      |\widetilde B^{\rho_{\rm sig},\pi}|
      +
      |B|^TF^{\rho_{\rm sig},\pi}}
  \Big),
\end{aligned}
\]
with the irreducible substitutions
\[
  E^{{\rm den},\rho_{\rm sig},\pi}_{tj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig},\pi}_{tj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_tj}|}
         {|\widehat d_\star|}
    \frac{4u+3u^2+u^3}{1-u}
  \right)
\]
and
\[
  F^{\rho_{\rm sig},\pi}_{tj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{b_{\sigma_t}(h)}}{\sqrt{s/r}}
    \sum_{v=0}^{b_{\sigma_t}(h)-1}
      |A_{k_{\sigma_t,v}^{\pi}(h),j}|
  \right).
\]
Therefore \(T_{{\rm CF,row},\rho_{\rm sig},\pi}^{\rm fp}\to0\) as
\[
  u,\gamma_s,\gamma_{b_i(h)},\frac{4u+3u^2+u^3}{1-u}\to0
\]
for fixed realized data.  The probability loss is unchanged,
\[
  \Theta\!\left(\frac{m^2}{r}+\Phi(\theta,r,\eps,s,q)\right),
\]
so the result is non-vacuous under
\(m^2/r+\Phi(\theta,r,\eps,s,q)<1\).
\end{corollary}

\subsection*{Tree-Reduced Stored-Sign Actual-Input Route}

Some sparse CountSketch implementations reduce each bucket by a fixed binary
summation tree instead of a flat left-to-right accumulation.  The tree shapes
are exact discrete implementation choices.  They are not random laws and are
not floating-point real quantities, but the arithmetic performed along each
tree is computed and must be charged.

For a realized hash \(h\), let \(\mathcal T_i(h)\) be the exact tree used for
bucket \(i\), and let \(d_i^{\mathcal T}(h)\) be its depth.  Assume the
roundoff guard for every realized tree depth is valid, so
\(\gamma_{d_i^{\mathcal T}(h)}\) is defined.  With the same stored sign modes
\(\rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}\), define
\[
\begin{aligned}
  E^{{\rm CS},\rho_{\rm sig},\mathcal T}_{ij}(h,\omega;A)
  &:=
  \bigl(u+\gamma_{d_i^{\mathcal T}(h)}
        +u\gamma_{d_i^{\mathcal T}(h)}\bigr)
  \sum_{k:h(k)=i}
      |\widehat\omega_k^{\rho_{\rm sig}}|\,|A_{kj}|\\
  &\quad+
  \sum_{k:h(k)=i}
      |\widehat\omega_k^{\rho_{\rm sig}}-\omega_k|\,|A_{kj}| .
\end{aligned}
\]
This is the only change from the flat stored-sign radius: the bucket
accumulation factor \(\gamma_{b_i(h)}\) is replaced by the tree-depth factor
\(\gamma_{d_i^{\mathcal T}(h)}\).  Let
\(\widehat Y^{\rho_{\rm sig},\mathcal T}\) be the rounded sparse CountSketch
apply to the actual input \(A\) using the stored signs and the tree reductions.
Define
\[
  \widehat B^{\rho_{\rm sig},\mathcal T}_{tj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_tj}}
         {\widehat d_\star}\right),
  \qquad
  \widetilde B^{\rho_{\rm sig},\mathcal T}_{tj}
  =
  \frac{\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_tj}}{d},
\]
\[
  E^{{\rm den},\rho_{\rm sig},\mathcal T}_{tj}
  =
  u|\widehat B^{\rho_{\rm sig},\mathcal T}_{tj}|
  +
  \frac{|\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_tj}|}
       {|\widehat d_\star|}
  \frac{4u+3u^2+u^3}{1-u},
\]
and
\[
  F^{\rho_{\rm sig},\mathcal T}_{tj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig},\mathcal T}_{\sigma_tj}
        (h,\omega;A)}{d}.
\]
The irreducible tree-reduced stored-sign downstream radius is
\[
  T_{{\rm CF,row},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig},\mathcal T}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig},\mathcal T}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig},\mathcal T}^{\rm fp},
\]
where the three terms are obtained from the preceding stored-sign definitions
by replacing
\(\widehat B^{\rho_{\rm sig}},\widetilde B^{\rho_{\rm sig}},
E^{{\rm den},\rho_{\rm sig}},F^{\rho_{\rm sig}}\) by their
\(\mathcal T\)-decorated versions.

\begin{corollary}[Tree-reduced stored-sign collision-free actual-input sampled Gram]
Assume the hypotheses of the stored-sign collision-free actual-input
corollary, and assume the tree-depth roundoff guards above.  Let
\[
  \widehat G_{{\rm CF},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig},\mathcal T})^T
    \widehat B^{\rho_{\rm sig},\mathcal T}\right)
\]
be the matrix produced by rounded sign storage, tree-reduced rounded sparse
CountSketch apply to the actual input \(A\), the concrete denominator
\(\widehat d_\star\), rounded sampled-row divisions, and rounded length-\(s\)
Gram dot products.  Then
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\eps A^TA
    -T_{{\rm CF,row},\rho_{\rm sig},\mathcal T}^{\rm fp}\I_n
    \preceq
    \widehat G_{{\rm CF},\rho_{\rm sig},\mathcal T}^{\rm fp}-A^TA
    \preceq
    \eps A^TA
    +T_{{\rm CF,row},\rho_{\rm sig},\mathcal T}^{\rm fp}\I_n
  \right]
  \ge 1-\delta .
\end{aligned}
\]
Exact objects are \(U,C,A=UC\), the hash/sign/row-sampling laws, the tree
shapes, \(Y=S_{h,\omega}A\), and \(A^TA\).  Computed non-probability objects
are the stored signs, tree-reduced sparse products and accumulations,
\(\widehat d_\star\), row divisions, and Gram dot products.  No extra
probability loss is introduced by the tree choice.

For fixed realized \(h,\omega,\sigma,A,\mathcal T\), fixed \(d>0\), and
nonzero leading deterministic coefficient,
\[
\begin{aligned}
  T_{{\rm CF,row},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s\Frob{
      |\widehat B^{\rho_{\rm sig},\mathcal T}|^T
      |\widehat B^{\rho_{\rm sig},\mathcal T}|}
  +
  \Frob{
      (E^{{\rm den},\rho_{\rm sig},\mathcal T})^T
      |\widehat B^{\rho_{\rm sig},\mathcal T}|
      +
      |\widetilde B^{\rho_{\rm sig},\mathcal T}|^T
      E^{{\rm den},\rho_{\rm sig},\mathcal T}}
  \\
  &+
  \Frob{
      (F^{\rho_{\rm sig},\mathcal T})^T
      |\widetilde B^{\rho_{\rm sig},\mathcal T}|
      +
      |B|^TF^{\rho_{\rm sig},\mathcal T}}
  \Big),
\end{aligned}
\]
with
\[
  E^{{\rm den},\rho_{\rm sig},\mathcal T}_{tj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig},\mathcal T}_{tj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_tj}|}
         {|\widehat d_\star|}
    \frac{4u+3u^2+u^3}{1-u}
  \right)
\]
and
\[
  F^{\rho_{\rm sig},\mathcal T}_{tj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{d_{\sigma_t}^{\mathcal T}(h)}}{\sqrt{s/r}}
    \sum_{k:h(k)=\sigma_t}|A_{kj}|
  \right).
\]
If the bucket trees are balanced, then
\(\gamma_{d_i^{\mathcal T}(h)}=\Theta(u\log(b_i(h)+1))\) in the
small-roundoff fixed-realization regime, so the sampled sparse-apply term is
\[
  F^{\rho_{\rm sig},\mathcal T}_{tj}
  =
  \Theta\!\left(
    \frac{u(1+\log(b_{\sigma_t}(h)+1))}{\sqrt{s/r}}
    \sum_{k:h(k)=\sigma_t}|A_{kj}|
  \right).
\]
The probability loss remains
\[
  \Theta\!\left(\frac{m^2}{r}+\Phi(\theta,r,\eps,s,q)\right),
\]
and the deterministic radius vanishes as
\[
  u,\gamma_s,\gamma_{d_i^{\mathcal T}(h)},
  \frac{4u+3u^2+u^3}{1-u}\to0
\]
for fixed realized data.
\end{corollary}

\subsection*{Product-Grid Stored CountSketch Signs}

If the realized CountSketch signs are stored before the sparse apply, the
probability law is still exact, but the stored sign table is a computed
non-probability object.  For a storage mode
\[
  \rho\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
define
\[
  \widehat\omega_k^\rho
  \in
  \{\fl(\omega_k\cdot1),\,\fl(\omega_k+0),\,\fl(\omega_k-0)\}.
\]
Since \(|\omega_k|=1\), each of these concrete storage modes satisfies
\[
  |\widehat\omega_k^\rho-\omega_k|\le u .
\]
The computed sparse apply now multiplies \(A_{kj}\) by
\(\widehat\omega_k^\rho\), not by the exact sign.  Its irreducible
entrywise radius is
\[
\begin{aligned}
  E^{{\rm CS},\rho}_{ij}(h,\omega;A)
  &:=
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{k:h(k)=i}|\widehat\omega_k^\rho|\,|A_{kj}|
  +
  u\sum_{k:h(k)=i}|A_{kj}|.
\end{aligned}
\]
The first term is the sparse product and bucket-accumulation error using the
stored signs; the second term is the exact deterministic storage deviation
back to the ideal \(S_{h,\omega}A\).  The resulting deterministic Gram radius
is obtained from the previous display by replacing \(E^{\rm CS}\) with
\(E^{{\rm CS},\rho}\):
\[
\begin{aligned}
  T_{{\rm CSGram},\rho}^{\rm fp}(h,\omega;A)
  &:=
  \Frob{
    \left(
      \gamma_r
      \sum_{i=1}^{r}
      \bigl(|Y_{ij}|+E^{{\rm CS},\rho}_{ij}\bigr)
      \bigl(|Y_{ik}|+E^{{\rm CS},\rho}_{ik}\bigr)
    \right)_{j,k=1}^{n}
  }
  \\
  &\quad+
  \Frob{
    \left(
      \sum_{i=1}^{r}
      \left[
        E^{{\rm CS},\rho}_{ij}|Y_{ik}|
        +
        |Y_{ij}|E^{{\rm CS},\rho}_{ik}
        +
        E^{{\rm CS},\rho}_{ij}E^{{\rm CS},\rho}_{ik}
      \right]
    \right)_{j,k=1}^{n}
  } .
\end{aligned}
\]
For each fixed realized \(h,\omega,A\),
\[
  \Frob{\widehat G^\rho-Y^TY}
  \le
  T_{{\rm CSGram},\rho}^{\rm fp}(h,\omega;A).
\]
Moreover
\[
  T_{{\rm CSGram},\rho}^{\rm fp}
  =
  \Theta\!\left(
    \gamma_r\Frob{|Y|^T|Y|}
    +
    \Frob{(E^{{\rm CS},\rho})^T|Y|+|Y|^TE^{{\rm CS},\rho}}
  \right),
\]
with
\[
  E^{{\rm CS},\rho}_{ij}
  =
  \Theta\!\left(
    (u+\gamma_{b_i(h)})
    \sum_{k:h(k)=i}|A_{kj}|
  \right)
\]
for the three displayed storage modes.  Thus the stored-sign radius is
non-vacuous: it tends to zero as \(u,\gamma_r,\gamma_{b_i}\to0\) for fixed
realized data and fixed \(A\).

\begin{corollary}[Product-grid CountSketch sparse-Gram theorem with stored signs]
Let \(A\in\R^{m\times n}\) be the exact input matrix handed to Algorithm 3,
and let the exact CountSketch law draw \(h\) and \(\omega\).  Let
\(\rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}\) select one
of the three sign-storage routines above.  Let \(\mathcal I\) be a finite
exact index set, let \(g:\mathcal I\to\R\) be an exact one-dimensional grid
covering \([-1,1]\) with radius \(\delta_{\rm grid}\), and assume
\[
  \delta_{\rm grid}\ge0,\qquad
  \sqrt n\,\delta_{\rm grid}\le\rho,\qquad
  \eta>0,\qquad
  L>0 .
\]
For every \(a:\{1,\ldots,n\}\to\mathcal I\), define
\[
  z_a(j)=g(a(j)),\qquad j=1,\ldots,n .
\]
Set
\[
  \tau_{{\rm pg},\rho_{\rm sig}}^{\rm fp}(h,\omega;A)
  =
  \eta+L(2\rho+\rho^2)
  +
  T_{{\rm CSGram},\rho_{\rm sig}}^{\rm fp}(h,\omega;A).
\]
If the floating-point model has valid \(\gamma_m\) and \(\gamma_r\), then
\[
\begin{aligned}
&\Prob_{h,\omega}
  \left[
    -\tau_{{\rm pg},\rho_{\rm sig}}^{\rm fp}(h,\omega;A)\I_n
    \preceq
    \widehat G^{\rho_{\rm sig}}(h,\omega;A)-A^TA
    \preceq
    \tau_{{\rm pg},\rho_{\rm sig}}^{\rm fp}(h,\omega;A)\I_n
  \right]
\\
&\qquad\ge
  1-
  \left(
    \sum_{a:\{1,\ldots,n\}\to\mathcal I}
      \frac{2\Norm{Az_a}^4}{r\eta^2}
    +
      \frac{2\Frob{A}^4}{rL^2}
  \right).
\end{aligned}
\]
Equivalently, if the displayed product-grid loss is at most \(\delta\), the
stored-sign computed sparse-Gram Loewner event has probability at least
\(1-\delta\).

The product-grid loss is unchanged by sign storage because it belongs to the
exact hash/sign probability analysis.  The computed non-probability quantities
are the stored sign table \(\widehat\omega^{\rho_{\rm sig}}\), the sparse
signed products, bucket accumulations, and rounded Gram dot products; their
floating-point contribution is exactly the deterministic radius
\(T_{{\rm CSGram},\rho_{\rm sig}}^{\rm fp}\).  For fixed exact \(A\), fixed
grid, fixed \(\eta,L\), and nonzero numerator, the probability-loss order is
\[
  \Theta\!\left(
    \frac{
      \sum_a\Norm{Az_a}^4/\eta^2+\Frob{A}^4/L^2
    }{r}
  \right),
\]
while the additional floating-point radius has the \(\Theta\)-order displayed
above and tends to zero with \(u,\gamma_r,\gamma_{b_i}\).
\end{corollary}

\subsection*{Stored CountSketch Signs with Permuted Bucket Layouts}

The preceding stored-sign theorem used the canonical exact enumeration of each
bucket.  A sparse implementation may instead visit the selected rows in a
different fixed memory order.  For each realized exact hash \(h\), let
\[
  B_i(h)=\{k:h(k)=i\},\qquad b_i(h)=|B_i(h)|,
\]
and let
\[
  k_{i,1},\ldots,k_{i,b_i(h)}
\]
be any exact ordering of the same bucket.  This ordering is a discrete index
operation, not a floating-point real computation.  With stored signs
\(\widehat\omega^\rho\), define the permuted sparse-apply radius
\[
\begin{aligned}
  E^{{\rm CS},\rho,\pi}_{ij}(h,\omega;A)
  &:=
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{t=1}^{b_i(h)}
    |\widehat\omega^{\rho_{\rm sig}}_{k_{i,t}}|\,|A_{k_{i,t}j}|
  \\
  &\quad+
  u\sum_{t=1}^{b_i(h)}|A_{k_{i,t}j}|.
\end{aligned}
\]
The first line charges the rounded signed products and the rounded
left-to-right accumulation in the chosen order.  The second line charges the
storage error of the realized signs.  The exact ideal reference remains
\[
  Y_{ij}=\sum_{k:h(k)=i}\omega_k A_{kj}.
\]
The corresponding Gram radius is
\[
\begin{aligned}
  T_{{\rm CSGram},\rho,\pi}^{\rm fp}(h,\omega;A)
  &:=
  \Frob{
    \left(
      \gamma_r
      \sum_{i=1}^{r}
      \bigl(|Y_{ij}|+E^{{\rm CS},\rho,\pi}_{ij}\bigr)
      \bigl(|Y_{ik}|+E^{{\rm CS},\rho,\pi}_{ik}\bigr)
    \right)_{j,k=1}^{n}
  }
  \\
  &\quad+
  \Frob{
    \left(
      \sum_{i=1}^{r}
      \left[
        E^{{\rm CS},\rho,\pi}_{ij}|Y_{ik}|
        +
        |Y_{ij}|E^{{\rm CS},\rho,\pi}_{ik}
        +
        E^{{\rm CS},\rho,\pi}_{ij}E^{{\rm CS},\rho,\pi}_{ik}
      \right]
    \right)_{j,k=1}^{n}
  } .
\end{aligned}
\]

\begin{corollary}[Product-grid CountSketch sparse-Gram theorem with stored signs and permuted buckets]
Keep the product-grid hypotheses of the preceding stored-sign corollary, and
fix any exact bucket ordering \(\pi\) for every realized hash \(h\).  Let
\[
  \widehat G^{\rho_{\rm sig},\pi}(h,\omega;A)
\]
be the computed Gram formed by storing the signs with mode
\(\rho_{\rm sig}\), visiting each bucket in the chosen order, accumulating
the sparse products in that order, and then forming rounded length-\(r\) Gram
dot products.  Set
\[
  \tau_{{\rm pg},\rho_{\rm sig},\pi}^{\rm fp}(h,\omega;A)
  =
  \eta+L(2\rho+\rho^2)
  +
  T_{{\rm CSGram},\rho_{\rm sig},\pi}^{\rm fp}(h,\omega;A).
\]
If the floating-point model has valid \(\gamma_m\) and \(\gamma_r\), then
\[
\begin{aligned}
&\Prob_{h,\omega}
  \left[
    -\tau_{{\rm pg},\rho_{\rm sig},\pi}^{\rm fp}(h,\omega;A)\I_n
    \preceq
    \widehat G^{\rho_{\rm sig},\pi}(h,\omega;A)-A^TA
    \preceq
    \tau_{{\rm pg},\rho_{\rm sig},\pi}^{\rm fp}(h,\omega;A)\I_n
  \right]
\\
&\qquad\ge
  1-
  \left(
    \sum_{a:\{1,\ldots,n\}\to\mathcal I}
      \frac{2\Norm{Az_a}^4}{r\eta^2}
    +
      \frac{2\Frob{A}^4}{rL^2}
  \right).
\end{aligned}
\]
Equivalently, the same event has probability at least \(1-\delta\) whenever
the displayed product-grid loss is at most \(\delta\).

The exact objects are \(A\), \(h\), \(\omega\), the bucket order \(\pi\), the
grid vectors \(z_a\), and the reference \(A^TA\).  The computed
non-probability objects are the stored sign table, the rounded signed
products, the rounded bucket accumulations in the chosen order, and the
rounded Gram dot products.  For fixed realized \(h,\omega,\pi,A\),
\[
  E^{{\rm CS},\rho,\pi}_{ij}
  =
  \Theta\!\left(
    (u+\gamma_{b_i(h)})
    \sum_{t=1}^{b_i(h)}|A_{k_{i,t}j}|
  \right)
\]
for the three stored-sign modes, and
\[
  T_{{\rm CSGram},\rho,\pi}^{\rm fp}
  =
  \Theta\!\left(
    \gamma_r\Frob{|Y|^T|Y|}
    +
    \Frob{(E^{{\rm CS},\rho,\pi})^T|Y|
      +|Y|^TE^{{\rm CS},\rho,\pi}}
  \right)
\]
when the displayed leading term is nonzero.  The roundoff radius tends to zero
as \(u,\gamma_r,\gamma_{b_i}\to0\) for fixed realized data and fixed \(A\).
\end{corollary}

\subsection*{Stored CountSketch Signs with Tree-Reduced Bucket Accumulation}

The preceding stored-sign and permuted-bucket statements use a left-to-right
fold within each CountSketch bucket.  A parallel sparse implementation may
instead reduce the bucket entries by a binary summation tree.  For every
realized exact hash \(h\), define
\[
  B_i(h)=\{k:h(k)=i\},
  \qquad
  b_i(h)=|B_i(h)|,
\]
and fix an exact enumeration
\[
  k_{i,1},\ldots,k_{i,b_i(h)}
\]
of \(B_i(h)\).  For each bucket \(i\), let
\[
  \mathcal T_i(h)
\]
be an exact binary summation tree with \(b_i(h)+1\) leaves.  The first
\(b_i(h)\) leaves hold the rounded signed products, and the last leaf is the
exact zero padding value.  The zero padding is not a floating-point
operation; it is only a modeling convention that lets empty buckets use the
same tree statement.  Let
\[
  d_i(h)=\mathrm{depth}\bigl(\mathcal T_i(h)\bigr).
\]
The floating-point assumptions for this route are valid \(\gamma_{d_i(h)}\)
for every realized bucket tree and valid \(\gamma_r\) for each length-\(r\)
Gram dot product.

As before, the exact Rademacher signs are \(\omega_k\in\{-1,1\}\).  The
implemented sign table is
\[
  \widehat\omega^{\rho_{\rm sig}},
  \qquad
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
where the three modes store signs by \(\fl(\omega_k\cdot1)\),
\(\fl(\omega_k+0)\), or \(\fl(\omega_k-0)\).  Let \(e_k^{\rho_{\rm sig}}\)
be the certified storage radius satisfying
\[
  |\widehat\omega_k^{\rho_{\rm sig}}-\omega_k|
  \le e_k^{\rho_{\rm sig}} .
\]
For the three concrete modes above, \(e_k^{\rho_{\rm sig}}\le u\) because
\(|\omega_k|=1\).  Define the tree-reduced stored-sign sparse-apply entry
radius
\[
\begin{aligned}
  E^{{\rm CS},\rho,\mathcal T}_{ij}(h,\omega;A)
  &:=
  \bigl(u+\gamma_{d_i(h)}+u\gamma_{d_i(h)}\bigr)
  \sum_{t=1}^{b_i(h)}
    |\widehat\omega^{\rho_{\rm sig}}_{k_{i,t}}|\,|A_{k_{i,t}j}|
\\
  &\quad+
  \sum_{t=1}^{b_i(h)}
    e_{k_{i,t}}^{\rho_{\rm sig}}\,|A_{k_{i,t}j}|.
\end{aligned}
\]
The first line charges the rounded signed products and the rounded tree
reduction.  The second line charges the stored sign table.  The exact ideal
reference is still
\[
  Y_{ij}=\sum_{k:h(k)=i}\omega_k A_{kj}.
\]
Let \(\widehat Y^{\rho_{\rm sig},\mathcal T}\) be the computed sparse sketch
formed from the stored signs, rounded signed products, and the bucket trees.
The corresponding fully expanded deterministic Gram radius is
\[
\begin{aligned}
  T_{{\rm CSGram},\rho,\mathcal T}^{\rm fp}(h,\omega;A)
  &:=
  \Frob{
    \left(
      \gamma_r
      \sum_{i=1}^{r}
      \bigl(|Y_{ij}|+E^{{\rm CS},\rho,\mathcal T}_{ij}\bigr)
      \bigl(|Y_{ik}|+E^{{\rm CS},\rho,\mathcal T}_{ik}\bigr)
    \right)_{j,k=1}^{n}
  }
\\
  &\quad+
  \Frob{
    \left(
      \sum_{i=1}^{r}
      \left[
        E^{{\rm CS},\rho,\mathcal T}_{ij}|Y_{ik}|
        +
        |Y_{ij}|E^{{\rm CS},\rho,\mathcal T}_{ik}
        +
        E^{{\rm CS},\rho,\mathcal T}_{ij}
          E^{{\rm CS},\rho,\mathcal T}_{ik}
      \right]
    \right)_{j,k=1}^{n}
  } .
\end{aligned}
\]

\begin{corollary}[Product-grid CountSketch sparse-Gram theorem with stored signs and tree reductions]
Keep the product-grid hypotheses of the stored-sign corollary, and fix exact
bucket trees \(\mathcal T_i(h)\) for every realized hash \(h\).  Let
\[
  \widehat G^{\rho_{\rm sig},\mathcal T}(h,\omega;A)
  =
  \fl\!\left(
    (\widehat Y^{\rho_{\rm sig},\mathcal T})^T
    \widehat Y^{\rho_{\rm sig},\mathcal T}
  \right)
\]
be the computed Gram whose length-\(r\) dot products are rounded.  Set
\[
  \tau_{{\rm pg},\rho_{\rm sig},\mathcal T}^{\rm fp}(h,\omega;A)
  =
  \eta+L(2\rho+\rho^2)
  +
  T_{{\rm CSGram},\rho_{\rm sig},\mathcal T}^{\rm fp}(h,\omega;A).
\]
If the floating-point model has valid \(\gamma_{d_i(h)}\) for every bucket
tree and valid \(\gamma_r\), then
\[
\begin{aligned}
&\Prob_{h,\omega}
  \left[
    -\tau_{{\rm pg},\rho_{\rm sig},\mathcal T}^{\rm fp}(h,\omega;A)\I_n
    \preceq
    \widehat G^{\rho_{\rm sig},\mathcal T}(h,\omega;A)-A^TA
    \preceq
    \tau_{{\rm pg},\rho_{\rm sig},\mathcal T}^{\rm fp}(h,\omega;A)\I_n
  \right]
\\
&\qquad\ge
  1-
  \left(
    \sum_{a:\{1,\ldots,n\}\to\mathcal I}
      \frac{2\Norm{Az_a}^4}{r\eta^2}
    +
      \frac{2\Frob{A}^4}{rL^2}
  \right).
\end{aligned}
\]
Equivalently, the same event has probability at least \(1-\delta\) whenever
the displayed product-grid loss is at most \(\delta\).

The exact objects are \(A\), \(h\), \(\omega\), the product-grid vectors
\(z_a\), the reference \(A^TA\), and the tree shapes
\(\mathcal T_i(h)\).  These tree shapes are exact discrete algorithm choices,
not floating-point real computations.  The computed non-probability objects
are the stored sign table, the rounded signed products, the rounded
tree-reduced bucket accumulations, and the rounded Gram dot products.

For fixed realized \(h,\omega,\mathcal T,A\), and for the three concrete
stored-sign modes, the entry budget has small-roundoff order
\[
  E^{{\rm CS},\rho,\mathcal T}_{ij}
  =
  \Theta\!\left(
    (u+\gamma_{d_i(h)})
    \sum_{t=1}^{b_i(h)}|A_{k_{i,t}j}|
  \right)
\]
whenever the displayed bucket-column absolute sum is nonzero.  If balanced
trees are selected, so that
\[
  d_i(h)=\Theta\!\bigl(\log(b_i(h)+1)\bigr),
\]
then \(\gamma_{d_i(h)}=\Theta(u\log(b_i(h)+1))\) in the usual small-\(u\)
regime, and therefore
\[
  E^{{\rm CS},\rho,\mathcal T}_{ij}
  =
  \Theta\!\left(
    u(1+\log(b_i(h)+1))
    \sum_{t=1}^{b_i(h)}|A_{k_{i,t}j}|
  \right).
\]
The deterministic Gram radius satisfies
\[
  T_{{\rm CSGram},\rho,\mathcal T}^{\rm fp}
  =
  \Theta\!\left(
    \gamma_r\Frob{|Y|^T|Y|}
    +
    \Frob{(E^{{\rm CS},\rho,\mathcal T})^T|Y|
      +|Y|^TE^{{\rm CS},\rho,\mathcal T}}
  \right)
\]
when the displayed leading term is nonzero; the exact expanded formula above
retains the higher-order \(E^TE\) and \(\gamma_r E\)-dependent terms.  The
probability-loss order is unchanged,
\[
  \Theta\!\left(
    \frac{
      \sum_a\Norm{Az_a}^4/\eta^2+\Frob{A}^4/L^2
    }{r}
  \right)
\]
for fixed exact input/grid/threshold data and nonzero numerator.  The result
is non-vacuous whenever the displayed product-grid loss is below one, and the
deterministic roundoff radius tends to zero as
\[
  u,\gamma_r,\gamma_{d_i(h)},e_k^{\rho_{\rm sig}}\longrightarrow0
\]
for fixed realized data and fixed exact \(A\).
\end{corollary}

\begin{corollary}[Product-grid CountSketch sparse-Gram theorem]
Let \(A\in\R^{m\times n}\) be the exact input matrix handed to Algorithm 3.
Let \(\mathcal I\) be a finite exact index set, and let
\[
  g:\mathcal I\to\R
\]
be an exact one-dimensional grid that covers \([-1,1]\) with radius
\(\delta_{\rm grid}\).  Assume
\[
  \delta_{\rm grid}\ge0,
  \qquad
  \sqrt n\,\delta_{\rm grid}\le\rho,
  \qquad
  \eta>0,
  \qquad
  L>0.
\]
For each product-grid index \(a:\{1,\ldots,n\}\to\mathcal I\), define
\[
  z_a(j)=g(a(j)),\qquad j=1,\ldots,n .
\]
Then \(\{z_a\}\) is an exact \(\rho\)-cover of the Euclidean unit ball in
\(\R^n\), and it has cardinality \(|\mathcal I|^n\).

Set
\[
  \tau_{\rm pg}^{\rm fp}(h,\omega;A)
  =
  \eta+L(2\rho+\rho^2)+T_{\rm CSGram}^{\rm fp}(h,\omega;A).
\]
If the floating-point model has valid \(\gamma_m\) and \(\gamma_r\), then
\[
\begin{aligned}
&\Prob_{h,\omega}
  \left[
    -\tau_{\rm pg}^{\rm fp}(h,\omega;A)\I_n
    \preceq
    \widehat G(h,\omega;A)-A^TA
    \preceq
    \tau_{\rm pg}^{\rm fp}(h,\omega;A)\I_n
  \right]
\\
&\qquad\ge
  1-
  \left(
    \sum_{a:\{1,\ldots,n\}\to\mathcal I}
      \frac{2\Norm{Az_a}^4}{r\eta^2}
    +
      \frac{2\Frob{A}^4}{rL^2}
  \right).
\end{aligned}
\]
Equivalently, if the displayed product-grid loss is at most \(\delta\), the
same computed sparse-Gram Loewner event has probability at least
\(1-\delta\).

All quantities in the product-grid loss are exact arithmetic analysis
quantities: \(A\), the grid \(g\), the product vectors \(z_a\), and the exact
hash/sign law.  The computed non-probability quantities are precisely
\(\widehat Y\) and \(\widehat G\), and their floating-point errors are charged
by the expanded \(T_{\rm CSGram}^{\rm fp}\) above.

For fixed exact \(A\), fixed grid \(g\), and fixed positive \(\eta,L\), the
probability loss has order
\[
  \Theta\!\left(
    \frac{
      \sum_{a:\{1,\ldots,n\}\to\mathcal I}\Norm{Az_a}^4/\eta^2
      +
      \Frob{A}^4/L^2
    }{r}
  \right)
\]
when the numerator is nonzero, and it is exactly zero when the numerator is
zero.  The probability bound is non-vacuous whenever the displayed loss is
less than one.  The floating-point radius is non-vacuous because
\[
  T_{\rm CSGram}^{\rm fp}(h,\omega;A)\to0
  \quad\text{as}\quad
  u,\gamma_r,\gamma_{b_i(h)}\to0
\]
for fixed realized \(h,\omega\) and fixed exact input \(A\).
\end{corollary}

\begin{corollary}[Orthonormal product-grid CountSketch sparse-Gram theorem]
Keep the exact CountSketch product-grid notation above.  Let
\(U\in\R^{m\times n}\) be an exact orthonormal-column analysis matrix,
\[
  U^TU=\I_n .
\]
For each product-grid index \(a:\{1,\ldots,n\}\to\mathcal I\), define the
exact grid vector
\[
  z_a(j)=g(a(j)).
\]
Because \(U\) has orthonormal columns,
\[
  \Norm{Uz_a}^2=\Norm{z_a}^2,
  \qquad
  \Frob{U}^2=n .
\]
Thus the exact product-grid probability loss reduces to the irreducible
orthonormal form
\[
  \mathcal L_{\rm pg}^{\rm orth}
  =
  \sum_{a:\{1,\ldots,n\}\to\mathcal I}
    \frac{2\Norm{z_a}^4}{r\eta^2}
  +
    \frac{2n^2}{rL^2}.
\]
Let
\[
  \tau_{\rm pg}^{\rm fp}(h,\omega;U)
  =
  \eta+L(2\rho+\rho^2)+T_{\rm CSGram}^{\rm fp}(h,\omega;U),
\]
where \(T_{\rm CSGram}^{\rm fp}\) is the sparse-apply and rounded-Gram
radius defined above.  If the floating-point model has valid \(\gamma_m\) and
\(\gamma_r\), then
\[
\begin{aligned}
&\Prob_{h,\omega}
  \left[
    -\tau_{\rm pg}^{\rm fp}(h,\omega;U)\I_n
    \preceq
    \widehat G(h,\omega;U)-\I_n
    \preceq
    \tau_{\rm pg}^{\rm fp}(h,\omega;U)\I_n
  \right]
\\
&\qquad\ge
  1-\mathcal L_{\rm pg}^{\rm orth}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg}^{\rm orth}\le\delta\), the same
computed sparse-Gram Loewner event has probability at least \(1-\delta\).

For the stored-sign implementation path, let
\(\rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}\), store the
realized signs as \(\widehat\omega^{\rho_{\rm sig}}\), and replace
\(T_{\rm CSGram}^{\rm fp}\) by
\(T_{{\rm CSGram},\rho_{\rm sig}}^{\rm fp}\).  Then the same probability loss
\(\mathcal L_{\rm pg}^{\rm orth}\) holds for the stored-sign computed event
\[
  -\tau_{{\rm pg},\rho_{\rm sig}}^{\rm fp}(h,\omega;U)\I_n
  \preceq
  \widehat G^{\rho_{\rm sig}}(h,\omega;U)-\I_n
  \preceq
  \tau_{{\rm pg},\rho_{\rm sig}}^{\rm fp}(h,\omega;U)\I_n,
\]
where
\[
  \tau_{{\rm pg},\rho_{\rm sig}}^{\rm fp}(h,\omega;U)
  =
  \eta+L(2\rho+\rho^2)
  +
  T_{{\rm CSGram},\rho_{\rm sig}}^{\rm fp}(h,\omega;U).
\]
The exact objects are \(U\), the grid \(g\), the product-grid vectors \(z_a\),
and the hash/sign probability law.  In the stored-sign path, the computed
non-probability objects are the stored sign table, sparse signed products,
bucket accumulations, and rounded Gram dot products.  The statement does not
charge probability construction, and it does not rely on an auxiliary
perturbation event or supplied certificate.

For fixed exact grid and fixed positive \(\eta,L\), the irreducible
probability-loss order is
\[
  \mathcal L_{\rm pg}^{\rm orth}
  =
  \Theta\!\left(
    \frac{
      \sum_{a:\{1,\ldots,n\}\to\mathcal I}\Norm{z_a}^4/\eta^2
      +
      n^2/L^2
    }{r}
  \right)
\]
when the numerator is nonzero, and the loss is exactly zero when the numerator
is zero.  The result is non-vacuous whenever
\(\mathcal L_{\rm pg}^{\rm orth}<1\).  The deterministic floating-point radius
tends to zero as the relevant \(u,\gamma_r,\gamma_{b_i(h)}\), and stored-sign
copy radii tend to zero for fixed realized data.
\end{corollary}

\subsection*{Downstream Uniform Rows After CountSketch}

After the CountSketch preprocessing, Algorithm 3 may sample \(s\) rows from
the \(r\)-row sketched matrix.  Let
\[
  \sigma=(\sigma_1,\ldots,\sigma_s),
  \qquad
  \sigma_q\in\{1,\ldots,r\},
\]
be exact iid uniform row indices.  Define the exact denominator
\[
  d=\sqrt{s/r}.
\]
The concrete denominator routine used here computes
\[
  \widehat d
  =
  \fl\!\left(
    \sqrt{s}\,
    \fl\!\left(\frac{1}{\sqrt r}\right)
  \right),
\]
implemented as
\[
  \fl_{\rm mul}\!\left(
    \fl_{\rm sqrt}(s),
    \fl_{\rm div}\!\left(1,\fl_{\rm sqrt}(r)\right)
  \right),
\]
and the proved denominator error radius is
\[
  E_d
  =
  d\,\frac{4u+3u^2+u^3}{1-u},
  \qquad
  |\widehat d-d|\le E_d.
\]
Assume \(\widehat d\ne0\), which is part of the concrete denominator
certificate.

For a realized \(h,\omega,\sigma\), define the exact scaled sampled rows
\[
  B_{qj}
  =
  \frac{Y_{\sigma_q j}}{d},
  \qquad
  q=1,\ldots,s,\quad j=1,\ldots,n.
\]
The implementation uses the already computed sparse sketch \(\widehat Y\) and
forms
\[
  \widehat B_{qj}
  =
  \fl\!\left(\frac{\widehat Y_{\sigma_q j}}{\widehat d}\right).
\]
An explicit entrywise radius for this sampled-row scaling is
\[
  E^B_{qj}
  =
  \frac{u|\widehat Y_{\sigma_q j}|}{|\widehat d|}
  +
  \frac{E^{\rm CS}_{\sigma_q j}}{|\widehat d|}
  +
  \frac{|Y_{\sigma_q j}|E_d}{|\widehat d|\,|d|}.
\]
The first term charges the rounded division by \(\widehat d\), the second term
propagates the computed sparse-apply error, and the third term charges the
computed denominator.

The final sampled Gram is
\[
  \widehat G_{\rm row}(h,\omega,\sigma;A)
  =
  \fl\!\left(\widehat B^T\widehat B\right),
\]
with rounded length-\(s\) dot products.  Its fully expanded deterministic
floating-point radius is
\[
\begin{aligned}
  T_{\rm CS,row}^{\rm fp}
  &:=
  \Frob{
    \left(
      \gamma_s
      \sum_{q=1}^{s}
        \bigl(|B_{qj}|+E^B_{qj}\bigr)
        \bigl(|B_{qk}|+E^B_{qk}\bigr)
    \right)_{j,k=1}^{n}
  }
  \\
  &\quad+
  \Frob{
    \left(
      \sum_{q=1}^{s}
      \left[
        E^B_{qj}|B_{qk}|
        +
        |B_{qj}|E^B_{qk}
        +
        E^B_{qj}E^B_{qk}
      \right]
    \right)_{j,k=1}^{n}
  } .
\end{aligned}
\]
For fixed realized \(h,\omega,\sigma,A\), this radius tends to zero as
\[
  u,\gamma_s,\gamma_{b_i(h)},E_d\longrightarrow0 .
\]

\begin{corollary}[Product-grid CountSketch plus downstream uniform rows]
Keep the hypotheses and product-grid notation of the preceding CountSketch
corollary.  Let \(\eta_{\rm row}>0\), and set
\[
  \tau_{\rm CS}=\eta+L(2\rho+\rho^2).
\]
Then the fully computed downstream sampled Gram satisfies
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{\rm CS,row}^{\rm fp}\bigr)\I_n
    \preceq
    \widehat G_{\rm row}(h,\omega,\sigma;A)-A^TA
  \right.
\\[-2pt]
&\left.\hspace{4.4cm}
    \preceq
    \bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{\rm CS,row}^{\rm fp}\bigr)\I_n
  \right]
\\
&\qquad\ge
  1-\mathcal L_{\rm pg,row},
\end{aligned}
\]
where the exact product-grid loss is
\[
\begin{aligned}
  \mathcal L_{\rm pg,row}
  &:=
  \sum_{a:\{1,\ldots,n\}\to\mathcal I}
    \frac{2}{r\eta^2}
      \sum_{p\ne q}
        \bigl((Az_a)_p(Az_a)_q\bigr)^2
\\
&\quad+
  \frac{2}{rL^2}
    \sum_{j,k=1}^{n}\sum_{p\ne q}
      (A_{pj}A_{qk})^2
  +
  \frac{r\,m^2\Frob{A}^4}{s\eta_{\rm row}^2}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg,row}\le\delta\), then the displayed
fully computed event has probability at least \(1-\delta\).

The exact objects are \(A\), the product grid \(z_a\), the exact hash/sign
law, and the exact uniform row-sampling law.  The computed non-probability
objects are \(\widehat Y\), \(\widehat d\), \(\widehat B\), and
\(\widehat G_{\rm row}\).  Their errors are charged by
\(E^{\rm CS}\), \(E_d\), \(E^B\), and the expanded
\(T_{\rm CS,row}^{\rm fp}\).

In the fixed exact-input/grid/threshold regime, the probability loss has order
\[
  \Theta\!\left(
    \sum_{a:\{1,\ldots,n\}\to\mathcal I}
      \frac{\sum_{p\ne q}((Az_a)_p(Az_a)_q)^2}{r\eta^2}
    +
    \frac{\sum_{j,k=1}^{n}\sum_{p\ne q}(A_{pj}A_{qk})^2}{rL^2}
    +
    \frac{r\,m^2\Frob{A}^4}{s\eta_{\rm row}^2}
  \right)
\]
when the displayed numerator is nonzero.  The result is non-vacuous whenever
\(\mathcal L_{\rm pg,row}<1\), and its deterministic floating-point radius
vanishes when the charged roundoff and denominator errors vanish.
\end{corollary}

\begin{corollary}[Product-grid CountSketch plus downstream uniform rows with stored signs]
Keep the exact product-grid notation above, and let the CountSketch signs be
stored by one of the concrete routines
\[
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}.
\]
Thus \(\widehat\omega^{\rho_{\rm sig}}\) is respectively formed by
\(\fl(\omega_k\cdot1)\), \(\fl(\omega_k+0)\), or \(\fl(\omega_k-0)\), and
\[
  E^{{\rm CS},\rho_{\rm sig}}_{ij}
  =
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{k:h(k)=i}|\widehat\omega_k^{\rho_{\rm sig}}|\,|A_{kj}|
  +
  u\sum_{k:h(k)=i}|A_{kj}|
\]
is the stored-sign sparse-apply entry radius defined before the sparse-Gram
corollary.

For a realized row trace \(\sigma=(\sigma_1,\ldots,\sigma_s)\), define
\[
  \widehat Y^{\rho_{\rm sig}}= \fl(S_{h,\widehat\omega^{\rho_{\rm sig}}}A),
  \qquad
  \widetilde B^{\rho_{\rm sig}}_{qj}
  =
  \frac{\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}}{d},
  \qquad
  \widehat B^{\rho_{\rm sig}}_{qj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}}{\widehat d}
  \right).
\]
The exact reference \(B_{qj}=Y_{\sigma_qj}/d\) uses the exact CountSketch
signs and the exact denominator.  The computed-denominator row entry radius
for the stored-sign computed sketch is
\[
  E^{{\rm den},\rho_{\rm sig}}_{qj}
  =
  |\widehat B^{\rho_{\rm sig}}_{qj}|\,u
  +
  \frac{|\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}|\,E_d}
       {|\widehat d|\,|d|}.
\]
The stored-sign basis perturbation sampled at row \(q\) is
\[
  F^{\rho_{\rm sig}}_{qj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig}}_{\sigma_qj}}{d}.
\]
Now define the irreducible deterministic downstream radius
\[
  T_{{\rm CS,row},\rho_{\rm sig}}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig}}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig}}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig}}^{\rm fp},
\]
where
\[
  T_{{\rm den},\rho_{\rm sig}}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      E^{{\rm den},\rho_{\rm sig}}_{qj}
        |\widehat B^{\rho_{\rm sig}}_{qk}|
      +
      |\widetilde B^{\rho_{\rm sig}}_{qj}|
        E^{{\rm den},\rho_{\rm sig}}_{qk}
    \right)_{j,k=1}^{n}
  },
\]
\[
  T_{{\rm dot},\rho_{\rm sig}}^{\rm fp}
  =
  \Frob{
    \left(
      \gamma_s\sum_{q=1}^{s}
      |\widehat B^{\rho_{\rm sig}}_{qj}|
      |\widehat B^{\rho_{\rm sig}}_{qk}|
    \right)_{j,k=1}^{n}
  },
\]
and
\[
  T_{{\rm basis},\rho_{\rm sig}}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      F^{\rho_{\rm sig}}_{qj}
        |\widetilde B^{\rho_{\rm sig}}_{qk}|
      +
      |B_{qj}|F^{\rho_{\rm sig}}_{qk}
    \right)_{j,k=1}^{n}
  }.
\]

With \(\eta_{\rm row}>0\) and
\[
  \tau_{\rm CS}=\eta+L(2\rho+\rho^2),
\]
the fully computed stored-sign downstream sampled Gram
\[
  \widehat G_{\rm row}^{\rho_{\rm sig}}(h,\omega,\sigma;A)
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig}})^T
    \widehat B^{\rho_{\rm sig}}
  \right)
\]
satisfies
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig}}^{\rm fp}\bigr)\I_n
    \preceq
    \widehat G_{\rm row}^{\rho_{\rm sig}}(h,\omega,\sigma;A)-A^TA
  \right.
\\[-2pt]
&\left.\hspace{4.2cm}
    \preceq
    \bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig}}^{\rm fp}\bigr)\I_n
  \right]
\\
&\qquad\ge
  1-\mathcal L_{\rm pg,row}.
\end{aligned}
\]
Equivalently, if the exact loss \(\mathcal L_{\rm pg,row}\) displayed in the
preceding corollary is at most \(\delta\), then this stored-sign fully
computed event has probability at least \(1-\delta\).

The exact objects are \(A\), the product grid \(z_a\), the exact CountSketch
hash/sign law, and the exact uniform row-sampling law.  The computed
non-probability objects are \(\widehat\omega^{\rho_{\rm sig}}\),
\(\widehat Y^{\rho_{\rm sig}}\), \(\widehat d\),
\(\widehat B^{\rho_{\rm sig}}\), and
\(\widehat G_{\rm row}^{\rho_{\rm sig}}\).  No perturbation event or
extra existence assumption is supplied.

For fixed realized \(h,\omega,\sigma,A\), fixed exact denominator \(d>0\),
and nonzero leading deterministic coefficient,
\[
  \begin{aligned}
  T_{{\rm CS,row},\rho_{\rm sig}}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s
      \Frob{|\widehat B^{\rho_{\rm sig}}|^T
            |\widehat B^{\rho_{\rm sig}}|}
  \\
  &+
    \Frob{(E^{{\rm den},\rho_{\rm sig}})^T
          |\widehat B^{\rho_{\rm sig}}|
          +
          |\widetilde B^{\rho_{\rm sig}}|^T
          E^{{\rm den},\rho_{\rm sig}}}
  \\
  &+
    \Frob{(F^{\rho_{\rm sig}})^T
          |\widetilde B^{\rho_{\rm sig}}|
          +
          |B|^TF^{\rho_{\rm sig}}}
  \Big).
  \end{aligned}
\]
Substituting the irreducible definitions,
\[
  E^{{\rm den},\rho_{\rm sig}}_{qj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig}}_{qj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}|}{|\widehat d|\,|d|}
    d\,\frac{4u+3u^2+u^3}{1-u}
  \right),
\]
and
\[
  F^{\rho_{\rm sig}}_{qj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{b_{\sigma_q}(h)}}{d}
    \sum_{k:h(k)=\sigma_q}|A_{kj}|
  \right).
\]
Thus, in the small-roundoff regime with fixed realized data,
\[
  T_{{\rm CS,row},\rho_{\rm sig}}^{\rm fp}
  \to0
  \quad\text{as}\quad
  u,\gamma_s,\gamma_{b_i(h)},\frac{4u+3u^2+u^3}{1-u}\to0.
\]
The probability-loss order remains the same \(\Theta\)-order as in the
preceding downstream corollary, because sign storage is a deterministic
floating-point radius and not a probability-law perturbation.
\end{corollary}

\begin{corollary}[Orthonormal product-grid CountSketch plus downstream uniform rows with stored signs]
Keep the product-grid, stored-sign, and downstream row notation introduced
above.  Now specialize the exact input to an orthonormal-column analysis
matrix \(U\in\R^{m\times n}\), so
\[
  U^TU=\I_n .
\]
For each product-grid index \(a:\{1,\ldots,n\}\to\mathcal I\), keep
\[
  z_a(j)=g(a(j)).
\]
The orthonormal identities
\[
  \Norm{Uz_a}^2=\Norm{z_a}^2,
  \qquad
  \Frob{U}^2=n
\]
turn the stored-sign downstream product-grid loss into
\[
\begin{aligned}
  \mathcal L_{\rm pg,row}^{\rm orth}
  &:=
  \sum_{a:\{1,\ldots,n\}\to\mathcal I}
    \frac{2\Norm{z_a}^4}{r\eta^2}
  +
    \frac{2n^2}{rL^2}
  +
    \frac{r(mn)^2}{s\eta_{\rm row}^2}.
\end{aligned}
\]
Let \(\rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\}\) be
one of the three stored-sign copy routines defined above, and let
\[
  \tau_{{\rm pg,row},\rho_{\rm sig}}^{\rm fp}(h,\omega,\sigma;U)
  =
  \eta+L(2\rho+\rho^2)
  +\eta_{\rm row}
  +T_{{\rm CS,row},\rho_{\rm sig}}^{\rm fp}(h,\omega,\sigma;U).
\]
Then the fully computed stored-sign downstream sampled Gram satisfies
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\tau_{{\rm pg,row},\rho_{\rm sig}}^{\rm fp}(h,\omega,\sigma;U)\I_n
    \preceq
    \widehat G_{\rm row}^{\rho_{\rm sig}}(h,\omega,\sigma;U)-\I_n
  \right.
\\[-2pt]
&\left.\hspace{4.5cm}
    \preceq
    \tau_{{\rm pg,row},\rho_{\rm sig}}^{\rm fp}(h,\omega,\sigma;U)\I_n
  \right]
\\
&\qquad\ge
  1-\mathcal L_{\rm pg,row}^{\rm orth}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg,row}^{\rm orth}\le\delta\), the same
fully computed event has probability at least \(1-\delta\).

The exact objects are \(U\), the product grid \(g\), the grid vectors \(z_a\),
the exact CountSketch hash/sign law, and the exact downstream uniform-row law.
The computed non-probability objects are the stored sign table,
\(\widehat Y^{\rho_{\rm sig}}\), the concrete denominator \(\widehat d\),
the rounded sampled rows \(\widehat B^{\rho_{\rm sig}}\), and the rounded
sampled Gram \(\widehat G_{\rm row}^{\rho_{\rm sig}}\).  The displayed
radius charges sign storage, sparse signed products, bucket accumulation,
denominator formation, row divisions, and sampled-Gram dot products.

For fixed exact grid and fixed positive \(\eta,L,\eta_{\rm row}\), the
irreducible probability-loss order is
\[
  \mathcal L_{\rm pg,row}^{\rm orth}
  =
  \Theta\!\left(
    \frac{
      \sum_{a:\{1,\ldots,n\}\to\mathcal I}\Norm{z_a}^4/\eta^2
      +
      n^2/L^2
    }{r}
    +
    \frac{r\,m^2n^2}{s\eta_{\rm row}^2}
  \right)
\]
when the displayed numerator is nonzero.  The result is non-vacuous whenever
\(\mathcal L_{\rm pg,row}^{\rm orth}<1\).  For fixed realized data, its
deterministic floating-point radius tends to zero as the unit roundoff,
\(\gamma_s\), the bucket-accumulation \(\gamma\)-factors, and the denominator
error tend to zero.
\end{corollary}

\begin{corollary}[Orthonormal product-grid downstream uniform rows with fixed-order or tree-reduced buckets]
Keep the exact orthonormal input \(U\), product-grid vectors \(z_a\), and
loss \(\mathcal L_{\rm pg,row}^{\rm orth}\) from the preceding corollary.
For every realized exact hash \(h\), consider either of the following exact
discrete layout choices.

First, a fixed-order layout \(\pi\) specifies, for every bucket \(i\), an
ordering of the exact bucket set \(B_i(h)=\{k:h(k)=i\}\).  Second, a
tree-reduced layout \(\mathcal T\) specifies, for every bucket \(i\), an exact
binary summation tree with depth \(d_i^{\mathcal T}(h)\).  The choices
\(\pi\) and \(\mathcal T\) are exact discrete inputs, not floating-point
computations.  Arithmetic performed along the chosen order or tree is
floating-point arithmetic and is charged in the deterministic radius.

Let
\[
  \ell\in\{\pi,\mathcal T\}
\]
denote one of these two layouts.  For a stored-sign routine
\[
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
write
\[
  \widehat Y^{\rho_{\rm sig},\ell}(h,\omega;U)
\]
for the computed sparse CountSketch basis obtained from \(U\) by storing the
realized signs, forming rounded signed products, and accumulating each bucket
according to layout \(\ell\).  The downstream sampled rows use the concrete
computed denominator
\[
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt r))
  \right),
\]
then round the row divisions and the sampled-Gram dot products.  Let the final
computed sampled Gram be
\[
  \widehat G_{{\rm row}}^{\rho_{\rm sig},\ell}(h,\omega,\sigma;U).
\]

Define
\[
  \tau_{{\rm pg,row},\rho_{\rm sig},\ell}^{\rm fp}
  (h,\omega,\sigma;U)
  =
  \eta+L(2\rho+\rho^2)
  +\eta_{\rm row}
  +T_{{\rm CS,row},\rho_{\rm sig},\ell}^{\rm fp}(h,\omega,\sigma;U),
\]
where \(T_{{\rm CS,row},\rho_{\rm sig},\pi}^{\rm fp}\) charges stored signs,
rounded sparse products, fixed-order bucket accumulation, denominator
formation, sampled-row divisions, and sampled-Gram dot products, while
\(T_{{\rm CS,row},\rho_{\rm sig},\mathcal T}^{\rm fp}\) charges the same
operations with the bucket-accumulation \(\gamma\)-factor replaced by the
tree-depth factors \(\gamma_{d_i^{\mathcal T}(h)}\).  The tree-reduced
statement assumes these tree-depth \(\gamma\)-factors are valid.

Then, for either \(\ell=\pi\) or \(\ell=\mathcal T\),
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\tau_{{\rm pg,row},\rho_{\rm sig},\ell}^{\rm fp}
      (h,\omega,\sigma;U)\I_n
    \preceq
    \widehat G_{{\rm row}}^{\rho_{\rm sig},\ell}(h,\omega,\sigma;U)-\I_n
  \right.
\\[-2pt]
&\left.\hspace{4.5cm}
    \preceq
    \tau_{{\rm pg,row},\rho_{\rm sig},\ell}^{\rm fp}
      (h,\omega,\sigma;U)\I_n
  \right]
\\
&\qquad\ge
  1-\mathcal L_{\rm pg,row}^{\rm orth}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg,row}^{\rm orth}\le\delta\), the same
fully computed layout-specific event has probability at least \(1-\delta\).

The exact objects are \(U\), the grid \(g\), the vectors \(z_a\), the exact
hash/sign laws, the exact downstream row law, and the exact layout choice
\(\ell\).  The computed non-probability objects are the stored signs,
layout-specific sparse products and bucket accumulations, \(\widehat d_\star\),
the rounded sampled rows, and the rounded sampled Gram.  No probability
construction is charged, and no auxiliary perturbation event is supplied.

The probability-loss order is the same irreducible order as in the preceding
corollary,
\[
  \mathcal L_{\rm pg,row}^{\rm orth}
  =
  \Theta\!\left(
    \frac{
      \sum_{a:\{1,\ldots,n\}\to\mathcal I}\Norm{z_a}^4/\eta^2
      +
      n^2/L^2
    }{r}
    +
    \frac{r\,m^2n^2}{s\eta_{\rm row}^2}
  \right),
\]
for fixed exact grid and fixed positive \(\eta,L,\eta_{\rm row}\) when the
displayed numerator is nonzero.  For fixed realized data, the layout-specific
deterministic radius tends to zero as the unit roundoff, \(\gamma_s\),
the fixed-order bucket \(\gamma\)-factors, or the tree-depth
\(\gamma\)-factors, and the denominator error tend to zero.
\end{corollary}

\begin{corollary}[Product-grid CountSketch plus downstream uniform rows with stored signs and permuted buckets]
Keep the exact product-grid notation and exact loss
\(\mathcal L_{\rm pg,row}\) from the preceding downstream corollaries.  Let
the CountSketch signs be stored by
\[
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
so each stored sign satisfies
\[
  |\widehat\omega_k^{\rho_{\rm sig}}-\omega_k|\le u .
\]
For each realized exact hash \(h\), fix an exact bucket order
\[
  k_{i,1},\ldots,k_{i,b_i(h)}
  \quad\text{of}\quad
  B_i(h)=\{k:h(k)=i\}.
\]
The order is an exact discrete memory-layout input and is not a
floating-point quantity.

The exact sparse sketch is
\[
  Y_{ij}
  =
  \sum_{t=1}^{b_i(h)}\omega_{k_{i,t}}A_{k_{i,t}j}.
\]
The computed sparse sketch
\[
  \widehat Y^{\rho_{\rm sig},\pi}
  =
  \fl_\pi(S_{h,\widehat\omega^{\rho_{\rm sig}}}A)
\]
stores the signs, forms rounded signed products, and accumulates the selected
bucket entries in the chosen order \(\pi\).  Its entrywise radius is
\[
\begin{aligned}
  E^{{\rm CS},\rho_{\rm sig},\pi}_{ij}
  &:=
  \bigl(u+\gamma_{b_i(h)}+u\gamma_{b_i(h)}\bigr)
  \sum_{t=1}^{b_i(h)}
    |\widehat\omega^{\rho_{\rm sig}}_{k_{i,t}}|\,|A_{k_{i,t}j}|
  \\
  &\quad+
  u\sum_{t=1}^{b_i(h)}|A_{k_{i,t}j}|.
\end{aligned}
\]

Let the downstream exact row trace be
\(\sigma=(\sigma_1,\ldots,\sigma_s)\), where each
\(\sigma_q\in\{1,\ldots,r\}\) is drawn from the exact uniform law.  Set
\[
  d=\sqrt{s/r},
  \qquad
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt r))
  \right),
\]
and assume the concrete denominator certificate
\[
  \widehat d_\star\ne0,\qquad
  |\widehat d_\star-d|
  \le
  d\,\Delta_\star,
  \qquad
  \Delta_\star=\frac{4u+3u^2+u^3}{1-u}.
\]
Define
\[
  B_{qj}=\frac{Y_{\sigma_qj}}{d},
  \qquad
  \widetilde B^{\rho_{\rm sig},\pi}_{qj}
  =
  \frac{\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_qj}}{d},
\]
and
\[
  \widehat B^{\rho_{\rm sig},\pi}_{qj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_qj}}
         {\widehat d_\star}
  \right).
\]
The computed-denominator row entry radius is
\[
  E^{{\rm den},\rho_{\rm sig},\pi}_{qj}
  =
  u|\widehat B^{\rho_{\rm sig},\pi}_{qj}|
  +
  \frac{|\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_qj}|}
       {|\widehat d_\star|}\,\Delta_\star ,
\]
and the sampled sparse-sketch basis perturbation is
\[
  F^{\rho_{\rm sig},\pi}_{qj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig},\pi}_{\sigma_qj}}{d}.
\]

Define the deterministic downstream floating-point radius by
\[
  T_{{\rm CS,row},\rho_{\rm sig},\pi}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig},\pi}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig},\pi}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig},\pi}^{\rm fp},
\]
where
\[
  T_{{\rm den},\rho_{\rm sig},\pi}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      E^{{\rm den},\rho_{\rm sig},\pi}_{qj}
        |\widehat B^{\rho_{\rm sig},\pi}_{qk}|
      +
      |\widetilde B^{\rho_{\rm sig},\pi}_{qj}|
        E^{{\rm den},\rho_{\rm sig},\pi}_{qk}
    \right)_{j,k=1}^{n}
  },
\]
\[
  T_{{\rm dot},\rho_{\rm sig},\pi}^{\rm fp}
  =
  \Frob{
    \left(
      \gamma_s\sum_{q=1}^{s}
      |\widehat B^{\rho_{\rm sig},\pi}_{qj}|
      |\widehat B^{\rho_{\rm sig},\pi}_{qk}|
    \right)_{j,k=1}^{n}
  },
\]
and
\[
  T_{{\rm basis},\rho_{\rm sig},\pi}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      F^{\rho_{\rm sig},\pi}_{qj}
        |\widetilde B^{\rho_{\rm sig},\pi}_{qk}|
      +
      |B_{qj}|F^{\rho_{\rm sig},\pi}_{qk}
    \right)_{j,k=1}^{n}
  }.
\]

With \(\eta_{\rm row}>0\) and
\[
  \tau_{\rm CS}=\eta+L(2\rho+\rho^2),
\]
the fully computed sampled Gram
\[
  \widehat G_{\rm row}^{\rho_{\rm sig},\pi}(h,\omega,\sigma;A)
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig},\pi})^T
    \widehat B^{\rho_{\rm sig},\pi}
  \right)
\]
satisfies
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig},\pi}^{\rm fp}\bigr)\I_n
    \preceq
    \widehat G_{\rm row}^{\rho_{\rm sig},\pi}(h,\omega,\sigma;A)-A^TA
  \right.
\\[-2pt]
&\left.\hspace{4.0cm}
    \preceq
    \bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig},\pi}^{\rm fp}\bigr)\I_n
  \right]
  \ge
  1-\mathcal L_{\rm pg,row}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg,row}\le\delta\), then the displayed
fully computed event has probability at least \(1-\delta\).

The exact objects are \(A\), the product grid \(z_a\), the exact CountSketch
hash/sign law, the exact row-sampling law, the exact per-bucket order
\(\pi\), and the exact reference \(A^TA\).  The computed non-probability
objects are \(\widehat\omega^{\rho_{\rm sig}}\),
\(\widehat Y^{\rho_{\rm sig},\pi}\), \(\widehat d_\star\),
\(\widehat B^{\rho_{\rm sig},\pi}\), and
\(\widehat G_{\rm row}^{\rho_{\rm sig},\pi}\).

For fixed realized \(h,\omega,\sigma,\pi,A\), fixed \(d>0\), and nonzero
leading deterministic coefficient,
\[
  \begin{aligned}
  T_{{\rm CS,row},\rho_{\rm sig},\pi}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s
      \Frob{|\widehat B^{\rho_{\rm sig},\pi}|^T
            |\widehat B^{\rho_{\rm sig},\pi}|}
  \\
  &+
    \Frob{(E^{{\rm den},\rho_{\rm sig},\pi})^T
          |\widehat B^{\rho_{\rm sig},\pi}|
          +
          |\widetilde B^{\rho_{\rm sig},\pi}|^T
          E^{{\rm den},\rho_{\rm sig},\pi}}
  \\
  &+
    \Frob{(F^{\rho_{\rm sig},\pi})^T
          |\widetilde B^{\rho_{\rm sig},\pi}|
          +
          |B|^TF^{\rho_{\rm sig},\pi}}
  \Big).
  \end{aligned}
\]
Substituting the irreducible definitions,
\[
  E^{{\rm den},\rho_{\rm sig},\pi}_{qj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig},\pi}_{qj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig},\pi}_{\sigma_qj}|}
         {|\widehat d_\star|}
    \frac{4u+3u^2+u^3}{1-u}
  \right),
\]
and
\[
  F^{\rho_{\rm sig},\pi}_{qj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{b_{\sigma_q}(h)}}{d}
    \sum_{t=1}^{b_{\sigma_q}(h)}
      |A_{k_{\sigma_q,t}j}|
  \right).
\]
The deterministic radius tends to zero as
\[
  u,\gamma_s,\gamma_{b_i(h)},\frac{4u+3u^2+u^3}{1-u}\to0
\]
for fixed realized data, while the probability loss remains exactly
\(\mathcal L_{\rm pg,row}\).
\end{corollary}

\begin{corollary}[Product-grid CountSketch plus downstream uniform rows with stored signs and tree-reduced buckets]
Let \(A\in\R^{m\times n}\) be the exact input matrix, let \(r>0\) be the
number of CountSketch rows, and let \(s>0\) be the number of downstream
uniformly sampled rows.  Let \(\mathcal I\) be the exact finite product-grid
index set, let \(z_a\in\R^n\) denote the exact grid vector indexed by
\(a:\{1,\ldots,n\}\to\mathcal I\), and let
\(\eta,L,\rho,\eta_{\rm row}>0\).  Define the exact product-grid plus
downstream row-sampling loss
\[
  \mathcal L_{\rm pg,row}
  =
  \sum_{a:\{1,\ldots,n\}\to\mathcal I}
    \frac{2\Norm{Az_a}^4}{r\eta^2}
  +
    \frac{2\Frob{A}^4}{rL^2}
  +
    \frac{r\,m^2\Frob{A}^4}{s\eta_{\rm row}^2}.
\]
The exact CountSketch hash is \(h:\{1,\ldots,m\}\to\{1,\ldots,r\}\), the
exact signs are \(\omega_k\in\{-1,1\}\), and the exact downstream row trace is
\(\sigma=(\sigma_1,\ldots,\sigma_s)\), drawn from the exact iid uniform law on
\(\{1,\ldots,r\}\).  These probability laws are exact mathematical inputs.

Let the implemented sign table be formed by one of the concrete routines
\[
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
so that \(\widehat\omega_k^{\rho_{\rm sig}}\) is respectively
\(\fl(\omega_k\cdot1)\), \(\fl(\omega_k+0)\), or \(\fl(\omega_k-0)\), and
\[
  |\widehat\omega_k^{\rho_{\rm sig}}-\omega_k|\le u.
\]
For each realized hash \(h\) and bucket \(i\), set
\[
  B_i(h)=\{k:h(k)=i\},
  \qquad
  b_i(h)=|B_i(h)|,
\]
and fix an exact enumeration
\[
  k_{i,1},\ldots,k_{i,b_i(h)}
\]
of \(B_i(h)\).  Let \(\mathcal T_i(h)\) be an exact binary summation tree with
\(b_i(h)+1\) leaves: the first \(b_i(h)\) leaves hold the rounded signed
products, and the final leaf is an exact zero padding value.  Define
\[
  d_i(h)=\mathrm{depth}\bigl(\mathcal T_i(h)\bigr).
\]
Assume the floating-point model has valid \(\gamma_{d_i(h)}\) for every
realized bucket tree and valid \(\gamma_s\) for the downstream length-\(s\)
sampled-Gram dot products.

The exact sparse sketch is
\[
  Y_{ij}
  =
  \sum_{t=1}^{b_i(h)}
    \omega_{k_{i,t}}A_{k_{i,t}j}.
\]
The computed sparse sketch
\[
  \widehat Y^{\rho_{\rm sig},\mathcal T}
\]
is obtained by storing the signs, forming rounded products
\(\fl(\widehat\omega_{k_{i,t}}^{\rho_{\rm sig}}A_{k_{i,t}j})\), and reducing
each bucket through \(\mathcal T_i(h)\).  Its entrywise radius is
\[
\begin{aligned}
  E^{{\rm CS},\rho_{\rm sig},\mathcal T}_{ij}
  &:=
  \bigl(u+\gamma_{d_i(h)}+u\gamma_{d_i(h)}\bigr)
  \sum_{t=1}^{b_i(h)}
    |\widehat\omega^{\rho_{\rm sig}}_{k_{i,t}}|\,|A_{k_{i,t}j}|
\\
  &\quad+
  u\sum_{t=1}^{b_i(h)}|A_{k_{i,t}j}|.
\end{aligned}
\]

Set the exact row-scale denominator and the concrete computed denominator to
\[
  d=\sqrt{s/r},
  \qquad
  \widehat d_\star
  =
  \fl\!\left(
    \fl(\sqrt{s})\,\fl(1/\fl(\sqrt r))
  \right).
\]
The concrete denominator certificate is
\[
  \widehat d_\star\ne0,\qquad
  |\widehat d_\star-d|\le d\,\Delta_\star,
  \qquad
  \Delta_\star=\frac{4u+3u^2+u^3}{1-u}.
\]
For \(q=1,\ldots,s\) and \(j=1,\ldots,n\), define
\[
  B_{qj}=\frac{Y_{\sigma_qj}}{d},
  \qquad
  \widetilde B^{\rho_{\rm sig},\mathcal T}_{qj}
  =
  \frac{\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_qj}}{d},
\]
and
\[
  \widehat B^{\rho_{\rm sig},\mathcal T}_{qj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_qj}}
         {\widehat d_\star}
  \right).
\]
The computed-denominator row entry radius is
\[
  E^{{\rm den},\rho_{\rm sig},\mathcal T}_{qj}
  =
  u|\widehat B^{\rho_{\rm sig},\mathcal T}_{qj}|
  +
  \frac{|\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_qj}|}
       {|\widehat d_\star|}\,\Delta_\star ,
\]
and the sampled sparse-sketch basis perturbation is
\[
  F^{\rho_{\rm sig},\mathcal T}_{qj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig},\mathcal T}_{\sigma_qj}}{d}.
\]

Define the deterministic downstream floating-point radius
\[
  T_{{\rm CS,row},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig},\mathcal T}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig},\mathcal T}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig},\mathcal T}^{\rm fp},
\]
where
\[
  T_{{\rm den},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      E^{{\rm den},\rho_{\rm sig},\mathcal T}_{qj}
        |\widehat B^{\rho_{\rm sig},\mathcal T}_{qk}|
      +
      |\widetilde B^{\rho_{\rm sig},\mathcal T}_{qj}|
        E^{{\rm den},\rho_{\rm sig},\mathcal T}_{qk}
    \right)_{j,k=1}^{n}
  },
\]
\[
  T_{{\rm dot},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  \Frob{
    \left(
      \gamma_s\sum_{q=1}^{s}
      |\widehat B^{\rho_{\rm sig},\mathcal T}_{qj}|
      |\widehat B^{\rho_{\rm sig},\mathcal T}_{qk}|
    \right)_{j,k=1}^{n}
  },
\]
and
\[
  T_{{\rm basis},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      F^{\rho_{\rm sig},\mathcal T}_{qj}
        |\widetilde B^{\rho_{\rm sig},\mathcal T}_{qk}|
      +
      |B_{qj}|F^{\rho_{\rm sig},\mathcal T}_{qk}
    \right)_{j,k=1}^{n}
  }.
\]

With
\[
  \tau_{\rm CS}=\eta+L(2\rho+\rho^2),
\]
the fully computed sampled Gram
\[
  \widehat G_{\rm row}^{\rho_{\rm sig},\mathcal T}(h,\omega,\sigma;A)
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig},\mathcal T})^T
    \widehat B^{\rho_{\rm sig},\mathcal T}
  \right)
\]
satisfies
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig},\mathcal T}^{\rm fp}\bigr)\I_n
    \preceq
    \widehat G_{\rm row}^{\rho_{\rm sig},\mathcal T}(h,\omega,\sigma;A)-A^TA
  \right.
\\[-2pt]
&\left.\hspace{4.0cm}
    \preceq
    \bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig},\mathcal T}^{\rm fp}\bigr)\I_n
  \right]
  \ge
  1-\mathcal L_{\rm pg,row}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg,row}\le\delta\), then the displayed
fully computed event has probability at least \(1-\delta\).

The exact objects are \(A\), the product grid \(z_a\), the exact CountSketch
hash/sign law, the exact downstream row-sampling law, the exact tree shapes
\(\mathcal T_i(h)\), and the reference \(A^TA\).  The tree shapes are exact
discrete implementation choices and not floating-point real computations.  The
computed non-probability objects are \(\widehat\omega^{\rho_{\rm sig}}\),
\(\widehat Y^{\rho_{\rm sig},\mathcal T}\), \(\widehat d_\star\),
\(\widehat B^{\rho_{\rm sig},\mathcal T}\), and
\(\widehat G_{\rm row}^{\rho_{\rm sig},\mathcal T}\).  No extra
perturbation event or extra existence hypothesis is used.

For fixed realized \(h,\omega,\sigma,\mathcal T,A\), fixed \(d>0\), and
nonzero leading deterministic coefficient,
\[
  \begin{aligned}
  T_{{\rm CS,row},\rho_{\rm sig},\mathcal T}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s
      \Frob{|\widehat B^{\rho_{\rm sig},\mathcal T}|^T
            |\widehat B^{\rho_{\rm sig},\mathcal T}|}
  \\
  &+
    \Frob{(E^{{\rm den},\rho_{\rm sig},\mathcal T})^T
          |\widehat B^{\rho_{\rm sig},\mathcal T}|
          +
          |\widetilde B^{\rho_{\rm sig},\mathcal T}|^T
          E^{{\rm den},\rho_{\rm sig},\mathcal T}}
  \\
  &+
    \Frob{(F^{\rho_{\rm sig},\mathcal T})^T
          |\widetilde B^{\rho_{\rm sig},\mathcal T}|
          +
          |B|^TF^{\rho_{\rm sig},\mathcal T}}
  \Big).
  \end{aligned}
\]
Substituting the irreducible definitions,
\[
  E^{{\rm den},\rho_{\rm sig},\mathcal T}_{qj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig},\mathcal T}_{qj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig},\mathcal T}_{\sigma_qj}|}
         {|\widehat d_\star|}
    \frac{4u+3u^2+u^3}{1-u}
  \right),
\]
and
\[
  F^{\rho_{\rm sig},\mathcal T}_{qj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{d_{\sigma_q}(h)}}{d}
    \sum_{t=1}^{b_{\sigma_q}(h)}
      |A_{k_{\sigma_q,t}j}|
  \right).
\]
If the selected bucket trees are balanced, so that
\[
  d_i(h)=\Theta\!\bigl(\log(b_i(h)+1)\bigr),
\]
then in the usual small-\(u\) regime
\[
  F^{\rho_{\rm sig},\mathcal T}_{qj}
  =
  \Theta\!\left(
    \frac{u(1+\log(b_{\sigma_q}(h)+1))}{d}
    \sum_{t=1}^{b_{\sigma_q}(h)}
      |A_{k_{\sigma_q,t}j}|
  \right).
\]
The deterministic radius tends to zero as
\[
  u,\gamma_s,\gamma_{d_i(h)},\Delta_\star\to0
\]
for fixed realized data, while the probability loss remains exactly
\(\mathcal L_{\rm pg,row}\).
\end{corollary}

\begin{corollary}[Stored-sign CountSketch with alternate computed denominators]
Keep the hypotheses, exact product-grid loss \(\mathcal L_{\rm pg,row}\),
stored-sign mode
\[
  \rho_{\rm sig}\in\{\mathrm{mul1},\mathrm{add0},\mathrm{sub0}\},
\]
and exact denominator \(d=\sqrt{s/r}\) from the preceding stored-sign
corollary.  Let the denominator route be
\[
  \lambda\in
  \{\mathrm{sqrtExact},\mathrm{divSqrt},
    \mathrm{invMulSqrt},\mathrm{sqrtDivSqrt}\}.
\]
The corresponding computed denominators are
\[
\begin{array}{@{}ll@{}}
\lambda=\mathrm{sqrtExact}:&
  \widehat d_\lambda=\fl_{\rm sqrt}(s/r),
  \quad\text{where the input ratio }s/r\text{ is supplied exactly},\\[1mm]
\lambda=\mathrm{divSqrt}:&
  \widehat d_\lambda=\fl_{\rm sqrt}(\fl_{\rm div}(s,r)),\\[1mm]
\lambda=\mathrm{invMulSqrt}:&
  \widehat d_\lambda=\fl_{\rm sqrt}(\fl_{\rm mul}(s,\fl_{\rm div}(1,r))),\\[1mm]
\lambda=\mathrm{sqrtDivSqrt}:&
  \widehat d_\lambda=\fl_{\rm div}(\fl_{\rm sqrt}(s),\fl_{\rm sqrt}(r)).
\end{array}
\]
For each route the concrete denominator certificate proves
\[
  \widehat d_\lambda\ne0,\qquad
  |\widehat d_\lambda-d|\le d\,\Delta_\lambda,
\]
where
\[
\begin{array}{@{}ll@{}}
\Delta_{\mathrm{sqrtExact}}=u,&
\Delta_{\mathrm{divSqrt}}=\sqrt{1+u}\,u+u,\\[1mm]
\Delta_{\mathrm{invMulSqrt}}=\sqrt{(1+u)(1+u)}\,u+2u+u^2,&
\Delta_{\mathrm{sqrtDivSqrt}}=\dfrac{3u+u^2}{1-u}.
\end{array}
\]
Define the route-dependent scaled rows
\[
  \widehat B^{\rho_{\rm sig},\lambda}_{qj}
  =
  \fl\!\left(
    \frac{\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}}
         {\widehat d_\lambda}
  \right),
  \qquad
  \widetilde B^{\rho_{\rm sig}}_{qj}
  =
  \frac{\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}}{d}.
\]
The exact reference \(B_{qj}=Y_{\sigma_qj}/d\) is unchanged.  The
route-dependent computed-denominator row entry radius is
\[
  E^{{\rm den},\rho_{\rm sig},\lambda}_{qj}
  =
  u|\widehat B^{\rho_{\rm sig},\lambda}_{qj}|
  +
  \frac{|\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}|}
       {|\widehat d_\lambda|}\,\Delta_\lambda .
\]
The stored-sign sparse-apply sampled radius is still
\[
  F^{\rho_{\rm sig}}_{qj}
  =
  \frac{E^{{\rm CS},\rho_{\rm sig}}_{\sigma_qj}}{d}.
\]
Set
\[
  T_{{\rm CS,row},\rho_{\rm sig},\lambda}^{\rm fp}
  =
  T_{{\rm den},\rho_{\rm sig},\lambda}^{\rm fp}
  +
  T_{{\rm dot},\rho_{\rm sig},\lambda}^{\rm fp}
  +
  T_{{\rm basis},\rho_{\rm sig},\lambda}^{\rm fp},
\]
with
\[
  T_{{\rm den},\rho_{\rm sig},\lambda}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      E^{{\rm den},\rho_{\rm sig},\lambda}_{qj}
        |\widehat B^{\rho_{\rm sig},\lambda}_{qk}|
      +
      |\widetilde B^{\rho_{\rm sig}}_{qj}|
        E^{{\rm den},\rho_{\rm sig},\lambda}_{qk}
    \right)_{j,k=1}^{n}
  },
\]
\[
  T_{{\rm dot},\rho_{\rm sig},\lambda}^{\rm fp}
  =
  \Frob{
    \left(
      \gamma_s\sum_{q=1}^{s}
      |\widehat B^{\rho_{\rm sig},\lambda}_{qj}|
      |\widehat B^{\rho_{\rm sig},\lambda}_{qk}|
    \right)_{j,k=1}^{n}
  },
\]
and
\[
  T_{{\rm basis},\rho_{\rm sig},\lambda}^{\rm fp}
  =
  \Frob{
    \left(
      \sum_{q=1}^{s}
      F^{\rho_{\rm sig}}_{qj}
        |\widetilde B^{\rho_{\rm sig}}_{qk}|
      +
      |B_{qj}|F^{\rho_{\rm sig}}_{qk}
    \right)_{j,k=1}^{n}
  }.
\]
Then the fully computed stored-sign downstream sampled Gram
\[
  \widehat G_{\rm row}^{\rho_{\rm sig},\lambda}(h,\omega,\sigma;A)
  =
  \fl\!\left(
    (\widehat B^{\rho_{\rm sig},\lambda})^T
    \widehat B^{\rho_{\rm sig},\lambda}
  \right)
\]
satisfies
\[
\begin{aligned}
&\Prob_{h,\omega,\sigma}
  \left[
    -\bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig},\lambda}^{\rm fp}\bigr)\I_n
    \preceq
    \widehat G_{\rm row}^{\rho_{\rm sig},\lambda}(h,\omega,\sigma;A)-A^TA
  \right.
\\[-2pt]
&\left.\hspace{4.0cm}
    \preceq
    \bigl(\tau_{\rm CS}+\eta_{\rm row}
      +T_{{\rm CS,row},\rho_{\rm sig},\lambda}^{\rm fp}\bigr)\I_n
  \right]
  \ge
  1-\mathcal L_{\rm pg,row}.
\end{aligned}
\]
Equivalently, if \(\mathcal L_{\rm pg,row}\le\delta\), then the displayed
fully computed event has probability at least \(1-\delta\).

The exact objects are \(A\), the product grid \(z_a\), the exact CountSketch
hash/sign law, the exact uniform row-sampling law, and the exact reference
matrix \(A^TA\).  The computed non-probability objects are
\(\widehat\omega^{\rho_{\rm sig}}\),
\(\widehat Y^{\rho_{\rm sig}}\), \(\widehat d_\lambda\),
\(\widehat B^{\rho_{\rm sig},\lambda}\), and
\(\widehat G_{\rm row}^{\rho_{\rm sig},\lambda}\).

For fixed realized \(h,\omega,\sigma,A\), fixed \(d>0\), and nonzero leading
deterministic coefficient,
\[
  \begin{aligned}
  T_{{\rm CS,row},\rho_{\rm sig},\lambda}^{\rm fp}
  =
  \Theta\!\Big(
  &\gamma_s
      \Frob{|\widehat B^{\rho_{\rm sig},\lambda}|^T
            |\widehat B^{\rho_{\rm sig},\lambda}|}
  \\
  &+
    \Frob{(E^{{\rm den},\rho_{\rm sig},\lambda})^T
          |\widehat B^{\rho_{\rm sig},\lambda}|
          +
          |\widetilde B^{\rho_{\rm sig}}|^T
          E^{{\rm den},\rho_{\rm sig},\lambda}}
  \\
  &+
    \Frob{(F^{\rho_{\rm sig}})^T
          |\widetilde B^{\rho_{\rm sig}}|
          +
          |B|^TF^{\rho_{\rm sig}}}
  \Big),
  \end{aligned}
\]
and, after substituting the irreducible definitions,
\[
  E^{{\rm den},\rho_{\rm sig},\lambda}_{qj}
  =
  \Theta\!\left(
    u|\widehat B^{\rho_{\rm sig},\lambda}_{qj}|
    +
    \frac{|\widehat Y^{\rho_{\rm sig}}_{\sigma_qj}|}
         {|\widehat d_\lambda|}\Delta_\lambda
  \right),
\]
\[
  F^{\rho_{\rm sig}}_{qj}
  =
  \Theta\!\left(
    \frac{u+\gamma_{b_{\sigma_q}(h)}}{d}
    \sum_{k:h(k)=\sigma_q}|A_{kj}|
  \right).
\]
Thus the deterministic floating-point radius is non-vacuous in the small
roundoff regime and tends to zero as
\[
  u,\gamma_s,\gamma_{b_i(h)},\Delta_\lambda\to0.
\]
The probability-loss order is unchanged from the exact product-grid
CountSketch plus exact downstream row-sampling loss; denominator computation
affects only the deterministic radius.
\end{corollary}

\begin{thebibliography}{9}

\bibitem{DrineasMahoney2016RandNLA}
Petros Drineas and Michael W. Mahoney.
\newblock RandNLA: randomized numerical linear algebra.
\newblock \emph{Communications of the ACM}, 59(6):80--90, 2016.
\newblock \url{https://doi.org/10.1145/2842602}.

\bibitem{Tropp2011SRHT}
Joel A. Tropp.
\newblock Improved analysis of the subsampled randomized Hadamard transform.
\newblock \emph{Advances in Adaptive Data Analysis}, 3(1--2):115--126, 2011.
\newblock \url{https://doi.org/10.1142/S1793536911000787};
preprint \url{https://arxiv.org/abs/1011.1595}.

\bibitem{CharikarChenFarachColton2002}
Moses Charikar, Kevin Chen, and Martin Farach-Colton.
\newblock Finding frequent items in data streams.
\newblock In \emph{Automata, Languages and Programming}, ICALP 2002,
Lecture Notes in Computer Science 2380, pages 693--703, 2002.
\newblock \url{https://doi.org/10.1007/3-540-45465-9_59}.

\bibitem{ClarksonWoodruff2013}
Kenneth L. Clarkson and David P. Woodruff.
\newblock Low rank approximation and regression in input sparsity time.
\newblock In \emph{Proceedings of the 45th Annual ACM Symposium on Theory of
Computing}, pages 81--90, 2013.
\newblock \url{https://doi.org/10.1145/2488608.2488620};
preprint \url{https://arxiv.org/abs/1207.6365}.

\bibitem{Ledoux1997}
Michel Ledoux.
\newblock On Talagrand's deviation inequalities for product measures.
\newblock \emph{ESAIM: Probability and Statistics}, 1:63--87, 1997.
\newblock \url{https://doi.org/10.1051/ps:1997103}.

\bibitem{Tropp2012}
Joel A. Tropp.
\newblock User-friendly tail bounds for sums of random matrices.
\newblock \emph{Foundations of Computational Mathematics}, 12:389--434, 2012.
\newblock \url{https://doi.org/10.1007/s10208-011-9099-z}.

\bibitem{Higham2002}
Nicholas J. Higham.
\newblock \emph{Accuracy and Stability of Numerical Algorithms}.
\newblock Second edition, SIAM, 2002.

\end{thebibliography}

\end{document}
